### 2014-08-22 main.tex
Deanna initial version + HRI template + formatting

\documentclass{sig-alternate}

% UTF8 support
\usepackage[utf8x]{inputenc}

\usepackage{hyperref}
\usepackage{epsf,graphicx}
\graphicspath{{figures/}}
\usepackage{subfigure}
\usepackage[colorinlistoftodos]{todonotes}

\newcommand{\eg}{{\textit{e.g.~}}}
\newcommand{\etal}{{\textit{et al.~}}}
\newcommand{\ie}{{\textit{i.e.~}}}

%
% --- Author Metadata here ---
\conferenceinfo{10th ACM/IEEE International Conference on Human-Robot Interaction}{2015 Portland, USA}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
% --- End of Author Metadata ---

\title{\LARGE \bf
``Those who can't do teach'': Learning Handwriting by Teaching a Robot
}

%%% HRI 2015 -> double-blind review process

%\numberofauthors{3} 
%\author{
%\alignauthor
%Deanna Hood\\
%Séverin Lemaignan\\
%Pierre Dillenbourg\\
%    \affaddr{Computer-Human Interaction in\\ Learning and Instruction (CHILI)}\\
%    \affaddr{Ecole Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
%    \affaddr{CH-1015 Lausanne, Switzerland}\\
%    \email{firstname.lastname@epfl.ch}
%\alignauthor
%Rafael Garcia\\
%    \affaddr{Computer Vision and Robotics}\\
%    \affaddr{University of Girona}\\
%    \affaddr{Girona, Spain}
%}
%

\begin{document}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

Despite the social motivation for the use of a teachable agent for the
engagement and support of children with handwriting difficulties, to date no
such technology is known to have been developed. Presented is a teachable
robotic agent in this context of handwriting skills acquisition. It is
hypothesised that such a system could not just engage an unmotivated student,
but could also present the opportunity for children to experience motor mimicry
during handwriting intervention. It also allows for exploring the potential for
the \emph{learning by teaching} paradigm to be employed in the interaction so as
to stimulate meta-cognition, empathy and increased self-esteem in the child
user.

By leveraging simulated handwriting on a synchronised tablet display, a Nao
humanoid robot with limited fine motor capabilities has been configured as a
suitably embodied handwriting partner. Shape models derived from principal
component analysis of a dataset of letter trajectories are generated and allow
the robot to draw purposefully deformed letters. As a result, the objective of
developing an algorithm learning how to write characters well may be satisfied
by learning the optimal parameters for the model of said characters. Such a
learning algorithm has been developed, capable of incorporating feedback from
users both in terms of which generated letters are the best and from user
demonstrations.

A pilot study, conducted to obtain insight into children's use of the system, is
presented, which has validated the interaction for an in situ experiment
scheduled with a primary school class to evaluate the human-robot interaction
outcomes of the system, the first of its kind.

\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{INTRODUCTION}

Handwriting difficulties in children at an early age often negatively affects
the academic performance of the students \cite{Christensen2005} in addition to
their self-esteem being adversely affected \cite{Malloy1995}, causing them to
shy away from expressing what they know \cite{Medwell2008}.
%A conclusion drawn
%in \cite{Hoy2011} is that any handwriting intervention studies considered in the
%systematic review which involved fewer than two practice sessions per week and
%fewer than a total of 20 practice sessions, including homework, were found to
%demonstrate ineffective results. This highlights the necessity to engage
%students in an interaction that will be sustainable over the long-term.

Successful interventions for children with handwriting difficulties involve the
student in many sessions where they are engaged in physically practising the
skill \cite{Hoy2011}. However, the link between handwriting difficulties and low
self-efficacy \cite{Engel-Yeger2009} results in children who are unmotivated to
participate in such sessions, potentially leading to a developmental arrest in
the acquisition of the skill.

%Engel-Yeger, Nagauker-Yanuv and Rosenblum \cite{Engel-Yeger2009} have shown the
%link between handwriting difficulties and low self-efficacy, the belief in
%one's capabilities to complete a task. Bandura \cite{Bandura1990} maintains
%that self-efficacy constitutes the basis for the choice of whether or not to
%attempt a task. Indeed, third graders receiving intervention for their
%handwriting skills in \cite{Berninger1997} spoke of how they avoid writing
%because of how it is illegible to others. This mindset of believing that one is
%unable to write may lead to a developmental arrest in the acquisition of this
%skill, which may make intervention more difficult in the future. Consequently,
%it is of importance to engage students in activities in which their
%self-efficacy and self-motivation is restored.

The learning by teaching paradigm, which engages the target student in the act
of teaching another, has been shown to produce motivational, meta-cognition, and
educational benefits in a range of disciplines \cite{Rohrbeck2003}. An
application which is yet to be explored, however, is the use of learning by
teaching in handwriting intervention. One reason why this may be the case is
that in order to engage a child in the learning by teaching paradigm, there must
be an appropriately unskilled peer for them to tutor. While in some cases it may
be appropriate for a peer or teacher to simulate a na\"ive learner, however this
acting is likely to be eventually detected if for an activity where one's skill
level is visually evident - as is the case in handwriting.

Presented is the development of the first known learning agent which is capable
of artificially making mistakes typical of children learning handwriting and
correcting them with external feedback, and therefore exhibiting the potential
to engage children in the learning by teaching paradigm in the context of
handwriting. Furthermore, the learning agent has been embodied in a commercially
affordable humanoid robot by leveraging synchronisation with a tablet display to
simulate fine motor skills otherwise infeasible for the robot.

The significance in the learning by teaching paradigm of observing a teachable
agent respond to what has been taught \cite{Okita2006} is reasoning for using an
embodied agent which is capable of responding to handwriting feedback with a
process rather than simply a product. Therefore investigating the use of a
humanoid capable of executing handwriting trajectories is supported. The
potential for motor mimicry to yield significant improvements in handwriting
interventions \cite{Berninger1997} further supports the case for investigating
the use of a humanoid robot capable of physically demonstrating handwriting
trajectories to its child learning partner.

Section \ref{sec:learningAlgorithm} presents the learning algorithm employed for
developing a learning agent in the context of handwriting, Section
\ref{sec:robotWriting} details the extension of this algorithm to an embodied
robotic learning agent, and Section \ref{sec:experiment} explains the potential
use of such a system in addressing pedagogical research questions, as inferred
from experiments conducted with primary school children.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Learning Agent in the Context of Handwriting} \label{sec:learningAlgorithm}

Because of the objective to use an artificial intelligence algorithm in a
reinforcement learning framework, a parameterisation of letters and their
deformities has been sought such that, depending on the parameters input to the
letter models, different quality shapes can be generated: from bad, to good,
with the help of feedback from the reinforcement learning partner. To this end,
a method which can generate a model from real-world data has been employed in
order to capture said realistic variations.

\subsection{Shape Modelling of Letters} \label{sec:writingGeneration}

One approach for a shape model which can appropriately represent realistic
variations in shapes with its parameters is statistical shape modelling, an
application of principle component analysis (PCA), where a linear transform that
de-correlates data vectors is found \cite{Stegmann2002}.

PCA on a set of letter paths captured from a digital pen has been performed,
using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
each letter (2 repetitions from 60 users). While it may be appropriate to
identify the location of the most salient features of the shapes in future work,
the features are currently taken as $n$ uniformly spaced points along the shape
path and arranged into an observation vector presented in (\ref{eq:obsVec}),
where $x_i$ and $y_i$ represent the coordinates of each of the points along the
path.

\begin{equation}\label{eq:obsVec}
{\bf x} = [x_1, x_2, \ldots, x_n, y_1, y_2, \ldots, y_n]^T
\end{equation}

In this work, the observation shapes are normalized such that they have a shape
centre of ${\bf 0}$ and a unit maximum dimension.

The projection from the original $2n$ dimensional feature space to the $N$
dimensional feature space is then found as in (\ref{eq:projection}), where ${\bf
p}$ contains the coordinates in the $N$ dimensional space with ${\bf 0}$-origin,
calculated as in (\ref{eq:paramCalc}). The $2n\times N$ matrix ${\bf \Phi }$ is
an orthogonal matrix composed of the eigenvectors ${\bf v}_i$ of the covariance
matrix of the observations which correspond to the largest $N$ eigenvalues
($\lambda_i$), as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}.

\begin{equation}\label{eq:projection}
{\bf \tilde{x}=\bar{x}+\Phi p}
\end{equation}
\begin{equation}\label{eq:paramCalc}
{\bf p} ={\bf \Phi}^T ({\bf {x}-\bar{x}})
\end{equation}
\begin{equation}\label{eq:transformCalc}
{\bf \Phi} = [{\bf v}_1, {\bf v}_2, \ldots, {\bf v}_N]^T
\end{equation}

If $N = 2n$, the projection will be nothing more than a change of basis, however
if there is correlation between the points in the observations, there will be
eigenvalues of the covariance matrix which are close to zero, and so removing
the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
reduction with minimal impact. Indeed, the amount of variance in the dataset
that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
therefore the proportion of the variance explained by each dimension/eigenvector
is as shown in (\ref{eq:proportionVar}).

\begin{equation}\label{eq:proportionVar}
\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
\end{equation}

Paths of a particular letter have been clustered using K-means clustering to
group different styles of writing the letter (\emph{allographs}), such that the
parameters in the resulting model are only representative of the specific
allograph of the letter in the dataset. PCA has been performed on all of the
paths of a particular allograph in the dataset at a time, to reduce the $2n$
dimensional space to one of a desired number of dimensions. This process may be
considered to generate a shape model in that (\ref{eq:projection}) may be used
to generate new shapes based on the parameters ${\bf p}$ which are used: ${\bf
p}={\bf 0}$ will yield the mean shape, and variations to each of the $N$ values
in ${\bf p}$ will cause a change in the shape represented by the corresponding
eigenvector (Figure \ref{fig:deviations_sPrint}).

\begin{figure}[thpb]
\centering
\subfigure{
\raisebox{-0.5\height}{\includegraphics[width=0.07\textwidth]{figures/sPrint_mean.png}
}}
\subfigure{
\raisebox{-0.5\height}{\includegraphics[width=0.38\textwidth]{figures/sPrint.png}
}}
\caption[The mean shape and the effect of varying the first five parameters of
the shape model derived from PCA from the dataset of print `s'
shapes.]{\label{fig:deviations_sPrint}The mean shape (left) and the effect
(right) of varying the first five parameters (each row) of the shape model
derived from PCA from the first cluster of `s' shapes, interpreted as the print
allograph. The percentage of the total variance in the dataset explained by each
parameter is shown on the appropriate row. }

\end{figure}

Interestingly, the parameters which result from the unsupervised statistical
shape analysis, to some extent, represent variations which could intuitively be
identified by a manual parameterisation: the gap in the top half of the letter
compared to the bottom half, the width of the top half of the letter compared to
the bottom half, the width of the overall shape, etc., and as a result the shape
modelling has produced the desired outcomes in terms of parameterising the
shapes in ways which are able to be used to deform them meaningfully.

\subsection{Generating Poor Letters}

After determining the appropriate number of dimensions (N) of the data
representing the majority of the variance observed within different samples of a
letter in the dataset, new letters can be generated by varying the parameter
values in this N dimensional space in accordance with (\ref{eq:projection}). By
choosing parameter values which lie within the observed range in the dataset, it
is possible to produce letters which are more likely to be reasonable looking.
When the parameter values are outside of the range observed in the dataset, they
are less likely to represent shapes from the dataset of reasonable,
adult-written letters, and as a result are more likely to represent poor shapes.
Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
models of `e' and `g' - made from 120 observations with 70 points - by selecting
random values for the first 5 parameters from a distribution with standard
deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$ standard
deviation observed in the dataset.

\begin{figure}[thpb]
\centering
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.08\textwidth]{figures/e1.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.05\textwidth]{figures/e4.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.08\textwidth]{figures/e3.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.08\textwidth]{figures/e5.png}}}\\
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g1.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g3.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g4.png}}}
\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g5.png}}}
\caption[Sample letters generated from the PCA shape model on 120 `e' and `g'
paths.]{\label{fig:sampleLetters}Sample letters generated from the PCA shape
model on 120 `e' (top) and `g' paths (bottom), generated randomly from
parameters with $3\times$ the standard deviation observed in the dataset.}

\end{figure}

It is therefore feasible that `poor' letters can be produced using the shape
model generated from a dataset of adults' writing with PCA. In
\cite{Chandra2013}, it was found that children aged 4-6 participating in a
handwriting peer tutoring pilot study most often made mistakes classified as
inappropriate \emph{internal proportions} or \emph{global deformations}, and it
would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
the same general categories. Consequently, while using a database of children's
letters when available may yield potential for parameterising other mistakes
made by children, such as merging strokes or decomposing a shape into multiple
subparts inappropriately, sufficient capabilities for the shape model to
generate shapes given parameter variations which are appropriate for simulating
a na\"ive learning in the context of handwriting have been demonstrated.

\subsection{Responding to Feedback}

In the same way that the shape model of a particular letter can be used to take
parameters and generate a letter, in the case of the statistical shape model
presented in Section \ref{sec:writingGeneration}, it may also be used to take a
letter and determine its parameters given the model. The potential for the
parameters of a user-drawn shape to be obtained from the shape model have been
capitalised on to incorporate the capabilities for the learning algorithm to
adapt to the user's feedback via demonstration.

The statistical shape model may be used to determine the parameters of a
demonstration shape by projecting the features of the observed shape into the
lower-dimensional space determined by the model. Mathematically, given a
demonstration ${\bf x}$, the associated parameters may be determined as in
(\ref{eq:param}).

\begin{equation}\label{eq:param}
{\bf p}_{demo} ={\bf \Phi}^T ({\bf {x}-\bar{x}})
\end{equation}

The parameters which are determined for a shape will not reconstruct the shape
exactly, but rather will reconstruct the closest point in the N dimensional
space which the eigenvectors span. With increasing value of N, the reconstructed
shape will be closer to the original shape, until N is equal to the number of
dimensions of the original shape, at which point there is no error incurred by
`projecting' onto the N dimensional space as the space is the same (but perhaps
with a different basis).

For the statistical shape model employed by the system, the method for
responding to user demonstrations is to move the learning algorithm's parameters
towards those of the demonstration to some extent. In the results presented in
this work, \[{\bf p}^{(k+1)} = {\bf p}^{(k)} + ({\bf p}_{demo}-{\bf
p}^{(k)})\times\alpha\] has been used, where ${\bf p}$ is the parameter vector
and $k$ is the time step, and $\alpha$ is the learning rate, between 0 and 1.
While it is possible that the resulting ${\bf p}^{(k+1)}$ yields an unacceptable
shape from combining ${\bf p}^{(k)}$ and ${\bf p}_{demo}$ which individually
yield acceptable shapes, what is significant about the proposed method for
adapting to user demonstration is that even it does not get stuck at such poor
shapes: with further demonstrations of the same letter, the system would
eventually approach it. It remains to be seen what the impact of such a poor
in-between shape being drawn by the teachable agent would have on the
interaction with the user, however, and how - if necessary - to avoid such an
event mathematically.

Further research may discover how to best model/limit the learning speed of the
robot so that it is noticeably learning while not improving so fast as to limit
the long-term interaction potential for the system, which may turn out to be
child-dependent.

Figure \ref{fig:demonstrationShapes2} illustrates the response of the system to
demonstrations from a child for the letter `u' using a learning rate of
$\alpha=1/2$.

\begin{figure}[thpb]
    \centering
    \includegraphics[width=0.3\textwidth]{figures/u_kids.png}
    \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
    responding to user demonstration of shapes for the letter `u.'}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{An Embodied Handwriting Learning Agent with the Nao Humanoid Robot} \label{sec:robotWriting}

In order to develop a teachable agent that is appropriate for engaging a child
through the learning by teaching paradigm - that is, that it is an embodied
agent, capable of eliciting motor mimicry, and capable of causing its teacher to
reflect on the process that has been used to respond to handwriting feedback -
capabilities for the robot to engage in handwriting have been established.

The Nao humanoid robot, which has been developed by Aldebaran-Robotics and
designed purposely to look approachable \cite{Gouaillier2008}, has been used for
this work. It is a commercially affordable biped robot, 58cm tall, with 25
degrees of freedom, two cameras, speech capabilities and the ability to
autonomously execute a range of tasks.

Because of the challenges in getting the Nao to write trajectories smoothly
because of its inherent ability to only reach discrete points in space, it has
been implemented instead that the robot uses simulated handwriting, as an
opportunity to have finer control over the robot's writing. The necessary
components to accomplish such are to:

\begin{enumerate}
    \item develop capabilities for the robot to trace handwriting,

    \item synchronise the robot's movements with the display of the writing on a
        tablet so that it seems that the robot is causing the handwriting to
        display because of its actions, and

    \item integrate the writing behaviour with the handwriting learning
        algorithm presented in Section \ref{sec:learningAlgorithm} to create a
        learning by teaching interaction with the agent. 
\end{enumerate}

These steps are presented in the sections that follow.

\subsection{Robot Trajectory Following}

As previously mentioned, the robot used in this system does not have
capabilities to reach all points in space due to its physical limitations
(finite degrees of freedom). Using simulated handwriting will not do anything to
fix this physical limitation, but it provides a context where the path traced by
the robot can be displayed smoother than it would have otherwise appeared if
written with a writing instrument. For believability, however, it is still
necessary that the robot's trajectory is close enough to that which is
displayed. As such, the requirements on the robot's fine motor skills are
lessened but not removed.

Aldebaran's NaoQi API has been used for the inverse kinematics of the trajectory
following. It provides the advantage of allowing the whole body to be used in
the inverse kinematics rather than simply the arm, which yields to an increased
working space of the robot. However, as motion planning is performed with
respect to the centre of the hand of the robot as opposed to the tip of a
writing instrument, restrictions on the orientation of the hand must be put in
place such that the writing instrument remains with the appropriate orientation
to the writing surface.

When pretending to write with a writing instrument, the requirement that the
instrument tip match the trajectory is still significant, and therefore any
change in orientation of the hand is exaggerated at the writing tip.

Rather than have the robot write with a writing instrument on a horizontal
surface, by instead having it point at a vertical writing surface to cause the
trajectory to appear (as in Figure \ref{fig:naoWriting}), several advantages are
presented:

\begin{itemize}

    \item The working space of the robot increases, both in the technical sense
        and the interaction sense: someone can, in theory, show the tablet to
        the robot from across the room and have it still respond, without
        needing the tablet to be within arm's reach.

    \item Concerns about whether or not the child would start mimicking the
        robot's incorrect (inhuman) writing style are mitigated. However, there
        is a possibility that this would also reduce the potential for students
        to benefit from motor imitation, although it is hypothesised that motor
        imitation is caused more from the overall concept of the trajectory
        being shown than from the pen grip being used.

    \item Perhaps most significantly, the accuracy of the matching of the
        robot's motion with the trajectory displayed on the tablet is not as
        critical, because the finger is not expected to touch the tablet exactly
        at the trajectory point, in contrast to the pen tip. This means that
        orientation degrees of freedom can be freed without significant adverse
        effects.

\end{itemize}

\begin{figure}[thpb]
     \begin{center}
        %\subfigure{
        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
        %}%
        \subfigure{
            \includegraphics[width=0.3\textwidth]{figures/naoWriting2.png}
        }%
%
    \end{center}
    \caption{A demonstration of the robot simulating the drawing of a word
        with its finger, synchronised with the tablet, communicating over ROS.
     }%

   \label{fig:naoWriting}
\end{figure}

Therefore the system presented utilises the context where the robot is
simulating handwriting by pointing at the tablet\footnote{Teachers interviewed
for their feedback on the system advised that children are asked to draw letters
in the air in a similar manner as part of their handwriting education.}.

\subsection{Synchronisation with the Tablet Trajectory Display}

After getting the robot to trace writing trajectories, the next step towards
simulated handwriting is getting the trajectories of the robot's `writing' to
display on an Android tablet instead of being displayed in the RViz
visualisation tool running on the computer.

ROS has been used to connect the devices used in the system, including the
Android tablet\footnote{For more information about ROS on Android devices see
\url{http://wiki.ros.org/android}}. As a result, aspects of the networking
between the tablet and the robot, such as the overheads associated with
connections, ports, message formats, publishers/subscribers, etc. have already
been implemented.

An Android application has been developed to receive the trajectory message over
a ROS topic and add each point of the trajectory one by one as a frame of an
animation. Synchronisation between the tablet and the robot has been achieved by

\begin{itemize}

    \item sending a requested start time accompanying the trajectory, which is
        sufficiently in the future, to account for varying transmission delays
        to the nodes on different devices,

    \item synchronising all clocks with NTP servers such that the ROS time used
        for responding to the requested start time is the same at all nodes,

    \item reducing the number of points along the trajectory passed to the
        robot's motion planner, as the more points, the more the robot gets out
        of synch with the requested timings, and

    \item not running computationally expensive tasks on the robot (such as
        camera publishing) while it is writing, as this interferes with the
        requested timings between points.

\end{itemize}

%\subsection{Integration and Synchronisation}

To instruct the robot where to write, the robot has been configured to detect a
particular fiducial marker, a \emph{chilitag}\footnote{See
\url{https://github.com/chili-epfl/ros_markers} for more information on the
fiducial marker detection node used.}, with the camera located in its head and
use that as the origin of the writing surface (Figure
\ref{fig:tabletDetection}). As publishing the robot's camera has been identified
as a computationally expensive task that can disrupt the robot's timing of
synchronised writing, it is only done when necessary and the tablet is assumed
to be stationary during the writing process.

\begin{figure}[htpb]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/chilitagDetection_cameraOverlay.png}
    \caption[Detection of the tablet using a chilitag to represent the origin of
    the writing surface frame.]{\label{fig:tabletDetection}Detection of the
    tablet using a chilitag to represent the origin of the writing surface frame
(left: robot's camera image, with markers overlaid).}

\end{figure}

A demonstration of the robot executing a trajectory in synch with the tablet is
shown in Figure \ref{fig:naoWriting}\footnote{See
\url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the
demonstration. }. As a result, the two relevant orientations of the hand were
fixed to keep the finger perpendicular to the writing surface, with the
remaining orientation free such that the wrist could rotate in order to easier
reach the points along the path. The use of whole body motion may be seen in
this demonstration, as the robot's centre of gravity is shifted to prevent the
wrist from rotating towards the centre of the robot, in which case the fingertip
would not match the writing trajectory. Without whole body motion control, it
would not have been possible to execute such a trajectory using only the degrees
of freedom in the arm.

\subsection{Integration into a Robotic Handwriting Learning Agent}

The fusion of the handwriting learning algorithm presented in Section
\ref{sec:learningAlgorithm} with the embodied handwriting agent developed
involves the integration of three components: the controller of the learning
algorithm, running on a computer, which manages the learning algorithm,
responding appropriate to feedback received, and publishes the shapes to be
drawn with their time and relevant position with respect to the writing surface;
the robot which draws the requested letters; and the application running on an
Android tablet which draws the requested letters in synch with the robot and
displays the result to the user, and acts as the medium for the user's feedback,
through touch gestures and user-drawn demonstrations.

Feedback from the user is passed to the controller with the location on the
tablet that it occurred at, and the task of interpreting the shape which the
feedback was intended for is left to the controller as it is aware of the
location of published shapes. The appropriate response in terms of the learning
algorithm is then taken for the respective shape.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{A Tool for Social and Pedagogical Investigations} \label{sec:experiment}

In addition to constituting a technically novel system, the teachable robotic
agent presented represents a tool which may be used for investigating social and
pedagogical research questions. One such question that is being worked towards
is what impact to the outcomes of a handwriting intervention the addition of
such a teachable robotic agent would have.

%\subsection{Interaction Context}

The interaction context which has been developed as a framework for addressing
such questions is one where participants are asked to improve the robot's
handwriting by correcting its letters. Figure \ref{fig:pilotInteraction}
illustrates an example interaction sequence between the participant and the
robot, which consists of the following stages.

\begin{enumerate}

    \item The participant shows the robot one of five different 3-letter words
        to write, which, combined, consist of 7 different letters (`c', `e',
        `n', `o', `s', `u', `w'). Fiducial markers placed on the word cards to
        allow for detection with a camera.

    \item The robot responds to the word request verbally and writes the letters
        by pointing at the tablet - placed in front of it with a vertical
        orientation - and imitating tracing the letters as they appear
        simultaneously by being displayed by the tablet.

    \item The robot asks for feedback from the participant and they demonstrate
        how to write the letter which they feel needs to be corrected. The
        demonstration is performed by drawing on the tablet with a stylus,
        either with the tablet still in a vertical orientation or by unfolding
        the stand and laying the tablet flat on the desk. The position of the
        participant's demonstration on the tablet encodes the shape letter that
        it is a demonstration for. The participant can clear their shapes if
        they are unhappy with them or they are in the wrong position. When the
        button to signal that it is the robot's turn is pressed, the
        demonstration is sent to the controller.

    \item The interaction iterates, with participants taking turns to interact
        with the robot.

\end{enumerate}

%To allow the system to take input from the user on which words to draw,
%fiducial markers were placed on cards which were detectable by a
%previously-developed ROS node processing a camera stream. A node which
%processed the fiducial markers detected was then created to convert the card
%detected into an appropriate message for the controller.

\begin{figure}[thpb!]
     \begin{center}
%
        \subfigure[The user shows a card to the robot with a word to write.]{%
            \label{fig:first}
            \includegraphics[width=0.2\textwidth]{figures/1card.png}
        }~
        \subfigure[The robot writes the word seen on the card and asks for feedback.]{%
           \label{fig:second}
           \includegraphics[width=0.2\textwidth]{figures/2word.png}
        }\\ %  ------- End of the first row ----------------------%
        \subfigure[The user provides feedback on the letters written via demonstration.]{%
            \label{fig:third}
            \includegraphics[width=0.2\textwidth]{figures/4correct.png}
        }~
        \subfigure[The robot responds to the feedback and asks for more.]{%
            \label{fig:fourth}
            \includegraphics[width=0.2\textwidth]{figures/5iterateAsk.png}
        }%
%
    \end{center}
    \caption{%
        A user interacting with the robot in the learning by teaching interaction using demonstrations.
     }%
   \label{fig:pilotInteraction}
\end{figure}

%\subsection{Outcomes}

A pilot study has been conducted to evaluate the interaction in preparation for
an experiment to be conducted on the 10th-11th of June, 2014. The pilot study
consisted of four groups of approximately 8 children, aged 6-7 years. Outcomes
from the pilot study include information on how children interact with the
system, sample letters written by children, opinions from the teachers involved,
and insight into what experimental conditions might be appropriate for the
experiment.

The system was validated, in that the learning algorithm and robotic writing
were believed by the children, and that the system withstood the interaction for
a total of 65 minutes, with the robot writing 96 letters, 49 of which in
response to demonstrations from the children, during that time.

Another key point which came from the pilot study is that children were observed
giving advice to the child designated as the letter demonstrator, potentially
giving rise to the higher level paradigm of learning by \emph{teaching to
teach}.

%\begin{itemize}
%
%\item Children would not intuitively write over the robot's letters, but rather
%above them. When instructed to write over the robot's letter, some participants
%would trace the letter as it had previously appeared as their demonstration. As
%such, the requested demonstration positioning will be modified for the
%experiment.
%
%\item While children spoke to the robot each time it requested feedback -
%suggesting that the anthropomorphised the robot - they also laughed when it
%wrote letters which were incorrect, which may suggest that they had not
%developed an empathetic connection with the robot by that point. 
%
%\item Children were observed giving advice to the child designated as the
%letter demonstrator, potentially giving rise to the higher level paradigm of
%learning by teaching to teach. 
%
%\end{itemize}

As a consequence of this observation, the upcoming experiment will address the
effect of the number of children interacting with the robot in order to
investigate the potential of the system to not only be used to set the context
of children tutoring the robot, but also children interacting as peer tutors
with each other.

%\section{ADDITIONAL REQUIREMENTS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions and Future Work}

%\subsection{Conclusions}

The technical challenges involved in developing a teachable robotic agent in the context of handwriting which have been addressed in this work include:

\begin{itemize}

    \item developing capabilities for a robot with limited fine motor
        capabilities, such as the Nao, to engage in the act of handwriting in a
        way that is believable for interacting with children, which has been
        accomplished by leveraging simulated handwriting with a synchronised
        tablet;

    \item developing a system for generating poorly written letters appropriate
        for simulating a na\"ive learner in the context of handwriting, achieved
        by using statistical shape models through PCA of observations of the
        trajectory of the same letter;

    \item developing an algorithm capable of incorporating user feedback and
        demonstrations in order to adapt the generated handwriting quality so as
        to simulate a teachable agent, which has been implemented by maintaining
        a learning algorithm in the parameter space of the shape models and
        converging towards the parameters of user demonstrations; and

    \item integrating the system into a working interaction suitable for
        engaging children in the learning by teaching paradigm, accomplished by
        fusing the robotic drawing capabilities and the learning algorithm for
        handwritten letters established.

\end{itemize}

%By leveraging the technology of a wirelessly synchronised tablet displaying a
%writing trajectory, the requirements for a robot with limited fine motor
%capabilities to accurately manipulate a writing implement have been reduced to
%instead requiring that the robot roughly trace the trajectory as it is
%simultaneously displayed on the tablet. Thus, capabilities for the Nao to
%engage in simulated handwriting have been demonstrated. By further lifting the
%constraint that the robot must draw with a writing instrument and allowing it
%instead to draw with its finger, in addition to increasing the range of
%trajectories which the robot is able to reach, the necessary accuracy in the
%robot's trajectory following is reduced as it is not necessary for the finger
%to physically touch the writing surface at the trajectory position for the
%simulation to be believable. As the motion control is currently limited to the
%position of the robot's hand rather than the writing tip, the reduced need for
%accurate motion in order to have a believable simulation was leveraged upon in
%the presented system to produce results with the robot drawing with its finger
%of sufficient accuracy.

%Statistical shape modeling using principal component analysis on a dataset of
%writing trajectories for a letter has been employed to generate shape models of
%different letters/allographs. These models, generated through unsupervised
%methods, have been shown to capture the internal proportions of letters in a
%similar way to how human intuition would identify the possible shape variances
%(width/height/proportional size of loops, skewness, etc.). As a result, the
%models have been used to generate synthetic letters which yield shapes
%appropriate for use in an artificial intelligence algorithm which uses user
%feedback on the best letter from a set of candidates drawn to converge to the
%parameter values of the selected shapes after some iterations.

%The letter model has been used to determine the parameter values of shapes
%demonstrated by the user. Provided that the user demonstrates the shape in the
%same style as those used to generate the shape model (i.e., with the strokes in
%the appropriate order and direction), the parameters of the demonstration may
%then be used as input to the learning algorithm to converge towards the user's
%writing demonstrations.

%The fusion of the robotic drawing capabilities and the learning algorithm for
%handwritten letters has resulted in a teachable robotic agent which can engage
%users in the learning by teaching paradigm in the context of handwriting. As
%such, the system developed has been shown to accomplish the technical goals
%which were set out to be achieved, and the implications of such a system
%evaluation of the system is underway, with an in situ interaction with primary
%school students being conducted in the coming weeks.

The work presented opens up the research area of the role for robots in the
education of handwriting and other embodied activities, and makes significant,
novel steps towards addressing the over-arching research question of how
interacting with such a robotic learning partner may be beneficial for
sustaining a child's interaction in handwriting interventions and the impact on
the participating child's motivation, self-esteem, and educational future.

%\subsection{Future Works}
%\section{Future work}

%A number of research questions remain open for investigation in the wider scope
%of the CoWriter project, in addition to those which have been raised as a
%result of the work carried out to develop the presented system.

%In the scope of open technical questions, it remains to be seen how shape
%models for letters might be generated which capture the full range of mistakes
%typical of children learning handwriting: extending the current system capable
%of incorporating internal proportion and global deformation errors to one which
%can also generate missing subparts of the letter, or break the letter down into
%primitive strokes at will, for example. Could incorporating a database of
%letters drawn by children into the shape modeling process facilitate this?

%In terms of the interaction experience, it may be interesting to investigate
%which other technology could be incorporated into the system for a more fluid
%interaction, such as integrating the user's gaze information to infer when the
%user is finished with a demonstration, or using a classification algorithm to
%determine which letter has been demonstrated irrespective of its positioning.

%On the educational side, open questions include how the handwriting error
%generation of the system may be abstracted to a higher level of control so that
%a teacher may configure it to work with a child on a particular type of
%mistakes, based on the child's performance. Where would the balance lie between
%developing autonomous capabilities for the system to determine the child's
%difficulties, and empowering the teaching staff to decide for themselves
%instead? And, as a result, the ultimate question for this area of research is
%to address what impact to the outcomes of a handwriting intervention the
%addition of such a teachable robotic agent would have: does it impact the
%motivation of the participants, their self-esteem, and/or the learning gains
%that they experience?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%\section{ACKNOWLEDGMENTS}

%The authors gratefully acknowledge the contribution of National Research Organization and reviewers' comments.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\begin{thebibliography}
\bibliographystyle{abbrv}
\bibliography{library}

%\end{thebibliography}

\end{document}

### 2014-08-22 main.tex
Rewritten conclusion

@@
 
+\subsection{Impact and Conclusion}
+
+We believe this article introduces three noteworthy contributions: an innovative
+application of data processing and artificial intelligence for the generation and
+learning of hand-written letters suitable for educative purposes; a robotic
+system that has been experimentally proven to provide convincing scaffolding for
+complex human-robot interactions (teacher-learner social interactions, learning by
+demonstration); an initial experimental investigation of what appears to be a
+new role for robots in education.
+
+Because it has the strongest impact for the human-robot interaction community,
+we would like to develop this last point in particular. The work presented here
+investigates a particular role for a robot in the education of handwriting: not
+only the robot is actively performing the activity (it draws letters), but it
+does so in a way that engages the child in a very specific social role. The child
+is the teacher, the robot is the learner: the child must engage in a
+(meta-)cognitive relation with the robot to try to understand why the
+robot fails and how to help it best.  Here, the robot is not only an activity
+facilitator or orchestrator: its physical presence and embodiment induce agency
+and anthropomorphizing, and cognitively engage the child into the learning
+activity, which we predict to lead to higher learning efficacy.
+
+Also notable, the robot is not used in the usual context of robotics or computer
+education, but instead in an activity -- handwriting -- that requires fine
+physical skills. In such activities, the embodied nature of the robot makes a
+lot of sense (due to motor mimicry, the arm motion for instance is, \emph{by
+itself}, part of the teaching). Along those lines, we hope to see more research
+on non-STEM educational applications of robotics.
+
+Beyond handwriting, we believe that this work provides a novel perspective on
+the role for robots in the education landscape. \emph{Learning by teaching} is a
+powerful paradigm because not only its pedagogical efficacy is proven, but it
+also positively impacts the child's motivation and self-esteem. We have
+discovered that it is also a very relevant context of use for robots. Indeed,
+when facing a child with school difficulties, robots can play a role (being the
+``even more ignorant student'') that neither the adults nor the peers (because
+of the social effects it would induce) can convincingly play.
+
+The strong social impact of early school problems makes research in this field
+a certainly useful challenge for HRI.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2014-08-22 main.tex
Re-enabled + rewritten Future Work section

@@
 \section{A Tool for Social and Pedagogical Investigations} \label{sec:experiment}
+\label{sec4}
 
@@
 
+\paragraph{Role of the experimenter}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-The technical challenges involved in developing a teachable robotic agent in the context of handwriting which have been addressed in this work include:
+The technical challenges involved in developing a teachable robotic agent in the
+context of handwriting which have been addressed in this work include:
 
@@
 
-The work presented opens up the research area of the role for robots in the
-education of handwriting and other embodied activities, and makes significant,
-novel steps towards addressing the over-arching research question of how
-interacting with such a robotic learning partner may be beneficial for
-sustaining a child's interaction in handwriting interventions and the impact on
-the participating child's motivation, self-esteem, and educational future.
+\subsection{Why a robot?}
 
-%\subsection{Future Works}
-%\section{Future work}
+\subsection{Future Work}
 
-%A number of research questions remain open for investigation in the wider scope
-%of the CoWriter project, in addition to those which have been raised as a
-%result of the work carried out to develop the presented system.
+In the scope of open technical questions, it remains to be seen how shape models
+for letters might be generated which capture the full range of mistakes typical
+of children learning handwriting: extending the current system capable of
+incorporating internal proportion and global deformation errors to one which can
+also generate missing subparts of the letter, or break the letter down into
+primitive strokes at will, for example. While we expect that incorporating a
+database of letters drawn by children into the shape modeling process would
+facilitate this, the current system has conceptual (a PCA only approach can not
+generate or learn a different shape topology) and technical (no support for
+multi-stroke shapes) limitations that need to be overcome.
 
-%In the scope of open technical questions, it remains to be seen how shape
-%models for letters might be generated which capture the full range of mistakes
-%typical of children learning handwriting: extending the current system capable
-%of incorporating internal proportion and global deformation errors to one which
-%can also generate missing subparts of the letter, or break the letter down into
-%primitive strokes at will, for example. Could incorporating a database of
-%letters drawn by children into the shape modeling process facilitate this?
+In terms of the interaction experience, the current experimental setting, while
+technically autonomous, can not robustly recover from situations outside of the
+nominal protocol (presented in section~\ref{sec4}), and consequently still requires the
+presence of an experimenter. The robot state machine would require to be
+extended in non-trivial ways to allow for long, fully autonomous, interactions
+with children.
 
-%In terms of the interaction experience, it may be interesting to investigate
+%it may be interesting to investigate
 %which other technology could be incorporated into the system for a more fluid
@@
 
-%On the educational side, open questions include how the handwriting error
-%generation of the system may be abstracted to a higher level of control so that
-%a teacher may configure it to work with a child on a particular type of
-%mistakes, based on the child's performance. Where would the balance lie between
-%developing autonomous capabilities for the system to determine the child's
-%difficulties, and empowering the teaching staff to decide for themselves
-%instead? And, as a result, the ultimate question for this area of research is
-%to address what impact to the outcomes of a handwriting intervention the
-%addition of such a teachable robotic agent would have: does it impact the
-%motivation of the participants, their self-esteem, and/or the learning gains
-%that they experience?
+On the educational side, open questions include how the handwriting error
+generation of the system may be abstracted to a higher level of control so that
+a teacher may configure it to work with a child on a particular type of
+mistakes, based on the child's performance. Where would the balance lie between
+developing autonomous capabilities for the system to determine the child's
+difficulties, and empowering the teaching staff to decide for themselves
+instead? And, as a result, the ultimate question for this area of research is
+to address what impact to the outcomes of a long-term handwriting intervention the
+addition of such a teachable robotic agent would have: does it impact the
+motivation of the participants, their self-esteem, and/or the learning gains
+that they experience? We are currently considering running a long-term study
+(about 20 hours of interactions per child) that would provide better evidences
+to answer these questions.
 

### 2014-09-04 main.tex
WIP

@@
 
+%(DH) is it too soon to claim learning by teaching benefits in the title...? 
+%(DH) the paper is not about "learning handwriting", it's about the robot.
 \title{\LARGE \bf
-``Those who can't do teach'': Learning Handwriting by Teaching a Robot
+``Those who can't do, teach'': a Teachable Robotic Agent for Children Learning Handwriting
 }
@@
 
-%\numberofauthors{3} 
-%\author{
-%\alignauthor
-%Deanna Hood\\
-%Séverin Lemaignan\\
-%Pierre Dillenbourg\\
-%    \affaddr{Computer-Human Interaction in\\ Learning and Instruction (CHILI)}\\
-%    \affaddr{Ecole Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
+% \numberofauthors{3} 
+% \author{
+% \alignauthor
+% Deanna Hood\\
+% Séverin Lemaignan\\
+% Pierre Dillenbourg\\
+%    \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
+%    \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
 %    \affaddr{CH-1015 Lausanne, Switzerland}\\
 %    \email{firstname.lastname@epfl.ch}
-%\alignauthor
-%Rafael Garcia\\
-%    \affaddr{Computer Vision and Robotics}\\
+% \alignauthor
+% Rafael Garcia\\
+%    \affaddr{Computer Vision and Robotics Group (ViCOROB)}\\
 %    \affaddr{University of Girona}\\
 %    \affaddr{Girona, Spain}
-%}
-%
+% }
+
+%(DH) my EPFL email address won't work for much longer....
 
@@
 
-Despite the social motivation for the use of a teachable agent for the
-engagement and support of children with handwriting difficulties, to date no
-such technology is known to have been developed. Presented is a teachable
-robotic agent in this context of handwriting skills acquisition. It is
-hypothesised that such a system could not just engage an unmotivated student,
-but could also present the opportunity for children to experience motor mimicry
-during handwriting intervention. It also allows for exploring the potential for
-the \emph{learning by teaching} paradigm to be employed in the interaction so as
-to stimulate meta-cognition, empathy and increased self-esteem in the child
-user.
+%Despite the social motivation for the use of a teachable agent for the
+%engagement and support of children with handwriting difficulties, to date no
+%such technology is known to have been developed.
+
+%(DH) abstract probably too long...
+%(DH) do we have to be specific somewhere about what stage of handwriting we're targeting..?
+
+Presented is a teachable humanoid agent in the context of handwriting skills
+acquisition. It is hypothesised that such a system could not just engage an
+unmotivated student, but could also present the opportunity for children to
+experience the typical benefits experienced during human-led handwriting
+interventions, such as motor mimicry. This system allows for exploring the
+potential for the \emph{learning by teaching} paradigm to be employed in the
+interaction, so as to stimulate meta-cognition, empathy and increased
+self-esteem in the child user.
 
@@
 component analysis of a dataset of letter trajectories are generated and allow
-the robot to draw purposefully deformed letters. As a result, the objective of
-developing an algorithm learning how to write characters well may be satisfied
-by learning the optimal parameters for the model of said characters. Such a
-learning algorithm has been developed, capable of incorporating feedback from
-users both in terms of which generated letters are the best and from user
-demonstrations.
+the robot to draw purposefully deformed letters. Learning how to write
+characters well is then achieved by incorporating feedback from user
+demonstrations, which allows the system to learn the optimal parameters for the
+appropriate shape models.
 
-A pilot study, conducted to obtain insight into children's use of the system, is
-presented, which has validated the interaction for an in situ experiment
-scheduled with a primary school class to evaluate the human-robot interaction
-outcomes of the system, the first of its kind.
+An in situ study has been conducted with primary school classes to obtain
+insight into children's use of the novel system. 
+%The technical components of the system have been validated, in that children 
+Children aged 6-8 were successfully 1) led to believe that the robot was
+actually writing on the tablet, and 2) able to improve the robot's writing to a
+level which they were satisfied with. Furthermore, the system represents a
+significant step towards an innovative use for robotics which addresses a
+widespread and socially meaningful challenge in education, and provides context
+for robotics in education beyond the well-explored use of teaching coding- and
+robotics-related subjects.
 
@@
 
-Handwriting difficulties in children at an early age often negatively affects
-the academic performance of the students \cite{Christensen2005} in addition to
+Handwriting difficulties in children at an early age often negatively affect
+the academic performance of the students \cite{Christensen2005}, in addition to
 their self-esteem being adversely affected \cite{Malloy1995}, causing them to
@@
 
-The learning by teaching paradigm, which engages the target student in the act
-of teaching another, has been shown to produce motivational, meta-cognition, and
-educational benefits in a range of disciplines \cite{Rohrbeck2003}. An
-application which is yet to be explored, however, is the use of learning by
-teaching in handwriting intervention. One reason why this may be the case is
-that in order to engage a child in the learning by teaching paradigm, there must
-be an appropriately unskilled peer for them to tutor. While in some cases it may
-be appropriate for a peer or teacher to simulate a na\"ive learner, however this
-acting is likely to be eventually detected if for an activity where one's skill
-level is visually evident - as is the case in handwriting.
+The \emph{learning by teaching} paradigm, which engages the target student in
+the act of teaching another, has been shown to produce motivational,
+meta-cognitive, and educational benefits in a range of disciplines
+\cite{Rohrbeck2003}. An application which is yet to be explored, however, is the
+application of learning by teaching to handwriting intervention. One reason why
+this has not been investigated to date is that in order to engage a child in the
+learning by teaching paradigm, there must be an appropriately unskilled peer for
+them to tutor. In the context where the target child is the lowest performer in
+their class, this may be a constraint. In some cases it may be appropriate for a
+peer or teacher to simulate a na\"ive learner for the target child to teach,
+however for an activity where one's skill level is visually evident - as is the
+case in handwriting - this acting is likely to be eventually detected. As such,
+there is motivation for the use of a teachable agent which can be configured for
+a variety of skill levels, and for which children do not have preconceptions
+about its handwriting ability.
 
 Presented is the development of the first known learning agent which is capable
-of artificially making mistakes typical of children learning handwriting and
-correcting them with external feedback, and therefore exhibiting the potential
+of artificially making mistakes typical of children learning handwriting, and
+correcting them with external feedback. Such a system therefore exhibits the potential
 to engage children in the learning by teaching paradigm in the context of
-handwriting. Furthermore, the learning agent has been embodied in a commercially
-affordable humanoid robot by leveraging synchronisation with a tablet display to
-simulate fine motor skills otherwise infeasible for the robot.
+handwriting.
 
-The significance in the learning by teaching paradigm of observing a teachable
-agent respond to what has been taught \cite{Okita2006} is reasoning for using an
-embodied agent which is capable of responding to handwriting feedback with a
-process rather than simply a product. Therefore investigating the use of a
-humanoid capable of executing handwriting trajectories is supported. The
-potential for motor mimicry to yield significant improvements in handwriting
-interventions \cite{Berninger1997} further supports the case for investigating
-the use of a humanoid robot capable of physically demonstrating handwriting
-trajectories to its child learning partner.
+There are three main points which have motivated the use of a robot as the
+teachable agent in the presented interaction:
 
-Section \ref{sec:learningAlgorithm} presents the learning algorithm employed for
-developing a learning agent in the context of handwriting, Section
-\ref{sec:robotWriting} details the extension of this algorithm to an embodied
-robotic learning agent, and Section \ref{sec:experiment} explains the potential
-use of such a system in addressing pedagogical research questions, as inferred
-from experiments conducted with primary school children.
+\begin{enumerate}
+    \item the engagement and ``protégé effect'' elicited by teaching an embodied
+        agent is anticipated to be stronger than that associated with a
+        tablet-based application, which children are increasingly recognising as
+        disposable technology,
+
+    \item observing a teachable agent respond to what it has been taught
+        \cite{Okita2006} is a significant step in the learning by teaching
+        paradigm, and therefore it may be significant for the agent to respond
+        with a writing \emph{process}, rather than simply a product, and
+
+    \item the potential for motor mimicry to yield significant improvements in
+        handwriting interventions \cite{Berninger1997} further supports the case
+        for investigating the use of a humanoid robot capable of physically
+        demonstrating handwriting trajectories to its child learning partner.
+\end{enumerate}
+
+Consequently, the learning agent developed has been embodied in a commercially
+affordable Nao humanoid robot. Its writing capabilities have been implemented by
+leveraging synchronisation with a tablet display to simulate fine motor skills
+otherwise infeasible for the robot.
+
+Section \ref{sec:learningAlgorithm} presents the novel work in the area of
+artificial intelligence to develop a learning algorithm suitable for a learning
+agent in the context of handwriting.  Section \ref{sec:robotWriting} details the
+extension of this algorithm to an embodied robotic learning agent, including the
+novel approach for achieving simulated fine motor skills on commercially
+affordable humanoid robots.  Section \ref{sec:experiment} explores the novel
+contributions made to the study of human-robot interaction, in discussing the
+use of the system with primary school children and its potential as a tool for
+addressing wider pedagogical research questions in education.
 
@@
 reinforcement learning framework, a parameterisation of letters and their
-deformities has been sought such that, depending on the parameters input to the
-letter models, different quality shapes can be generated: from bad, to good,
-with the help of feedback from the reinforcement learning partner. To this end,
-a method which can generate a model from real-world data has been employed in
-order to capture said realistic variations.
+deformities has been sought. Depending on the parameters input to the letter
+models, different quality shapes can be generated. The system can therefore be
+configured to improve its writing by modifying the parameters used to generate
+the letters, based on feedback from the reinforcement learning partner. To this
+end, a method which can generate a model from real-world data has been employed
+in order to capture realistic variations in letters.
 
@@
 One approach for a shape model which can appropriately represent realistic
-variations in shapes with its parameters is statistical shape modelling, an
-application of principle component analysis (PCA), where a linear transform that
-de-correlates data vectors is found \cite{Stegmann2002}.
+variations in shapes with changes to its parameters is statistical shape
+modelling. Statistical shape modelling is an application of principle component
+analysis (PCA), where a linear transform which de-correlates data vectors is
+found \cite{Stegmann2002} and allows for dimensionality reduction.
 
-PCA on a set of letter paths captured from a digital pen has been performed,
+PCA has been performed on a set of letter paths captured from a digital pen,
 using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
-each letter (2 repetitions from 60 users). While it may be appropriate to
+each letter (2 repetitions from 60 adult users). While it may be appropriate to
 identify the location of the most salient features of the shapes in future work,
 the features are currently taken as $n$ uniformly spaced points along the shape
-path and arranged into an observation vector presented in (\ref{eq:obsVec}),
+path as salient features are not guaranteed from children's handwriting. The
+points are arranged into an observation vector presented in (\ref{eq:obsVec}),
 where $x_i$ and $y_i$ represent the coordinates of each of the points along the
@@
 
-The projection from the original $2n$ dimensional feature space to the $N$
-dimensional feature space is then found as in (\ref{eq:projection}), where ${\bf
-p}$ contains the coordinates in the $N$ dimensional space with ${\bf 0}$-origin,
+The projection from the original $2n$-dimensional feature space $(n=70)$ to an
+$N$-dimensional space is found as in (\ref{eq:projection}), where ${\bf p}$
+contains the coordinates in the $N$ dimensional space with ${\bf 0}$-origin,
 calculated as in (\ref{eq:paramCalc}). The $2n\times N$ matrix ${\bf \Phi }$ is
-an orthogonal matrix composed of the eigenvectors ${\bf v}_i$ of the covariance
-matrix of the observations which correspond to the largest $N$ eigenvalues
-($\lambda_i$), as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}.
+an orthogonal matrix composed of the eigenvectors ${\bf v}_i$ corresponding to
+the largest $N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
+observations, as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}. As such,
+each shape may be approximated by the mean shape plus a sum of the top $N$
+eigenvectors, weighted by the parameter vector $p$.
 
@@
 
-If $N = 2n$, the projection will be nothing more than a change of basis, however
-if there is correlation between the points in the observations, there will be
-eigenvalues of the covariance matrix which are close to zero, and so removing
+If there is correlation between the points in the observations, there will be
+eigenvalues of the covariance matrix which are close to zero. As such, removing
 the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
@@
 
-Paths of a particular letter have been clustered using K-means clustering to
-group different styles of writing the letter (\emph{allographs}), such that the
-parameters in the resulting model are only representative of the specific
-allograph of the letter in the dataset. PCA has been performed on all of the
-paths of a particular allograph in the dataset at a time, to reduce the $2n$
-dimensional space to one of a desired number of dimensions. This process may be
-considered to generate a shape model in that (\ref{eq:projection}) may be used
+For the dataset presented in Figure \ref{fig:deviations_sPrint}, the
+eigenvectors associated with the 5 largest eigenvalues explain 90.0\% of the
+variance in the dataset, illustrating the capability of the statistical shape
+modelling approach to produce compact parameterisation of shapes.
+
+Clusters within paths of a particular letter have been identified using K-means
+clustering to group different styles of writing the letter (\emph{allographs}),
+such that the parameters in the resulting model are only representative of the
+specific allograph of the letter in the dataset. 
+% * <deanna.m.hood@gmail.com> 2014-09-03T13:05:23.576Z:
+%
+% in the end this was pointless so maybe not worth mentioning
+%
+PCA has been performed on all of the paths of a particular allograph in the
+dataset at a time, to reduce the $2n$ dimensional space to one of a desired
+number of dimensions.
+
+(\ref{eq:projection}) may be used
 to generate new shapes based on the parameters ${\bf p}$ which are used: ${\bf
@@
 \subfigure{
-\raisebox{-0.5\height}{\includegraphics[width=0.07\textwidth]{figures/sPrint_mean.png}
+\raisebox{-0.5\height}{\includegraphics[width=0.05\textwidth]{figures/sPrint_mean.png}
 }}
 \subfigure{
-\raisebox{-0.5\height}{\includegraphics[width=0.38\textwidth]{figures/sPrint.png}
+\raisebox{-0.5\height}{\includegraphics[width=0.35\textwidth]{figures/sPrint_top3.png}
 }}
-\caption[The mean shape and the effect of varying the first five parameters of
+\caption[The mean shape and the effect of varying the first three parameters of
 the shape model derived from PCA from the dataset of print `s'
 shapes.]{\label{fig:deviations_sPrint}The mean shape (left) and the effect
-(right) of varying the first five parameters (each row) of the shape model
-derived from PCA from the first cluster of `s' shapes, interpreted as the print
-allograph. The percentage of the total variance in the dataset explained by each
-parameter is shown on the appropriate row. }
+    (right) of varying the first three parameters (each row) of a shape model.
+    The presented model has been derived from PCA on the first cluster of `s'
+    shapes, interpreted as the print allograph. The extent to which each
+parameter is varied is dependent on the eigenvector $\lambda$ corresponding to
+the parameter's eigenvector. The percentage of the total variance in the dataset
+explained by each parameter is shown to the left of the corresponding row. }
 
@@
 
-Interestingly, the parameters which result from the unsupervised statistical
-shape analysis, to some extent, represent variations which could intuitively be
-identified by a manual parameterisation: the gap in the top half of the letter
-compared to the bottom half, the width of the top half of the letter compared to
-the bottom half, the width of the overall shape, etc., and as a result the shape
-modelling has produced the desired outcomes in terms of parameterising the
-shapes in ways which are able to be used to deform them meaningfully.
+Interestingly, although the parameters are the result of an \emph{unsupervised}
+statistical shape analysis, they still represent variations which could have
+been intuitively identified by a manual parameterisation. For example, for the
+model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
+the width of the top half of the letter compared to the bottom half, the width
+of the overall shape, etc. Consequently, the shape modelling process has
+produced the desired outcomes of parameterising the shapes in ways which are
+able to be used to deform them meaningfully.
 
@@
 
-After determining the appropriate number of dimensions (N) of the data
-representing the majority of the variance observed within different samples of a
-letter in the dataset, new letters can be generated by varying the parameter
-values in this N dimensional space in accordance with (\ref{eq:projection}). By
-choosing parameter values which lie within the observed range in the dataset, it
-is possible to produce letters which are more likely to be reasonable looking.
+After determining the appropriate number of dimensions ($N$) for the shape
+models, new letters can be generated by varying the parameter values in this
+$N$-dimensional space in accordance with (\ref{eq:projection}). By choosing
+parameter values which lie within the observed range in the dataset, it is
+possible to produce letters which are more likely to be reasonable looking.
 When the parameter values are outside of the range observed in the dataset, they
@@
 Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
-models of `e' and `g' - made from 120 observations with 70 points - by selecting
-random values for the first 5 parameters from a distribution with standard
-deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$ standard
-deviation observed in the dataset.
+models of `e' and `g' - made from 120 observations each, with 70 sample points -
+by selecting random values for the first 5 parameters from a distribution with
+standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
+standard deviation observed in the dataset.
 
@@
 
-It is therefore feasible that `poor' letters can be produced using the shape
-model generated from a dataset of adults' writing with PCA. In
-\cite{Chandra2013}, it was found that children aged 4-6 participating in a
-handwriting peer tutoring pilot study most often made mistakes classified as
-inappropriate \emph{internal proportions} or \emph{global deformations}, and it
+In \cite{Chandra2013}, it was found that children aged 4-6 years participating
+in a handwriting peer tutoring pilot study most often made mistakes classified
+as inappropriate \emph{internal proportions} or \emph{global deformations}. It
 would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
-the same general categories. Consequently, while using a database of children's
-letters when available may yield potential for parameterising other mistakes
-made by children, such as merging strokes or decomposing a shape into multiple
-subparts inappropriately, sufficient capabilities for the shape model to
-generate shapes given parameter variations which are appropriate for simulating
-a na\"ive learning in the context of handwriting have been demonstrated.
+the same general categories. Using a database of children's letters when
+available may yield potential for parameterising other mistakes made by
+children, such as merging strokes or decomposing a shape into multiple subparts
+inappropriately. Nevertheless, sufficient capabilities for the shape model to
+generate `poor' letters which are appropriate for simulating a na\"ive learning
+in the context of handwriting have been demonstrated, using the shape model
+generated with PCA from a dataset of only adults' writing.
 
@@
 
-In the same way that the shape model of a particular letter can be used to take
-parameters and generate a letter, in the case of the statistical shape model
-presented in Section \ref{sec:writingGeneration}, it may also be used to take a
-letter and determine its parameters given the model. The potential for the
-parameters of a user-drawn shape to be obtained from the shape model have been
-capitalised on to incorporate the capabilities for the learning algorithm to
-adapt to the user's feedback via demonstration.
+It was shown in Section \ref{sec:writingGeneration} how the statistical shape
+model of a particular letter may convert a set of parameters into a generated
+letter of the same allograph. Similarly, the model may also be used to convert a
+letter into its parameters, given the model. The parameters of user-drawn
+letters may therefore be used in order to incorporate the capabilities for the
+learning algorithm to adapt to the user's feedback via demonstration.
 
@@
 lower-dimensional space determined by the model. Mathematically, given a
-demonstration ${\bf x}$, the associated parameters may be determined as in
+demonstration ${\bf x}_{demo}$, the associated parameters may be determined as in
 (\ref{eq:param}).
@@
 \begin{equation}\label{eq:param}
-{\bf p}_{demo} ={\bf \Phi}^T ({\bf {x}-\bar{x}})
+{\bf p}_{demo} ={\bf \Phi}^T ({\bf{x}_{demo}-\bar{x}})
 \end{equation}
 
-The parameters which are determined for a shape will not reconstruct the shape
-exactly, but rather will reconstruct the closest point in the N dimensional
-space which the eigenvectors span. With increasing value of N, the reconstructed
-shape will be closer to the original shape, until N is equal to the number of
-dimensions of the original shape, at which point there is no error incurred by
-`projecting' onto the N dimensional space as the space is the same (but perhaps
-with a different basis).
+The parameters which are determined for a shape in (\ref{eq:param}) will not
+reconstruct the shape exactly if $N<2n$, but rather will reconstruct the closest
+point in the $N$-dimensional space which the eigenvectors span. $N=10$ has been
+used for the work presented.
 
@@
 p}^{(k)})\times\alpha\] has been used, where ${\bf p}$ is the parameter vector
-and $k$ is the time step, and $\alpha$ is the learning rate, between 0 and 1.
-While it is possible that the resulting ${\bf p}^{(k+1)}$ yields an unacceptable
-shape from combining ${\bf p}^{(k)}$ and ${\bf p}_{demo}$ which individually
-yield acceptable shapes, what is significant about the proposed method for
-adapting to user demonstration is that even it does not get stuck at such poor
-shapes: with further demonstrations of the same letter, the system would
-eventually approach it. It remains to be seen what the impact of such a poor
-in-between shape being drawn by the teachable agent would have on the
-interaction with the user, however, and how - if necessary - to avoid such an
-event mathematically.
-
-Further research may discover how to best model/limit the learning speed of the
-robot so that it is noticeably learning while not improving so fast as to limit
-the long-term interaction potential for the system, which may turn out to be
-child-dependent.
+at time step $k$, and $\alpha$ is the learning rate, between 0 and 1.  It is
+possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
+individually yield acceptable shapes, may produce parameters ${\bf p}^{(k+1)}$
+which yield an unacceptable shape. The proposed method for adapting to user
+demonstration would not get stuck at such poor shapes, however: with further
+demonstrations of the same letter, the system would eventually approach it. As a
+result, this event would not limit the interaction proposed in Section
+\ref{sec:experiment}, but it may influence the user's perception of the learning
+agent. It remains to be seen if it is necessary to avoid such an event
+mathematically.
 
@@
 
+% * <deanna.m.hood@gmail.com> 2014-09-04T09:19:16.057Z:
+%
+% improve img
+%
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 In order to develop a teachable agent that is appropriate for engaging a child
-through the learning by teaching paradigm - that is, that it is an embodied
-agent, capable of eliciting motor mimicry, and capable of causing its teacher to
-reflect on the process that has been used to respond to handwriting feedback -
+through the learning by teaching paradigm, 
+%- that is, that it is an embodied agent, capable of eliciting motor mimicry,
+%and capable of causing its teacher to reflect on the process that has been used
+%to respond to handwriting feedback -
 capabilities for the robot to engage in handwriting have been established.
@@
 
-Because of the challenges in getting the Nao to write trajectories smoothly
-because of its inherent ability to only reach discrete points in space, it has
-been implemented instead that the robot uses simulated handwriting, as an
-opportunity to have finer control over the robot's writing. The necessary
-components to accomplish such are to:
+%Because of the challenges in getting the Nao to write trajectories smoothly
+%because of its inherent ability to only reach discrete points in space, 
+A fine level of control over what the robot is writing is necessary in the
+proposed application of a learning agent in the context of handwriting. Because
+of the limited fine motor skills possible with such an affordable robot, in
+addition to the absence of force feedback and other technical necessities, the
+Nao has been configured to use simulated handwriting with a synchronised tablet
+to achieve this level of control. The necessary components of implementing the
+proposed teachable robotic agent are, therefore:
 
 \begin{enumerate}
-    \item develop capabilities for the robot to trace handwriting,
+    \item developing capabilities for the robot to trace handwriting,
 
-    \item synchronise the robot's movements with the display of the writing on a
+    \item synchronising the robot's movements with the display of the writing on a
         tablet so that it seems that the robot is causing the handwriting to
@@
 
-    \item integrate the writing behaviour with the handwriting learning
+    \item integrating the writing behaviour with the handwriting learning
         algorithm presented in Section \ref{sec:learningAlgorithm} to create a
-        learning by teaching interaction with the agent. 
+        \emph{learning by teaching} interaction with the agent. 
 \end{enumerate}
 
-These steps are presented in the sections that follow.
+These steps are presented in the sections which follow.
 
@@
 
-As previously mentioned, the robot used in this system does not have
-capabilities to reach all points in space due to its physical limitations
-(finite degrees of freedom). Using simulated handwriting will not do anything to
-fix this physical limitation, but it provides a context where the path traced by
-the robot can be displayed smoother than it would have otherwise appeared if
-written with a writing instrument. For believability, however, it is still
-necessary that the robot's trajectory is close enough to that which is
-displayed. As such, the requirements on the robot's fine motor skills are
-lessened but not removed.
+Using simulated handwriting provides an opportunity for the robot's writing to
+appear smoother than would be achievable with a writing instrument. However, the
+robot's motions must still sufficiently match the displayed trajectory in order
+capture the engagement of the child user in the action.
 
 Aldebaran's NaoQi API has been used for the inverse kinematics of the trajectory
-following. It provides the advantage of allowing the whole body to be used in
-the inverse kinematics rather than simply the arm, which yields to an increased
-working space of the robot. However, as motion planning is performed with
-respect to the centre of the hand of the robot as opposed to the tip of a
-writing instrument, restrictions on the orientation of the hand must be put in
-place such that the writing instrument remains with the appropriate orientation
-to the writing surface.
+following. The Robot Operating System (ROS)\footnote{The ROS stack for Nao is
+available at: \url{http://wiki.ros.org/nao_robot}} has been used for integration
+of the Nao with external reference frames using the $tf$ transformation library
+\cite{Foote2013}, such as the tablet's location.
 
-When pretending to write with a writing instrument, the requirement that the
-instrument tip match the trajectory is still significant, and therefore any
-change in orientation of the hand is exaggerated at the writing tip.
-
-Rather than have the robot write with a writing instrument on a horizontal
-surface, by instead having it point at a vertical writing surface to cause the
+When using simulated handwriting, it is no longer necessary that the robot
+engages in the typical style of handwriting with a writing instrument at a desk.
+By instead having the robot point at a vertical writing surface to cause the
 trajectory to appear (as in Figure \ref{fig:naoWriting}), several advantages are
@@
     \item Concerns about whether or not the child would start mimicking the
-        robot's incorrect (inhuman) writing style are mitigated. However, there
-        is a possibility that this would also reduce the potential for students
-        to benefit from motor imitation, although it is hypothesised that motor
-        imitation is caused more from the overall concept of the trajectory
-        being shown than from the pen grip being used.
+        robot's incorrect (inhuman) writing style are mitigated. % * <deanna.m.hood@gmail.com> 2014-09-04T09:59:44.707Z:
+%
+% is this point significant enough?
+%
 
@@
         critical, because the finger is not expected to touch the tablet exactly
-        at the trajectory point, in contrast to the pen tip. This means that
-        orientation degrees of freedom can be freed without significant adverse
-        effects.
+        at the trajectory point, in contrast to the pen tip.
+        % This means that orientation degrees of freedom can be freed without significant adverse effects.
 
@@
     \end{center}
-    \caption{A demonstration of the robot simulating the drawing of a word
-        with its finger, synchronised with the tablet, communicating over ROS.
+    \caption{A demonstration of the robot simulating the writing of a word
+        with its finger. The motion of the robot is synchronised with the display of the tablet, communicating over ROS.
      }%
@@
 
-Therefore the system presented utilises the context where the robot is
+Therefore, the system presented utilises the context where the robot is
 simulating handwriting by pointing at the tablet\footnote{Teachers interviewed
 for their feedback on the system advised that children are asked to draw letters
-in the air in a similar manner as part of their handwriting education.}.
+in the air in a similar manner as part of their handwriting education.}. Because
+motion planning is performed with respect to the hand of the robot, rather than
+its fingertip, the one or two of the orientation degrees of freedom of the hand
+are fixed to keep the finger approximately perpendicular to the writing surface,
+depending on the desired accuracy. The remaining free orientation(s), coupled
+with the whole-body motion control available, allow for a sufficient working
+space for writing on the entire tablet.
 
-\subsection{Synchronisation with the Tablet Trajectory Display}
+\subsection{Synchronisation with the Tablet Trajectory Display}\label{sec:tabletSynch}
 
@@
 simulated handwriting is getting the trajectories of the robot's `writing' to
-display on an Android tablet instead of being displayed in the RViz
-visualisation tool running on the computer.
+display on an Android tablet.
 
-ROS has been used to connect the devices used in the system, including the
-Android tablet\footnote{For more information about ROS on Android devices see
-\url{http://wiki.ros.org/android}}. As a result, aspects of the networking
-between the tablet and the robot, such as the overheads associated with
-connections, ports, message formats, publishers/subscribers, etc. have already
-been implemented.
+ROS has been used for the communication between the devices used in the system,
+including the Android tablet\footnote{For more information about ROS on Android
+devices see \url{http://wiki.ros.org/android}}. As a result, aspects of the
+networking between the tablet and the robot, such as the overheads associated
+with connections, ports, message formats, etc. have been simplified.
 
@@
 a ROS topic and add each point of the trajectory one by one as a frame of an
-animation. Synchronisation between the tablet and the robot has been achieved by
+animation. Synchronisation between the tablet and the robot has been achieved by:
 
@@
     \item reducing the number of points along the trajectory passed to the
-        robot's motion planner, as the more points, the more the robot gets out
-        of synch with the requested timings, and
+        robot's motion planner, to improve timing accuracy, and
 
@@
 
-%\subsection{Integration and Synchronisation}
-
 To instruct the robot where to write, the robot has been configured to detect a
@@
 \url{https://github.com/chili-epfl/ros_markers} for more information on the
-fiducial marker detection node used.}, with the camera located in its head and
-use that as the origin of the writing surface (Figure
-\ref{fig:tabletDetection}). As publishing the robot's camera has been identified
-as a computationally expensive task that can disrupt the robot's timing of
-synchronised writing, it is only done when necessary and the tablet is assumed
-to be stationary during the writing process.
+fiducial markers used.}, with the camera located in its head and use that as the
+origin of the writing surface (Figure \ref{fig:tabletDetection}). When used in
+an interaction with a child, this allows the user to move the tablet as required
+for the interaction. As publishing the robot's camera has been identified as a
+computationally expensive task which can disrupt the robot's timing of
+synchronised writing, it is only done when the robot is not writing, and the
+tablet is assumed to be stationary during the writing process.
 
@@
 
-\end{figure}
+\end{figure}% * <deanna.m.hood@gmail.com> 2014-09-04T11:21:59.328Z:
+%
+% this image is pretty bad, and doesn't add much
+%
 
@@
 \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the
-demonstration. }. As a result, the two relevant orientations of the hand were
-fixed to keep the finger perpendicular to the writing surface, with the
-remaining orientation free such that the wrist could rotate in order to easier
-reach the points along the path. The use of whole body motion may be seen in
-this demonstration, as the robot's centre of gravity is shifted to prevent the
-wrist from rotating towards the centre of the robot, in which case the fingertip
-would not match the writing trajectory. Without whole body motion control, it
-would not have been possible to execute such a trajectory using only the degrees
-of freedom in the arm.
+demonstration. }. % * <deanna.m.hood@gmail.com> 2014-09-04T11:40:30.176Z:
+%
+% this sounds dumb on paper.....
+%
 
@@
 
-The fusion of the handwriting learning algorithm presented in Section
-\ref{sec:learningAlgorithm} with the embodied handwriting agent developed
-involves the integration of three components: the controller of the learning
-algorithm, running on a computer, which manages the learning algorithm,
-responding appropriate to feedback received, and publishes the shapes to be
-drawn with their time and relevant position with respect to the writing surface;
-the robot which draws the requested letters; and the application running on an
-Android tablet which draws the requested letters in synch with the robot and
-displays the result to the user, and acts as the medium for the user's feedback,
-through touch gestures and user-drawn demonstrations.
+The fusion of the embodied handwriting agent developed with the handwriting
+learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
+integration of three components. The robot and Android tablet application
+present the writing process/result to the user, as in Section
+\ref{sec:tabletSynch}. Furthermore, the tablet application is extended to act as
+the primary medium for capturing user interaction, and publishes the user's
+demonstrations when user is satisfied with their writing. The user
+demonstrations are received by an interaction controller, running on a desktop
+computer. It is responsible for getting the Nao to prompt and respond
+appropriately to feedback received using a finite state machine to manage the
+interaction stage. It also manages the learning algorithm, by inferring the
+letter which user demonstrations are for, based on their position on the tablet,
+and publish the shapes to be written which are generated by the learning
+algorithm in response to the feedback.
 
-Feedback from the user is passed to the controller with the location on the
-tablet that it occurred at, and the task of interpreting the shape which the
-feedback was intended for is left to the controller as it is aware of the
-location of published shapes. The appropriate response in terms of the learning
-algorithm is then taken for the respective shape.
+%Feedback from the user is passed to the controller with the location on the
+%tablet that it occurred at, and the task of interpreting the shape which the
+%feedback was intended for is left to the controller as it is aware of the
+%location of published shapes. The appropriate response in terms of the learning
+%algorithm is then taken for the respective shape.
 
@@
 such questions is one where participants are asked to improve the robot's
-handwriting by correcting its letters. Figure \ref{fig:pilotInteraction}
+handwriting by correcting its letters. Figure~\ref{fig:pilotInteraction}
 illustrates an example interaction sequence between the participant and the
@@
 with each other.
+
+Further research may discover how to best model/limit the learning speed of the
+robot so that it is noticeably learning while not improving so fast as to limit
+the long-term interaction potential for the system, which may turn out to be
+child-dependent.
 

### 2014-09-08 main.tex
Tuning, refining, improving

@@
 
-%%% HRI 2015 -> double-blind review process
-
 % \numberofauthors{3} 
@@
 \begin{abstract}
+% * <deanna.m.hood@gmail.com> 2014-09-05T11:44:33.364Z:
+%
+% capitalise inside the phrase?
+%
+
+%%% HRI 2015 -> double-blind review process
+
+% * <deanna.m.hood@gmail.com> 2014-09-05T11:44:54.921Z:
+%
+% Ana Paiva is a reviewer....
+%
 
@@
 
-Presented is a teachable humanoid agent in the context of handwriting skills
-acquisition. It is hypothesised that such a system could not just engage an
-unmotivated student, but could also present the opportunity for children to
-experience the typical benefits experienced during human-led handwriting
-interventions, such as motor mimicry. This system allows for exploring the
-potential for the \emph{learning by teaching} paradigm to be employed in the
-interaction, so as to stimulate meta-cognition, empathy and increased
-self-esteem in the child user.
+Presented is a robotic partner which children can teach handwriting. It is
+hypothesised that such a system could not just engage an unmotivated student,
+but could also present the opportunity for children to experience the typical
+benefits encountered during human-led handwriting interventions, such as motor
+mimicry. Moreover, this system allows for exploring the potential for the
+\emph{learning by teaching} paradigm to be employed in the interaction, so as to
+stimulate meta-cognition, empathy and increased self-esteem in the child user.
 
@@
 suitably embodied handwriting partner. Shape models derived from principal
-component analysis of a dataset of letter trajectories are generated and allow
+component analysis of a dataset of letter trajectories are generated, and allow
 the robot to draw purposefully deformed letters. Learning how to write
@@
 
-An in situ study has been conducted with primary school classes to obtain
+Preliminary in situ studies have been conducted with primary school classes to obtain
 insight into children's use of the novel system. 
@@
 %students in an interaction that will be sustainable over the long-term. 
-
 Successful interventions for children with handwriting difficulties involve the
@@
 meta-cognitive, and educational benefits in a range of disciplines
-\cite{Rohrbeck2003}. An application which is yet to be explored, however, is the
-application of learning by teaching to handwriting intervention. One reason why
-this has not been investigated to date is that in order to engage a child in the
-learning by teaching paradigm, there must be an appropriately unskilled peer for
-them to tutor. In the context where the target child is the lowest performer in
-their class, this may be a constraint. In some cases it may be appropriate for a
+\cite{Rohrbeck2003}. An application which is yet to be explored, however, is
+that of handwriting intervention. One reason why this has not been investigated
+to date may be that in order to engage a child in the learning by teaching
+paradigm, there must be an appropriately unskilled peer for them to tutor. In
+the context where the target child is the lowest performer in their class, this
+may present a logistical constraint. In some cases, it may be appropriate for a
 peer or teacher to simulate a na\"ive learner for the target child to teach,
@@
 a variety of skill levels, and for which children do not have preconceptions
-about its handwriting ability.
+about handwriting ability.
 
-Presented is the development of the first known learning agent which is capable
+Presented is the development of the first known teachable agent which is capable
 of artificially making mistakes typical of children learning handwriting, and
@@
 There are three main points which have motivated the use of a robot as the
-teachable agent in the presented interaction:
+teachable agent in the presented work:
 
@@
         tablet-based application, which children are increasingly recognising as
-        disposable technology,
+        disposable technology,% * <deanna.m.hood@gmail.com> 2014-09-08T11:07:10.004Z:
+%
+% ... citation needed?
+%
 
     \item observing a teachable agent respond to what it has been taught
-        \cite{Okita2006} is a significant step in the learning by teaching
-        paradigm, and therefore it may be significant for the agent to respond
+        is a significant step in the learning by teaching
+        paradigm \cite{Okita2006}, and therefore it may be significant for the agent to respond
         with a writing \emph{process}, rather than simply a product, and
@@
 otherwise infeasible for the robot. 
+% * <deanna.m.hood@gmail.com> 2014-09-08T11:08:36.426Z:
+%
+% linking sentence...
+%
 
 Section \ref{sec:learningAlgorithm} presents the novel work in the area of
-artificial intelligence to develop a learning algorithm suitable for a learning
+artificial intelligence to develop a learning algorithm suitable for a teachable
 agent in the context of handwriting.  Section \ref{sec:robotWriting} details the
@@
 novel approach for achieving simulated fine motor skills on commercially
-affordable humanoid robots.  Section \ref{sec:experiment} explores the novel
+affordable humanoid robots.  Section \ref{sec:experiment} explores the novel% * <deanna.m.hood@gmail.com> 2014-09-08T11:09:28.480Z:
+%
+% use a different word
+%
 contributions made to the study of human-robot interaction, in discussing the
@@
 
-Because of the objective to use an artificial intelligence algorithm in a
-reinforcement learning framework, a parameterisation of letters and their
-deformities has been sought. Depending on the parameters input to the letter
-models, different quality shapes can be generated. The system can therefore be
-configured to improve its writing by modifying the parameters used to generate
-the letters, based on feedback from the reinforcement learning partner. To this
-end, a method which can generate a model from real-world data has been employed
-in order to capture realistic variations in letters.
+For the development of a reinforcement learning algorithm in the context of
+handwriting, a parameterisation of letters and their deformities has been sought
+to generate the necessary letter models. Depending on the parameters input to
+the letter models, different quality shapes can be generated. The system can
+therefore be configured to improve its writing by modifying the parameters used
+to generate the letters, based on feedback from the reinforcement learning
+partner. To this end, a method which can generate a model from real-world data
+has been employed in order to capture realistic variations in letters.
 
@@
 One approach for a shape model which can appropriately represent realistic
-variations in shapes with changes to its parameters is statistical shape
+variations in shapes is statistical shape
 modelling. Statistical shape modelling is an application of principle component
@@
 $N$-dimensional space is found as in (\ref{eq:projection}), where ${\bf p}$
-contains the coordinates in the $N$ dimensional space with ${\bf 0}$-origin,
+contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
 calculated as in (\ref{eq:paramCalc}). The $2n\times N$ matrix ${\bf \Phi }$ is
@@
 PCA has been performed on all of the paths of a particular allograph in the
-dataset at a time, to reduce the $2n$ dimensional space to one of a desired
+dataset at a time, to reduce the $2n$-dimensional space to one of a desired
 number of dimensions.
 
-(\ref{eq:projection}) may be used
+(\ref{eq:projection}) may also be used
 to generate new shapes based on the parameters ${\bf p}$ which are used: ${\bf
@@
 
-In \cite{Chandra2013}, it was found that children aged 4-6 years participating
+In \cite{Chandra2013}, it was found that children aged 4-6 years participating% * <deanna.m.hood@gmail.com> 2014-09-05T11:43:42.851Z:
+%
+% this is not peer-reviewed!
+%
 in a handwriting peer tutoring pilot study most often made mistakes classified
@@
 \begin{equation}\label{eq:param}
-{\bf p}_{demo} ={\bf \Phi}^T ({\bf{x}_{demo}-\bar{x}})
+{\bf p}_{demo} ={\bf \Phi}^T ({\bf{x}_{demo}}-\bf{\bar{x}})
 \end{equation}
@@
 responding to user demonstrations is to move the learning algorithm's parameters
-towards those of the demonstration to some extent. In the results presented in
-this work, \[{\bf p}^{(k+1)} = {\bf p}^{(k)} + ({\bf p}_{demo}-{\bf
-p}^{(k)})\times\alpha\] has been used, where ${\bf p}$ is the parameter vector
-at time step $k$, and $\alpha$ is the learning rate, between 0 and 1.  It is
-possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
+towards those of the demonstration. In the results presented in this work, the
+update equation shown in \ref{eq:update} has been used, where ${\bf p}$ is the
+learned parameter vector at time step $k$, and $\alpha$ is the learning rate,
+between 0 and 1.
+
+\begin{equation}\label{eq:update}
+{\bf p}^{(k+1)} = {\bf p}^{(k)} + ({\bf p}_{demo}-{\bf
+p}^{(k)})\times\alpha
+\end{equation}
+
+It is possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
 individually yield acceptable shapes, may produce parameters ${\bf p}^{(k+1)}$
-which yield an unacceptable shape. The proposed method for adapting to user
+by which yield an unacceptable shape. The proposed method for adapting to user
 demonstration would not get stuck at such poor shapes, however: with further
-demonstrations of the same letter, the system would eventually approach it. As a
-result, this event would not limit the interaction proposed in Section
-\ref{sec:experiment}, but it may influence the user's perception of the learning
+demonstrations of the same letter, the system would eventually approach the
+demonstration shape. As a result, the event of poor-looking intermediate letters
+would not limit the interaction later proposed in Section \ref{sec:experiment}
+in a technical sense, but it may influence the user's perception of the learning
 agent. It remains to be seen if it is necessary to avoid such an event
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{An Embodied Handwriting Learning Agent with the Nao Humanoid Robot} \label{sec:robotWriting}
+\section{An Embodied Handwriting Learning Agent with the Nao Humanoid Robot}
+\label{sec:robotWriting}
 
@@
 robot's motions must still sufficiently match the displayed trajectory in order
-capture the engagement of the child user in the action.
-
-Aldebaran's NaoQi API has been used for the inverse kinematics of the trajectory
-following. The Robot Operating System (ROS)\footnote{The ROS stack for Nao is
-available at: \url{http://wiki.ros.org/nao_robot}} has been used for integration
-of the Nao with external reference frames using the $tf$ transformation library
+capture the engagement of the child user in the action. Aldebaran's NaoQi API
+has been used for the inverse kinematics of the trajectory following. The Robot
+Operating System (ROS)\footnote{The ROS stack for Nao is available at:
+\url{http://wiki.ros.org/nao_robot}} has been used for integration of the Nao
+with external reference frames using the $tf$ transformation library
 \cite{Foote2013}, such as the tablet's location.
@@
 When using simulated handwriting, it is no longer necessary that the robot
-engages in the typical style of handwriting with a writing instrument at a desk.
+engages in the typical style of handwriting, with a writing instrument at a desk.
 By instead having the robot point at a vertical writing surface to cause the
@@
         critical, because the finger is not expected to touch the tablet exactly
-        at the trajectory point, in contrast to the pen tip.
+        at the trajectory point, in contrast to a pen tip.
         % This means that orientation degrees of freedom can be freed without significant adverse effects.
@@
     \end{center}
-    \caption{A demonstration of the robot simulating the writing of a word
-        with its finger. The motion of the robot is synchronised with the display of the tablet, communicating over ROS.
-     }%
+    \caption{A demonstration of the robot simulating the writing of a word with
+    its finger. The motion of the robot is synchronised with the display of the
+    tablet, communicating over ROS.}%
 
@@
 for their feedback on the system advised that children are asked to draw letters
-in the air in a similar manner as part of their handwriting education.}. Because
+in the air in a similar manner as part of their handwriting education.}. As
+interacting with a tablet with one's finger is not uncommon, this may aid the
+acceptance of the writing style by users.
+
+Because
 motion planning is performed with respect to the hand of the robot, rather than
-its fingertip, the one or two of the orientation degrees of freedom of the hand
+its fingertip, one or two of the orientation degrees of freedom of the hand
 are fixed to keep the finger approximately perpendicular to the writing surface,
@@
 \url{https://github.com/chili-epfl/ros_markers} for more information on the
-fiducial markers used.}, with the camera located in its head and use that as the
-origin of the writing surface (Figure \ref{fig:tabletDetection}). When used in
-an interaction with a child, this allows the user to move the tablet as required
-for the interaction. As publishing the robot's camera has been identified as a
-computationally expensive task which can disrupt the robot's timing of
-synchronised writing, it is only done when the robot is not writing, and the
-tablet is assumed to be stationary during the writing process.
+fiducial markers used.}, with the camera located in its head, and use that to
+determine the relative position of the writing surface (Figure
+\ref{fig:tabletDetection}). When used in an interaction involving a user, this
+allows a user to move the tablet as required for the interaction. As publishing
+the robot's camera has been identified as a computationally expensive task which
+can disrupt the robot's timing of synchronised writing, it is only done when the
+robot is not writing, and the tablet is assumed to be stationary during the
+writing process.
 
@@
 learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
-integration of three components. The robot and Android tablet application
-present the writing process/result to the user, as in Section
-\ref{sec:tabletSynch}. Furthermore, the tablet application is extended to act as
-the primary medium for capturing user interaction, and publishes the user's
-demonstrations when user is satisfied with their writing. The user
-demonstrations are received by an interaction controller, running on a desktop
-computer. It is responsible for getting the Nao to prompt and respond
-appropriately to feedback received using a finite state machine to manage the
-interaction stage. It also manages the learning algorithm, by inferring the
-letter which user demonstrations are for, based on their position on the tablet,
-and publish the shapes to be written which are generated by the learning
-algorithm in response to the feedback.
+integration of three components: the robot, the tablet, and a centralised controller. % * <deanna.m.hood@gmail.com> 2014-09-08T12:03:16.473Z:
+%
+% centralised is the right word yeah? all messages pass through the controller
+%
+The robot and Android tablet application present the writing process/result to
+the user, as in Section \ref{sec:tabletSynch}. Furthermore, the tablet
+application is extended to act as the primary medium for capturing user
+interaction, and publishes the user's demonstrations when user is satisfied with
+their writing. The user demonstrations are received by the interaction
+controller, running on a desktop computer. It is responsible for getting the Nao
+to prompt and respond appropriately to feedback received, using a finite state
+machine to manage the interaction stage and various system inputs. It also
+manages the learning algorithm, by inferring the letter which user
+demonstrations are for, based on their position on the tablet, and publishes the
+shapes to be written which are generated by the learning algorithm in response
+to the feedback.
 
@@
 
-In addition to constituting a technically novel system, the teachable robotic
-agent presented represents a tool which may be used for investigating social and
-pedagogical research questions. One such question that is being worked towards
-is what impact to the outcomes of a handwriting intervention the addition of
-such a teachable robotic agent would have.
+In addition to constituting a technically novel system, the presented teachable
+robotic agent represents a tool which may be used for investigating social and
+pedagogical research questions. One such question is what impact the addition of
+such a teachable robotic agent would have on the outcomes of a typical
+handwriting intervention.
 
-%\subsection{Interaction Context}
+\subsection{Interaction Context}
 
 The interaction context which has been developed as a framework for addressing
-such questions is one where participants are asked to improve the robot's
+relevant research questions is one where participants are asked to improve the robot's
 handwriting by correcting its letters. Figure~\ref{fig:pilotInteraction}
@@
 
-    \item The participant shows the robot one of five different 3-letter words
+    \item The participant shows the robot one of seven different 3-letter words
         to write, which, combined, consist of 7 different letters (`c', `e',
-        `n', `o', `s', `u', `w'). Fiducial markers placed on the word cards to
-        allow for detection with a camera.
+        `n', `o', `s', `u', `w'). Fiducial markers which are printed on the word
+        cards allow them to be detected with the robot's camera.
 
-    \item The robot responds to the word request verbally and writes the letters
-        by pointing at the tablet - placed in front of it with a vertical
-        orientation - and imitating tracing the letters as they appear
-        simultaneously by being displayed by the tablet.
+    \item The robot responds to the word request verbally, and writes the
+        letters by pointing at the tablet and imitating tracing the letters. The
+        tablet, placed in front of the robot with a vertical orientation,
+        displays the letters in synchronisation with the robot's movements.
 
@@
         how to write the letter which they feel needs to be corrected. The
-        demonstration is performed by drawing on the tablet with a stylus,
-        either with the tablet still in a vertical orientation or by unfolding
-        the stand and laying the tablet flat on the desk. The position of the
-        participant's demonstration on the tablet encodes the shape letter that
-        it is a demonstration for. The participant can clear their shapes if
-        they are unhappy with them or they are in the wrong position. When the
-        button to signal that it is the robot's turn is pressed, the
+        demonstration is performed by drawing on the tablet with a stylus. The
+        tablet may be moved into the most appropriate position for the child to
+        write on it. Only one letter may be demonstrated at a time, and the
+        position of the participant's demonstration on the tablet encodes the
+        letter that it is a demonstration for. The participant can remove and
+        repeat their letter if they are unhappy with it.
+        %, or if it is in the wrong position as determined by the researcher
+        %conducting the interaction
+        When the participant is satisfied with the demonstration, a button on
+        the tablet which signals that it is the robot's turn is pressed, and the
         demonstration is sent to the controller.
 
-    \item The interaction iterates, with participants taking turns to interact
-        with the robot.
+    \item The controller produces an adapted letter for the robot to write in
+        response to the participant's feedback, and the interaction iterates,
+        with participants taking turns to interact with the robot if necessary.
+        When the child is satisfied with the robot's performance on all letters,
+        they may use the ``test'' card and an additional word on which they will
+        verbally evaluate the robot's performance.
 
@@
         }~
-        \subfigure[The robot responds to the feedback and asks for more.]{%
+        \subfigure[The robot responds to the feedback, until the user is satisfied.]{%
             \label{fig:fourth}
@@
     \caption{%
-        A user interacting with the robot in the learning by teaching interaction using demonstrations.
-     }%
+        A user engaging with the robot in the \emph{learning by teaching}
+    interaction, using demonstrations as feedback.}%
+
    \label{fig:pilotInteraction}
@@
 
-%\subsection{Outcomes}
+\subsection{Outcomes of Preliminary Studies}% * <deanna.m.hood@gmail.com> 2014-09-05T08:43:38.105Z:
+%
+% I guess this is what we call the non-experiments.. Are the dates important?
+%
 
-A pilot study has been conducted to evaluate the interaction in preparation for
-an experiment to be conducted on the 10th-11th of June, 2014. The pilot study
-consisted of four groups of approximately 8 children, aged 6-7 years. Outcomes
-from the pilot study include information on how children interact with the
-system, sample letters written by children, opinions from the teachers involved,
-and insight into what experimental conditions might be appropriate for the
-experiment.
+Preliminary studies at two schools in the Geneva area have been conducted to
+evaluate the feasibility and technical soundness of the interaction system
+proposed. A pilot study at the first school consisted of four groups of
+approximately 8 english-speaking children, aged 6-7 years. The children
+interacted with the system for a total of 65 minutes, with the robot writing 96
+letters, 49 of which in response to demonstrations from the children.
 
-The system was validated, in that the learning algorithm and robotic writing
-were believed by the children, and that the system withstood the interaction for
-a total of 65 minutes, with the robot writing 96 letters, 49 of which in
-response to demonstrations from the children, during that time.
+As a result of the pilot study, two key observations were acted on. The first
+was that children appeared to have a difficult time providing demonstrations to
+the robot in the same place as previously-written letters. At the time, the
+system required the children to write ontop of a letter of the same type as the
+one which they were demonstrating, and the children seemed to find this
+counter-intuitive and would occasionally just trace the robot's letter as it
+appeared. As such, the technical components of the system were extended to allow
+the children the opportunity to write around previously-written letters instead
+of just ontop.
 
-Another key point which came from the pilot study is that children were observed
-giving advice to the child designated as the letter demonstrator, potentially
-giving rise to the higher level paradigm of learning by \emph{teaching to
-teach}.
+The second key point which came from the pilot study was that children were
+observed giving advice to the child designated as the letter demonstrator,
+potentially giving rise to the higher level paradigm of learning by
+\emph{teaching to teach}. As a consequence of this observation, the study which
+followed at the second school was designed to further observe the effect of the
+number of children interacting with the robot.
+%in order to investigate the potential of the system to not only be used to set
+%the context of children tutoring the robot, but also children interacting as
+%peer tutors with each other.
 
-%\begin{itemize}
+The study at the second school involved 21 french-speaking students: 7 children
+interacted with the robot by themselves, and 7 sessions included the remaining
+14 students interacting with the robot in pairs. The duration of the sessions
+was between 8 and 15 minutes, with an average of 11.4 minutes (standard
+deviation of 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
 %
-%\item Children would not intuitively write over the robot's letters, but rather
-%above them. When instructed to write over the robot's letter, some participants
-%would trace the letter as it had previously appeared as their demonstration. As
-%such, the requested demonstration positioning will be modified for the
-%experiment.
+% We prompted them when time was short, didn't we? Or did they just say test
+% whenever they wanted to...
 %
-%\item While children spoke to the robot each time it requested feedback -
-%suggesting that the anthropomorphised the robot - they also laughed when it
-%wrote letters which were incorrect, which may suggest that they had not
-%developed an empathetic connection with the robot by that point. 
+
+The following conclusions were successfully drawn about the system as a result
+of the study at the second school:
+
+\begin{itemize}% * <deanna.m.hood@gmail.com> 2014-09-05T09:34:46.545Z:
 %
-%\item Children were observed giving advice to the child designated as the
-%letter demonstrator, potentially giving rise to the higher level paradigm of
-%learning by teaching to teach. 
+% taking this out of bullet points gains extra space in paper if needed
 %
-%\end{itemize}
 
-As a consequence of this observation, the upcoming experiment will address the
-effect of the number of children interacting with the robot in order to
-investigate the potential of the system to not only be used to set the context
-of children tutoring the robot, but also children interacting as peer tutors
-with each other.
+    \item \textbf{The simulated robotic writing was believed by the children in all
+    cases.} There were, at times, 
+    % * <deanna.m.hood@gmail.com> 2014-09-05T11:59:03.640Z:
+    %
+    % how many
+    %
+    questions about the robot's writing method at the beginning of the interaction,
+    but when advised that the robot ``tells the tablet what it wants to write,''
+    this was accepted by the children. To allow the children an opportunity to
+    express doubt in the robot's ability to write without explicitly asking them if
+    the robot was pretending, the children were asking if they believed that the
+    robot would be able to write its name, \emph{Nao}, which had not previously been
+    demonstrated. It was reasoned that this would prompt the children to question
+    the point of the robot actually \emph{writing} if they had any concerns that
+    they were being fooled, but this was never the case. In the event where the
+    robot's writing was not synchronised with the tablet, this did not affect the
+    response of the child. If older children participate in the interaction study,
+    which may be likely as children with lasting handwriting difficulties are used
+    as participants, it may become more important to invest time into the
+    believability of the robot's writing scheme. however for 6-8 year olds the
+    proposed setup has been proven viable.
 
-Further research may discover how to best model/limit the learning speed of the
-robot so that it is noticeably learning while not improving so fast as to limit
-the long-term interaction potential for the system, which may turn out to be
-child-dependent.
+    \item \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
+    %
+    % maybe this is too strong as a 'conclusion' and should just be an observation. plus what does this even mean.. the child walking around the room was 'engaged' too...?
+    %
+    An average of 10.9 demonstration letters (standard deviation of 4.4) were
+    provided to the robot for each session during the interaction. Furthermore,
+    in 9 out of the 14 sessions (64\%), the robot received demonstration letters
+    \emph{after} reaching the test stage of the interaction. The participants'
+    teaching after the test word had been written and evaluated -- the only
+    purposefully imposed external motivation -- may suggest that by that time
+    the participants had become intrinsically motivated to engage in the
+    interaction.% * <deanna.m.hood@gmail.com> 2014-09-05T10:30:45.293Z:
+    %
+    % I guess it could have also come from us sitting there watching them
+    %
 
-%\section{ADDITIONAL REQUIREMENTS}
+    \item \textbf{All children believed that the robot was learning, and that
+        they were the ones teaching it.} This was concluded from their responses
+        when the children were asked directly. This is in contrast to a prior
+        feasibility study for a version of the interaction which only allowed
+        for touch-based feedback, not user demonstrations, in which three of the
+        seven adult participants did not feel that it was their input which
+        helped the robot improve.% * <deanna.m.hood@gmail.com>
+        2014-09-05T09:46:49.117Z:
+    %
+    % probably can't just casually mention this study without going into more detail...
+    %
+
+    %, and also their reaction to the ``test word'' written by the robot at the end of the interaction.
+In X\% of cases, the child concluded that the robot had `passed' the test, or congratulated it in some way.
+
+    \item \textbf{The system has been validated as a technically sound
+        autonomous interaction.} The interaction setup including the teachable
+        robotic agent withstood the interaction for a total of 160 minutes, with
+        the robot writing 335 letters, 152 of which in response to
+        demonstrations received from the 21 children. During this time, the
+        technical components of the system operated autonomously, with only the
+        verbal interaction being maintained by an observing researcher, and only
+        required intervention for the three instances that the robot fell later
+        in the day.% * <deanna.m.hood@gmail.com> 2014-09-05T10:49:26.786Z:
+    %
+    % could probably get away without mentioning this....
+    %
+
+\end{itemize}
+
+\subsection{Discussion}% * <deanna.m.hood@gmail.com> 2014-09-05T11:42:42.979Z:
+%
+% this is a reasonable title right?
+%
+
+In addition to the conclusions which 
+Anecdotes which raise questions:
+- "Would have problems with the 'n'" - (8) projecting human learning characteristics. Another said "programmed to write badly" (4)
+- Children saying the other was bad... (3, 9). Child saying the other child's was good (5). Child saying the robot was better than him (9).
+- When one child wrote u differently to the other, they didn't discuss :(
+- so many of them wanted to write the whole word.. robot says "show me a word" and maybe misleading
+- not seeming to notice small changes (12) but maybe from experimenter
+
+- awkward silence, speaking over the top of the robot to talk to experimenter....
+- child walking around
+- word very close to robot's camera
+
+Evidence of engagement:
+- work and/or play
+- once word was good were thinking for a long time about how to improve (8)
+- child `helping' other.. grabbing the pen
+- children trying to cheat the system (10)
+- excitement at stop and test cards - new letters? diff font
+- teaching cursive. group 7 excited to do this even after test finished.
+- unnecessary (unsent) demo from child 11 after it was acceptable but not perfect
 
@@
         capabilities, such as the Nao, to engage in the act of handwriting in a
-        way that is believable for interacting with children, which has been
+        way which is believable for interacting with children. This has been
         accomplished by leveraging simulated handwriting with a synchronised
@@
         fusing the robotic drawing capabilities and the learning algorithm for
-        handwritten letters established.
+        handwritten letters established with a central controller which manages
+        the flow of the interaction and turn taking, etc.
 
@@
 
-%By leveraging the technology of a wirelessly synchronised tablet displaying a
-%writing trajectory, the requirements for a robot with limited fine motor
-%capabilities to accurately manipulate a writing implement have been reduced to
-%instead requiring that the robot roughly trace the trajectory as it is
-%simultaneously displayed on the tablet. Thus, capabilities for the Nao to
-%engage in simulated handwriting have been demonstrated. By further lifting the
-%constraint that the robot must draw with a writing instrument and allowing it
-%instead to draw with its finger, in addition to increasing the range of
-%trajectories which the robot is able to reach, the necessary accuracy in the
-%robot's trajectory following is reduced as it is not necessary for the finger
-%to physically touch the writing surface at the trajectory position for the
-%simulation to be believable. As the motion control is currently limited to the
-%position of the robot's hand rather than the writing tip, the reduced need for
-%accurate motion in order to have a believable simulation was leveraged upon in
-%the presented system to produce results with the robot drawing with its finger
-%of sufficient accuracy.
+\subsection{Future Work}
 
-%Statistical shape modeling using principal component analysis on a dataset of
-%writing trajectories for a letter has been employed to generate shape models of
-%different letters/allographs. These models, generated through unsupervised
-%methods, have been shown to capture the internal proportions of letters in a
-%similar way to how human intuition would identify the possible shape variances
-%(width/height/proportional size of loops, skewness, etc.). As a result, the
-%models have been used to generate synthetic letters which yield shapes
-%appropriate for use in an artificial intelligence algorithm which uses user
-%feedback on the best letter from a set of candidates drawn to converge to the
-%parameter values of the selected shapes after some iterations.
-
-%The letter model has been used to determine the parameter values of shapes
-%demonstrated by the user. Provided that the user demonstrates the shape in the
-%same style as those used to generate the shape model (i.e., with the strokes in
-%the appropriate order and direction), the parameters of the demonstration may
-%then be used as input to the learning algorithm to converge towards the user's
-%writing demonstrations.
-
-%The fusion of the robotic drawing capabilities and the learning algorithm for
-%handwritten letters has resulted in a teachable robotic agent which can engage
-%users in the learning by teaching paradigm in the context of handwriting. As
-%such, the system developed has been shown to accomplish the technical goals
-%which were set out to be achieved, and the implications of such a system
-%evaluation of the system is underway, with an in situ interaction with primary
-%school students being conducted in the coming weeks.
-
-\subsection{Why a robot?}
-
-\subsection{Future Work}
+Further research may discover how to best model/limit the learning speed of the
+robot so that it is noticeably learning while not improving so fast as to limit
+the long-term interaction potential for the system, which may turn out to be
+child-dependent.
 
@@
 generate or learn a different shape topology) and technical (no support for
-multi-stroke shapes) limitations that need to be overcome.
+multi-stroke shapes) limitations which need to be overcome.
 
@@
 nominal protocol (presented in section~\ref{sec4}), and consequently still requires the
-presence of an experimenter. The robot state machine would require to be
+presence of an experimenter. The interaction state machine would require to be
 extended in non-trivial ways to allow for long, fully autonomous, interactions
 with children.
-
-%it may be interesting to investigate
-%which other technology could be incorporated into the system for a more fluid
-%interaction, such as integrating the user's gaze information to infer when the
-%user is finished with a demonstration, or using a classification algorithm to
-%determine which letter has been demonstrated irrespective of its positioning.
 

### 2014-09-09 main.tex
Added system diagram

@@
 \usepackage{subfigure}
-\usepackage[colorinlistoftodos]{todonotes}
+%\usepackage[colorinlistoftodos]{todonotes}
+
+\usepackage[usenames,dvipsnames]{xcolor}
+\usepackage{tikz}
+\usetikzlibrary{positioning, calc}
 
@@
 learning algorithm presented in Section \ref{sec:learningAlgorithm} involves the
-integration of three components: the robot, the tablet, and a centralised controller. % * <deanna.m.hood@gmail.com> 2014-09-08T12:03:16.473Z:
-%
-% centralised is the right word yeah? all messages pass through the controller
-%
-The robot and Android tablet application present the writing process/result to
-the user, as in Section \ref{sec:tabletSynch}. Furthermore, the tablet
-application is extended to act as the primary medium for capturing user
-interaction, and publishes the user's demonstrations when user is satisfied with
-their writing. The user demonstrations are received by the interaction
-controller, running on a desktop computer. It is responsible for getting the Nao
-to prompt and respond appropriately to feedback received, using a finite state
-machine to manage the interaction stage and various system inputs. It also
-manages the learning algorithm, by inferring the letter which user
-demonstrations are for, based on their position on the tablet, and publishes the
-shapes to be written which are generated by the learning algorithm in response
-to the feedback.
+integration of three components: the robot, the tablet, and a central controller
+(Figure~\ref{fig:archi}).  The robot and Android tablet application present the
+writing process/result to the user, as in Section \ref{sec:tabletSynch}.
+Furthermore, the tablet application is extended to act as the primary medium for
+capturing user interaction, and publishes the user's demonstrations when user is
+satisfied with their writing. The user demonstrations are received by the
+interaction controller, running on a desktop computer. It is responsible for
+getting the Nao to prompt and respond appropriately to feedback received, using
+a finite state machine to manage the interaction stage and various system
+inputs. It also manages the learning algorithm, by inferring the letter which
+user demonstrations are for, based on their position on the tablet, and
+publishes the shapes to be written which are generated by the learning algorithm
+in response to the feedback.
 
@@
 %algorithm is then taken for the respective shape.
+
+\begin{figure}[ht]
+\centering
+
+\resizebox{0.9\linewidth}{!}{%
+
+\begin{tikzpicture}[
+    >=latex,
+    node distance=2cm,
+    every edge/.style={draw, very thick},
+    redarrow/.style={fill=Red, draw=Red},
+    greenarrow/.style={fill=GreenYellow, draw=GreenYellow},
+    yellowarrow/.style={fill=BurntOrange, draw=BurntOrange},
+    cmpt/.style={draw, align=center, rounded corners, inner sep=5pt, font=\sf, fill=black!20},
+    label/.style={midway, align=left, font=\scriptsize\sf, fill=white, above,opacity=0,text opacity=1}]
+
+    \node at (0,0)[cmpt, fill=Cyan!50] (tactile) {tactile interaction \\ manager};
+    \node[cmpt, fill=Cyan!50, left=of tactile] (display) {display \\ manager};
+
+    \node [cmpt, fill=Turquoise!50, below=of tactile] (shape) {shape position \\ manager};
+    \node [cmpt, fill=Turquoise!50, left=of shape] (learner) {letter \\ learner};
+    \node [cmpt, fill=Turquoise!50, left=of learner] (card) {card \\ detector};
+
+    \node [cmpt, fill=YellowOrange!50, below=1.5cm of shape] (writer) {nao writer};
+    \node [cmpt, fill=YellowOrange!50, left=of writer] (tablet) {tablet detector};
+    \node [cmpt, fill=YellowOrange!50, left=of tablet] (camera) {nao camera};
+    \node [cmpt, fill=YellowOrange!50, below=1cm of tablet] (pose) {robot state publisher};
+
+    %%% Relations between components
+    \path (tactile) edge [->] node[label] {clear \\ screen} (display);
+
+    \path ($(shape.north west)!0.33!(shape.north east)$) edge [<-] node[label,left] {clear \\ screen} ($(tactile.south west)!0.33!(tactile.south east)$);
+    \path ($(shape.north west)!0.66!(shape.north east)$) edge [<-, greenarrow] node[label,right] {feedback \\ + location} ($(tactile.south west)!0.66!(tactile.south east)$);
+
+    \path (shape) edge [->, redarrow] node[label, left, align=right] {letter to write \\ + time \\ + position} (display);
+    \path (shape) edge [->,redarrow] node[label, right] {letter to write \\ + time \\ + position in\\tablet frame} (writer);
+
+    \path ($(shape.north west)!0.66!(shape.south west)$) edge [->, greenarrow] node[label,below] {feedback \\ + letter} ($(learner.north east)!0.66!(learner.south east)$);
+    \path ($(shape.north west)!0.33!(shape.south west)$) edge [<-, redarrow] node[label] {letter to write \\ + time} ($(learner.north east)!0.33!(learner.south east)$);
+
+    \path (card) edge [->, yellowarrow] node[label] {word to learn} (learner);
+    \path (camera) edge [->, yellowarrow] node[label, right] {camera image} (card);
+    \path (camera) edge [->, redarrow] node[label] {camera image} (tablet);
+    \path (tablet) edge [->, redarrow] node[label] {tablet pose} (writer);
+    \path (pose) edge [->, redarrow] node[label, right] {head pose} (tablet);
+
+    \path (-8, 0) edge [->, redarrow] node[label] {Writing letters} (-7, 0);
+    \path (-8, -0.6) edge [->, greenarrow] node[label] {Responding to feedback} (-7, -0.6);
+    \path (-8, -1.2) edge [->, yellowarrow] node[label] {Detecting card input} (-7, -1.2);
+
+\end{tikzpicture}
+}
+
+\caption{Overview of the system. The top row runs on the tablet, the middle row on the central controller and the bottom row on the robot.}
+
+    \label{fig:archi}
+\end{figure}
 

### 2014-09-09 main.tex
Minor fixes

@@
 %
+% ^ <deanna.m.hood@gmail.com> 2014-09-09T09:11:57.672Z.
 
@@
         seven adult participants did not feel that it was their input which
-        helped the robot improve.% * <deanna.m.hood@gmail.com>
-        2014-09-05T09:46:49.117Z:
+        helped the robot improve.
+        % * <deanna.m.hood@gmail.com> 2014-09-05T09:46:49.117Z:
     %
@@
 technically autonomous, can not robustly recover from situations outside of the
-nominal protocol (presented in section~\ref{sec4}), and consequently still requires the
+nominal protocol (presented in Section~\ref{sec4}), and consequently still requires the
 presence of an experimenter. The interaction state machine would require to be

### 2014-09-16 main.tex
Re-organize the last part of the paper
{Conclusion} -> {Towards long-term intervention + Conclusion}

@@
         \subfigure{
-            \includegraphics[width=0.3\textwidth]{figures/naoWriting2.png}
+            \includegraphics[width=0.9\linewidth]{figures/naoWriting2.png}
         }%
@@
     \includegraphics[width=0.45\textwidth]{figures/chilitagDetection_cameraOverlay.png}
-    \caption[Detection of the tablet using a chilitag to represent the origin of
-    the writing surface frame.]{\label{fig:tabletDetection}Detection of the
-    tablet using a chilitag to represent the origin of the writing surface frame
-(left: robot's camera image, with markers overlaid).}
+    \caption{\label{fig:tabletDetection}Detection of the tablet using a fiducial
+    marker to represent the origin of the writing surface frame. The robot's
+    camera image is on the left (the text trajectory overlay is also visible).}
 
@@
 \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the
-demonstration. }. % * <deanna.m.hood@gmail.com> 2014-09-04T11:40:30.176Z:
+demonstration. }.
+% * <deanna.m.hood@gmail.com> 2014-09-04T11:40:30.176Z:
 %
@@
 
-\subsection{Integration into a Robotic Handwriting Learning Agent}
+\subsection{Integration into a Robotic Agent}
 
@@
 
-\subsection{Discussion}% * <deanna.m.hood@gmail.com> 2014-09-05T11:42:42.979Z:
-%
-% this is a reasonable title right?
-%
-
-In addition to the conclusions which 
-Anecdotes which raise questions:
-- "Would have problems with the 'n'" - (8) projecting human learning characteristics. Another said "programmed to write badly" (4)
-- Children saying the other was bad... (3, 9). Child saying the other child's was good (5). Child saying the robot was better than him (9).
-- When one child wrote u differently to the other, they didn't discuss :(
-- so many of them wanted to write the whole word.. robot says "show me a word" and maybe misleading
-- not seeming to notice small changes (12) but maybe from experimenter
-
-- awkward silence, speaking over the top of the robot to talk to experimenter....
-- child walking around
-- word very close to robot's camera
-
-Evidence of engagement:
-- work and/or play
-- once word was good were thinking for a long time about how to improve (8)
-- child `helping' other.. grabbing the pen
-- children trying to cheat the system (10)
-- excitement at stop and test cards - new letters? diff font
-- teaching cursive. group 7 excited to do this even after test finished.
-- unnecessary (unsent) demo from child 11 after it was acceptable but not perfect
-
-\paragraph{Role of the experimenter}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Conclusions and Future Work}
-
-%\subsection{Conclusions}
-
-The technical challenges involved in developing a teachable robotic agent in the
-context of handwriting which have been addressed in this work include:
-
-\begin{itemize}
-
-    \item developing capabilities for a robot with limited fine motor
-        capabilities, such as the Nao, to engage in the act of handwriting in a
-        way which is believable for interacting with children. This has been
-        accomplished by leveraging simulated handwriting with a synchronised
-        tablet;
-
-    \item developing a system for generating poorly written letters appropriate
-        for simulating a na\"ive learner in the context of handwriting, achieved
-        by using statistical shape models through PCA of observations of the
-        trajectory of the same letter;
-
-    \item developing an algorithm capable of incorporating user feedback and
-        demonstrations in order to adapt the generated handwriting quality so as
-        to simulate a teachable agent, which has been implemented by maintaining
-        a learning algorithm in the parameter space of the shape models and
-        converging towards the parameters of user demonstrations; and
-
-    \item integrating the system into a working interaction suitable for
-        engaging children in the learning by teaching paradigm, accomplished by
-        fusing the robotic drawing capabilities and the learning algorithm for
-        handwritten letters established with a central controller which manages
-        the flow of the interaction and turn taking, etc.
-
-\end{itemize}
-
-\subsection{Future Work}
-
-Further research may discover how to best model/limit the learning speed of the
-robot so that it is noticeably learning while not improving so fast as to limit
-the long-term interaction potential for the system, which may turn out to be
-child-dependent.
+\section{Towards Long-term Interventions}
+
+As noted in the introduction, existing literature on handwriting interventions
+agrees to consider 20 hours spread over 20 weeks as a reasonable intervention
+duration to measure actual effects. This directly questions how suitable is our
+approach for such long-term interactions, and raises several challenges, both
+technical and human.
 
@@
 technically autonomous, can not robustly recover from situations outside of the
-nominal protocol (presented in Section~\ref{sec4}), and consequently still requires the
-presence of an experimenter. The interaction state machine would require to be
-extended in non-trivial ways to allow for long, fully autonomous, interactions
-with children.
+nominal protocol (presented in Section~\ref{sec4}), and consequently still
+requires the presence of an experimenter. The interaction state machine would
+require to be extended in non-trivial ways to allow for long, fully autonomous,
+interactions with children. Also, further research may discover how to best
+model/limit the learning speed of the robot so that it is noticeably learning
+while not improving so fast as to limit the long-term interaction potential for
+the system, which may turn out to be child-dependent.
 
@@
 that they experience? We are currently considering running a long-term study
-(about 20 hours of interactions per child) that would provide better evidences
-to answer these questions.
-
-\subsection{Impact and Conclusion}
+that would provide better evidences to answer these questions.
+
+%In addition to the conclusions which 
+%Anecdotes which raise questions:
+%- "Would have problems with the 'n'" - (8) projecting human learning characteristics. Another said "programmed to write badly" (4)
+%- Children saying the other was bad... (3, 9). Child saying the other child's was good (5). Child saying the robot was better than him (9).
+%- When one child wrote u differently to the other, they didn't discuss :(
+%- so many of them wanted to write the whole word.. robot says "show me a word" and maybe misleading
+%- not seeming to notice small changes (12) but maybe from experimenter
+%
+%- awkward silence, speaking over the top of the robot to talk to experimenter....
+%- child walking around
+%- word very close to robot's camera
+%
+%Evidence of engagement:
+%- work and/or play
+%- once word was good were thinking for a long time about how to improve (8)
+%- child `helping' other.. grabbing the pen
+%- children trying to cheat the system (10)
+%- excitement at stop and test cards - new letters? diff font
+%- teaching cursive. group 7 excited to do this even after test finished.
+%- unnecessary (unsent) demo from child 11 after it was acceptable but not perfect
+
+\section{Impact and Conclusion}
 
@@
 
-Because it has the strongest impact for the human-robot interaction community,
-we would like to develop this last point in particular. The work presented here
-investigates a particular role for a robot in the education of handwriting: not
-only the robot is actively performing the activity (it draws letters), but it
-does so in a way that engages the child in a very specific social role. The child
-is the teacher, the robot is the learner: the child must engage in a
-(meta-)cognitive relation with the robot to try to understand why the
-robot fails and how to help it best.  Here, the robot is not only an activity
-facilitator or orchestrator: its physical presence and embodiment induce agency
-and anthropomorphizing, and cognitively engage the child into the learning
-activity, which we predict to lead to higher learning efficacy.
+Specifically, the technical challenges involved in developing a teachable
+robotic agent in the context of handwriting which have been addressed in this
+work include:
+
+\begin{itemize}
+
+    \item developing capabilities for a robot with limited fine motor
+        capabilities, such as the Nao, to engage in the act of handwriting in a
+        way which is believable for interacting with children. This has been
+        accomplished by leveraging simulated handwriting with a synchronised
+        tablet;
+
+    \item developing a system for generating poorly written letters appropriate
+        for simulating a na\"ive learner in the context of handwriting, achieved
+        by using statistical shape models through PCA of observations of the
+        trajectory of the same letter;
+
+    \item developing an algorithm capable of incorporating user feedback and
+        demonstrations in order to adapt the generated handwriting quality so as
+        to simulate a teachable agent, which has been implemented by maintaining
+        a learning algorithm in the parameter space of the shape models and
+        converging towards the parameters of user demonstrations; and
+
+    \item integrating the system into a working interaction suitable for
+        engaging children in the learning by teaching paradigm, accomplished by
+        fusing the robotic drawing capabilities and the learning algorithm for
+        handwritten letters established with a central controller which manages
+        the flow of the interaction and turn taking, etc.
+
+\end{itemize}
+
+However, we believe that the strongest impact of this work for the human-robot
+interaction community relates to the very \emph{nature} of the interaction
+fostered by this research. The work presented here investigates a particular
+role for a robot in the education of handwriting: not only the robot is actively
+performing the activity (it draws letters), but it does so in a way that engages
+the child in a very specific social role. The child is the teacher, the robot is
+the learner: the child must engage in a (meta-)cognitive relation with the robot
+to try to understand why the robot fails and how to help it best.  Here, the
+robot is not only an activity facilitator or orchestrator: its physical presence
+and embodiment induce agency and anthropomorphizing, and cognitively engage the
+child into the learning activity, which we predict to lead to higher learning
+efficacy.
 

### 2014-09-19 main.tex
Full pass on the text

@@
 
-% * <deanna.m.hood@gmail.com> 2014-09-05T11:44:54.921Z:
-%
-% Ana Paiva is a reviewer....
-%
-
 %Despite the social motivation for the use of a teachable agent for the
@@
 
-By leveraging simulated handwriting on a synchronised tablet display, a Nao
+By leveraging simulated handwriting on a synchronised tablet display, a {\sc nao}
 humanoid robot with limited fine motor capabilities has been configured as a
 suitably embodied handwriting partner. Shape models derived from principal
-component analysis of a dataset of letter trajectories are generated, and allow
+component analysis of a dataset of letter trajectories have been generated, and allow
 the robot to draw purposefully deformed letters. Learning how to write
@@
 actually writing on the tablet, and 2) able to improve the robot's writing to a
-level which they were satisfied with. Furthermore, the system represents a
+level which they were satisfied with.
+
+Furthermore, the system represents a
 significant step towards an innovative use for robotics which addresses a
@@
 peer or teacher to simulate a na\"ive learner for the target child to teach,
-however for an activity where one's skill level is visually evident - as is the
-case in handwriting - this acting is likely to be eventually detected. As such,
+however for an activity where one's skill level is visually evident -- as is the
+case in handwriting -- this acting is likely to be eventually detected. As such,
 there is motivation for the use of a teachable agent which can be configured for
 a variety of skill levels, and for which children do not have preconceptions
-about handwriting ability.
+about its handwriting ability.
 
@@
 
-There are three main points which have motivated the use of a robot as the
-teachable agent in the presented work:
+The teachable agent developed has the potential to be embedded as a simulated 
+computer-based agent, however there are three main points which have motivated 
+the use of a robot instead as the teachable agent in the presented work:
 
@@
         paradigm \cite{Okita2006}, and therefore it may be significant for the agent to respond
-        with a writing \emph{process}, rather than simply a product, and
+        with a physical writing \emph{process}, rather than simply a product, and
 
@@
 Consequently, the learning agent developed has been embodied in a commercially
-affordable Nao humanoid robot. Its writing capabilities have been implemented by
+affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
 leveraging synchronisation with a tablet display to simulate fine motor skills
 otherwise infeasible for the robot.
-% * <deanna.m.hood@gmail.com> 2014-09-08T11:08:36.426Z:
-%
-% linking sentence...
-%
-
-Section \ref{sec:learningAlgorithm} presents the novel work in the area of
+
+Within this article, Section \ref{sec:learningAlgorithm} presents the novel work in the area of
 artificial intelligence to develop a learning algorithm suitable for a teachable
@@
 extension of this algorithm to an embodied robotic learning agent, including the
-novel approach for achieving simulated fine motor skills on commercially
-affordable humanoid robots.  Section \ref{sec:experiment} explores the novel% * <deanna.m.hood@gmail.com> 2014-09-08T11:09:28.480Z:
-%
-% use a different word
-%
+new approach for achieving simulated fine motor skills on commercially
+affordable humanoid robots.  Section \ref{sec:experiment} explores the 
 contributions made to the study of human-robot interaction, in discussing the
-use of the system with primary school children and its potential as a tool for
+use of the first-of-its-kind system with primary school children and its potential as a tool for
 addressing wider pedagogical research questions in education.
+Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the content and impact of the article's contributions.
 
@@
 handwriting, a parameterisation of letters and their deformities has been sought
-to generate the necessary letter models. Depending on the parameters input to
-the letter models, different quality shapes can be generated. The system can
+which is capable of generating the necessary letter models. Depending on the parameters input to
+the letter models, different quality shapes should be generated. The system can
 therefore be configured to improve its writing by modifying the parameters used
@@
 using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
-each letter (2 repetitions from 60 adult users). While it may be appropriate to
-identify the location of the most salient features of the shapes in future work,
+each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
+identify the location of salient features of the shapes which are robust to unanticipated user input,
 the features are currently taken as $n$ uniformly spaced points along the shape
-path as salient features are not guaranteed from children's handwriting. The
+path. The
 points are arranged into an observation vector presented in (\ref{eq:obsVec}),
 where $x_i$ and $y_i$ represent the coordinates of each of the points along the
-path.
+path. The observation shapes are normalised such that they have a shape
+centre of ${\bf 0}$ and a unit maximum dimension.
 
@@
 
-In this work, the observation shapes are normalized such that they have a shape
-centre of ${\bf 0}$ and a unit maximum dimension.
-
-The projection from the original $2n$-dimensional feature space $(n=70)$ to an
+The projection from the original $2n$-dimensional feature space $(n=70)$ to a reduced
 $N$-dimensional space is found as in (\ref{eq:projection}), where ${\bf p}$
@@
 each shape may be approximated by the mean shape plus a sum of the top $N$
-eigenvectors, weighted by the parameter vector $p$.
+eigenvectors, weighted by the parameter vector ${\bf p}$.
 
@@
 For the dataset presented in Figure \ref{fig:deviations_sPrint}, the
-eigenvectors associated with the 5 largest eigenvalues explain 90.0\% of the
+eigenvectors associated with the 3 largest eigenvalues explain 78.5\% of the
 variance in the dataset, illustrating the capability of the statistical shape
@@
 
-Clusters within paths of a particular letter have been identified using K-means
-clustering to group different styles of writing the letter (\emph{allographs}),
-such that the parameters in the resulting model are only representative of the
-specific allograph of the letter in the dataset. 
+%Clusters within paths of a particular letter have been identified using K-means
+%clustering to group different styles of writing the letter (\emph{allographs}),
+%such that the parameters in the resulting model are only representative of the
+%specific allograph of the letter in the dataset. 
 % * <deanna.m.hood@gmail.com> 2014-09-03T13:05:23.576Z:
@@
 dataset at a time, to reduce the $2n$-dimensional space to one of a desired
-number of dimensions.
+number of dimensions. $N=10$ has been used for the work presented.
 
@@
     (right) of varying the first three parameters (each row) of a shape model.
-    The presented model has been derived from PCA on the first cluster of `s'
-    shapes, interpreted as the print allograph. The extent to which each
-parameter is varied is dependent on the eigenvector $\lambda$ corresponding to
+     The extent to which each
+parameter is varied is dependent on the eigenvalue $\lambda$ corresponding to
 the parameter's eigenvector. The percentage of the total variance in the dataset
@@
 model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
-the width of the top half of the letter compared to the bottom half, the width
+the height of the top half of the letter compared to the bottom half, the width
 of the overall shape, etc. Consequently, the shape modelling process has
@@
 Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
-models of `e' and `g' - made from 120 observations each, with 70 sample points -
-by selecting random values for the first 5 parameters from a distribution with
+models of `e' and `g' by selecting random values for the first 5 parameters 
+from a distribution with
 standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
@@
 \centering
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.08\textwidth]{figures/e1.png}}}
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.05\textwidth]{figures/e4.png}}}
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.08\textwidth]{figures/e3.png}}}
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.08\textwidth]{figures/e5.png}}}\\
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g1.png}}}
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g3.png}}}
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g4.png}}}
-\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.12\textwidth]{figures/g5.png}}}
-\caption[Sample letters generated from the PCA shape model on 120 `e' and `g'
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.04\textwidth]{figures/e1.png}}}
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.025\textwidth]{figures/e4.png}}}
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.04\textwidth]{figures/e3.png}}}
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.04\textwidth]{figures/e5.png}}}~~~~~
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.06\textwidth]{figures/g1.png}}}
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.06\textwidth]{figures/g3.png}}}
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.06\textwidth]{figures/g4.png}}}
+\subfigure{\raisebox{-0.5\height}{\includegraphics[height=0.06\textwidth]{figures/g5.png}}}
+\caption[Sample letters generated from the PCA shape model on `e' and `g'
 paths.]{\label{fig:sampleLetters}Sample letters generated from the PCA shape
-model on 120 `e' (top) and `g' paths (bottom), generated randomly from
+model on `e' (left) and `g' paths (right), generated randomly from
 parameters with $3\times$ the standard deviation observed in the dataset.}
@@
 
-In \cite{Chandra2013}, it was found that children aged 4-6 years participating% * <deanna.m.hood@gmail.com> 2014-09-05T11:43:42.851Z:
-%
-% this is not peer-reviewed!
-%
+In \cite{Chandra2013}, it was found that children aged 4-6 years participating
 in a handwriting peer tutoring pilot study most often made mistakes classified
@@
 in the context of handwriting have been demonstrated, using the shape model
-generated with PCA from a dataset of only adults' writing.
+generated from PCA on a dataset of only adults' writing.
 
@@
 model of a particular letter may convert a set of parameters into a generated
-letter of the same allograph. Similarly, the model may also be used to convert a
+letter of the same allograph. Similarly, the model may also be used ``in reverse'' 
+to convert a
 letter into its parameters, given the model. The parameters of user-drawn
@@
 reconstruct the shape exactly if $N<2n$, but rather will reconstruct the closest
-point in the $N$-dimensional space which the eigenvectors span. $N=10$ has been
-used for the work presented.
+point in the $N$-dimensional space which the eigenvectors span.
 
@@
 towards those of the demonstration. In the results presented in this work, the
-update equation shown in \ref{eq:update} has been used, where ${\bf p}$ is the
+linear update equation shown in (\ref{eq:update}) has been used, where ${\bf p}$ is the
 learned parameter vector at time step $k$, and $\alpha$ is the learning rate,
@@
 
+Figure \ref{fig:demonstrationShapes2} illustrates the response of the system to
+demonstrations from a child for the letter `s' using a learning rate of
+$\alpha=1/2$.
+
+\begin{figure}[thpb]
+    \centering
+    \includegraphics[width=0.45\textwidth]{figures/learningSdemo}
+    \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
+    responding to user demonstration of shapes for the letter `s' (demonstrations received from two 7-8 year-old children).}
+\end{figure}
+
 It is possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
-individually yield acceptable shapes, may produce parameters ${\bf p}^{(k+1)}$
-by which yield an unacceptable shape. The proposed method for adapting to user
+individually yield acceptable shapes, produce parameters ${\bf p}^{(k+1)}$
+which yield an unacceptable shape, especially if the demonstration shape is of a different style to that learnt at time $k$, as there are no restrictions imposed on parameter values.
+The proposed method for adapting to user
 demonstration would not get stuck at such poor shapes, however: with further
 demonstrations of the same letter, the system would eventually approach the
-demonstration shape. As a result, the event of poor-looking intermediate letters
+demonstration shape (Figure \ref{fig:eDemo}. As a result, the event of poor-looking 
+intermediate letters
 would not limit the interaction later proposed in Section \ref{sec:experiment}
-in a technical sense, but it may influence the user's perception of the learning
+in a technical sense, but it may influence the user's \emph{perception} of the learning
 agent. It remains to be seen if it is necessary to avoid such an event
@@
 
-Figure \ref{fig:demonstrationShapes2} illustrates the response of the system to
-demonstrations from a child for the letter `u' using a learning rate of
-$\alpha=1/2$.
-
 \begin{figure}[thpb]
     \centering
-    \includegraphics[width=0.3\textwidth]{figures/u_kids.png}
-    \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
-    responding to user demonstration of shapes for the letter `u.'}
+    \includegraphics[width=0.3\textwidth]{figures/learningEdemo}
+    \caption{\label{fig:eDemo}Example of the learning algorithm
+    responding to user demonstration of shapes for the letter `e', passing through a parameter state which yields a poor letter (demonstrations received from a 7-8 year-old child).}
 \end{figure}
 
-% * <deanna.m.hood@gmail.com> 2014-09-04T09:19:16.057Z:
-%
-% improve img
-%
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{An Embodied Handwriting Learning Agent with the Nao Humanoid Robot}
+\section{An Embodied Handwriting Learning Agent with the NAO Humanoid Robot}
 \label{sec:robotWriting}
@@
 %to respond to handwriting feedback -
-capabilities for the robot to engage in handwriting have been established.
-
-The Nao humanoid robot, which has been developed by Aldebaran-Robotics and
+capabilities for the robot to engage in handwriting and interactive turn-taking have been established.
+
+The {\sc nao} humanoid robot, which has been developed by Aldebaran Robotics and
 designed purposely to look approachable \cite{Gouaillier2008}, has been used for
@@
 
-%Because of the challenges in getting the Nao to write trajectories smoothly
+%Because of the challenges in getting the {\sc nao} to write trajectories smoothly
 %because of its inherent ability to only reach discrete points in space, 
@@
 addition to the absence of force feedback and other technical necessities, the
-Nao has been configured to use simulated handwriting with a synchronised tablet
+{\sc nao} has been configured to use simulated handwriting with a synchronised tablet
 to achieve this level of control. The necessary components of implementing the
@@
 \begin{enumerate}
-    \item developing capabilities for the robot to trace handwriting,
+    \item developing capabilities for the robot to trace handwriting ``in the air'',
 
@@
 has been used for the inverse kinematics of the trajectory following. The Robot
-Operating System (ROS)\footnote{The ROS stack for Nao is available at:
-\url{http://wiki.ros.org/nao_robot}} has been used for integration of the Nao
-with external reference frames using the $tf$ transformation library
-\cite{Foote2013}, such as the tablet's location.
+Operating System (ROS)\footnote{The ROS stack for {\sc nao} is available at:
+\url{http://wiki.ros.org/nao_robot}.} has been used for integration of the {\sc nao}
+with external reference frames, such as the tablet's location, using the $tf$ transformation library \cite{Foote2013}.
 
@@
     \item Concerns about whether or not the child would start mimicking the
-        robot's incorrect (inhuman) writing style are mitigated. % * <deanna.m.hood@gmail.com> 2014-09-04T09:59:44.707Z:
-%
-% is this point significant enough?
-%
+        robot's incorrect writing form (\eg pen grip) are mitigated.
 
@@
         \subfigure{
-            \includegraphics[width=0.9\linewidth]{figures/naoWriting2.png}
+            \includegraphics[width=0.8\linewidth]{figures/naoWriting2.png}
         }%
@@
     its finger. The motion of the robot is synchronised with the display of the
-    tablet, communicating over ROS.}%
+    tablet, communicating over ROS.\protect\footnotemark}%
 
@@
 \end{figure}
+\footnotetext{See
+\url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised writing 
+demonstration. }
 
@@
 for their feedback on the system advised that children are asked to draw letters
-in the air in a similar manner as part of their handwriting education.}. As
+in the air in a similar manner as part of their handwriting education. The behaviour 
+is hence not unfamiliar to children.}. As
 interacting with a tablet with one's finger is not uncommon, this may aid the
@@
 An Android application has been developed to receive the trajectory message over
-a ROS topic and add each point of the trajectory one by one as a frame of an
+a ROS topic and display the trajectory as an
 animation. Synchronisation between the tablet and the robot has been achieved by:
@@
     \centering
-    \includegraphics[width=0.45\textwidth]{figures/chilitagDetection_cameraOverlay.png}
+    \includegraphics[width=0.35\textwidth]{figures/chilitagDetection_cameraOverlay.png}
     \caption{\label{fig:tabletDetection}Detection of the tablet using a fiducial
-    marker to represent the origin of the writing surface frame. The robot's
-    camera image is on the left (the text trajectory overlay is also visible).}
-
-\end{figure}% * <deanna.m.hood@gmail.com> 2014-09-04T11:21:59.328Z:
-%
-% this image is pretty bad, and doesn't add much
-%
-
-A demonstration of the robot executing a trajectory in synch with the tablet is
-shown in Figure \ref{fig:naoWriting}\footnote{See
-\url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the
-demonstration. }.
-% * <deanna.m.hood@gmail.com> 2014-09-04T11:40:30.176Z:
-%
-% this sounds dumb on paper.....
-%
+    marker to represent the origin of the writing surface frame, visualised in RViz. The robot's
+    camera image is on the left, with the text trajectory overlay visible.}
+
+\end{figure}
 
@@
 writing process/result to the user, as in Section \ref{sec:tabletSynch}.
-Furthermore, the tablet application is extended to act as the primary medium for
+Furthermore, the tablet application has been extended to act as the primary medium for
 capturing user interaction, and publishes the user's demonstrations when user is
@@
 interaction controller, running on a desktop computer. It is responsible for
-getting the Nao to prompt and respond appropriately to feedback received, using
+getting the {\sc nao} to prompt and respond appropriately to feedback received, using
 a finite state machine to manage the interaction stage and various system
-inputs. It also manages the learning algorithm, by inferring the letter which
-user demonstrations are for, based on their position on the tablet, and
+inputs. The controller also manages the learning algorithm, by inferring the letter which
+user demonstrations are for based on their position on the tablet, and
 publishes the shapes to be written which are generated by the learning algorithm
@@
 
-    \node [cmpt, fill=Turquoise!50, below=of tactile] (shape) {shape position \\ manager};
-    \node [cmpt, fill=Turquoise!50, left=of shape] (learner) {letter \\ learner};
-    \node [cmpt, fill=Turquoise!50, left=of learner] (card) {card \\ detector};
+    \node [cmpt, fill=Green!50, below=of tactile] (shape) {shape position \\ manager};
+    \node [cmpt, fill=Green!50, left=of shape] (learner) {letter \\ learner};
+    \node [cmpt, fill=Green!50, left=of learner] (card) {card \\ detector};
 
@@
 
-\caption{Overview of the system. The top row runs on the tablet, the middle row on the central controller and the bottom row on the robot.}
+\caption{Overview of the system. Components in the top row run on the tablet, 
+those in the middle row on the central controller, and those in the bottom row 
+on the robot.}
 
@@
 robotic agent represents a tool which may be used for investigating social and
-pedagogical research questions. One such question is what impact the addition of
+pedagogical research questions. For example, one such question is what impact the addition of
 such a teachable robotic agent would have on the outcomes of a typical
@@
         letters by pointing at the tablet and imitating tracing the letters. The
-        tablet, placed in front of the robot with a vertical orientation,
+        tablet, placed in front of the robot with a vertical, landscape orientation,
         displays the letters in synchronisation with the robot's movements.
@@
         with participants taking turns to interact with the robot if necessary.
-        When the child is satisfied with the robot's performance on all letters,
-        they may use the ``test'' card and an additional word on which they will
+        When the participant(s) is/are satisfied with the robot's performance on 
+	all letters,
+        they may use the ``test'' card and an additional word for which they will
         verbally evaluate the robot's performance.
@@
 
-\subsection{Outcomes of Preliminary Studies}% * <deanna.m.hood@gmail.com> 2014-09-05T08:43:38.105Z:
-%
-% I guess this is what we call the non-experiments.. Are the dates important?
-%
-% ^ <deanna.m.hood@gmail.com> 2014-09-09T09:11:57.672Z.
-
-Preliminary studies at two schools in the Geneva area have been conducted to
-evaluate the feasibility and technical soundness of the interaction system
-proposed. A pilot study at the first school consisted of four groups of
+\subsection{Outcomes of Preliminary Studies}
+
+Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
+have been conducted to evaluate the feasibility and technical soundness of the 
+interaction system proposed.
+
+A pilot study at the first school consisted of four groups of
 approximately 8 english-speaking children, aged 6-7 years. The children
@@
 the robot in the same place as previously-written letters. At the time, the
-system required the children to write ontop of a letter of the same type as the
+system required the children to write on top of a letter of the same type as the
 one which they were demonstrating, and the children seemed to find this
@@
 the children the opportunity to write around previously-written letters instead
-of just ontop.
+of just on top.
 
@@
 
-The study at the second school involved 21 french-speaking students: 7 children
+The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
 interacted with the robot by themselves, and 7 sessions included the remaining
 14 students interacting with the robot in pairs. The duration of the sessions
-was between 8 and 15 minutes, with an average of 11.4 minutes (standard
-deviation of 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
+was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
 %
@@
 The following conclusions were successfully drawn about the system as a result
-of the study at the second school:
-
-\begin{itemize}% * <deanna.m.hood@gmail.com> 2014-09-05T09:34:46.545Z:
-%
-% taking this out of bullet points gains extra space in paper if needed
-%
-
-    \item \textbf{The simulated robotic writing was believed by the children in all
+of the study at the second school.
+
+    \textbf{The simulated robotic writing was believed by the children in all
     cases.} There were, at times, 
@@
     the robot was pretending, the children were asking if they believed that the
-    robot would be able to write its name, \emph{Nao}, which had not previously been
+    robot would be able to write its name, \emph{{\sc nao}}, which had not previously been
     demonstrated. It was reasoned that this would prompt the children to question
-    the point of the robot actually \emph{writing} if they had any concerns that
-    they were being fooled, but this was never the case. In the event where the
-    robot's writing was not synchronised with the tablet, this did not affect the
-    response of the child. If older children participate in the interaction study,
-    which may be likely as children with lasting handwriting difficulties are used
-    as participants, it may become more important to invest time into the
-    believability of the robot's writing scheme. however for 6-8 year olds the
+    the point of the robot actually \emph{writing} if they had any suspicion that
+    the robot was pretending, but this was never the case. In the event where the
+    robot's writing was not correctly synchronised with the tablet, this did not affect the
+    response of the child. If older children participate in the interaction study --
+    which may be likely as children with lasting handwriting difficulties are included
+    as participants -- it may become more important to invest time into the
+    believability of the robot's writing scheme. However, for 6-8 year olds the
     proposed setup has been proven viable.
 
-    \item \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
+    \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
     %
@@
     %
-    An average of 10.9 demonstration letters (standard deviation of 4.4) were
+    An average of 10.9 demonstration letters (SD = 4.4) were
     provided to the robot for each session during the interaction. Furthermore,
@@
 
-    \item \textbf{All children believed that the robot was learning, and that
+    \textbf{All children believed that the robot was learning, and that
         they were the ones teaching it.} This was concluded from their responses
@@
 
-    \item \textbf{The system has been validated as a technically sound
+    \textbf{The system has been validated as a technically sound
         autonomous interaction.} The interaction setup including the teachable
@@
         the robot writing 335 letters, 152 of which in response to
-        demonstrations received from the 21 children. During this time, the
-        technical components of the system operated autonomously, with only the
-        verbal interaction being maintained by an observing researcher, and only
-        required intervention for the three instances that the robot fell later
-        in the day.% * <deanna.m.hood@gmail.com> 2014-09-05T10:49:26.786Z:
-    %
-    % could probably get away without mentioning this....
-    %
-
-\end{itemize}
+        demonstrations received from the 21 children. During this time, technical 
+	intervention was only required for the three instances that the robot fell 
+	later in the day. Otherwise, the technical components of the system operated 
+	autonomously and as expected over the sessions.
+        %, with only verbal interaction for prompting being required from an observing researcher.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Towards Long-term Interventions}
-
-As noted in the introduction, existing literature on handwriting interventions
-agrees to consider 20 hours spread over 20 weeks as a reasonable intervention
-duration to measure actual effects. This directly questions how suitable is our
-approach for such long-term interactions, and raises several challenges, both
-technical and human.
-
-In the scope of open technical questions, it remains to be seen how shape models
+\section{Towards Long-term Interventions}\label{sec:futureWork}
+%why is this title going into the margins....
+
+As noted in the introduction, a conclusion drawn in~\cite{Hoy2011} is that any 
+handwriting intervention studies considered in the systematic review which involved 
+fewer than two practice sessions per week and fewer than a total of 20 practice 
+sessions, including homework, were not found to demonstrate effective results. This 
+highlights the necessity to engage students in an interaction which will be sustainable
+ over the long-term if we wish to move towards using the proposed system to answer 
+research questions which involve the measurement of learning gains to gauge effects. 
+Several challenges are raised in developing such long-term capabilities for the system,
+ from both technical and socialogical points of view. %not sure this makes sense
+
+In terms of the interaction experience, the current experimental setting, while
+technically autonomous, can not robustly recover from situations outside of the
+nominal protocol (presented in Section~\ref{sec4}), and consequently still
+requires the presence of an experimenter. The interaction state machine would
+require extension in non-trivial ways to allow for long, fully autonomous
+interactions with children.
+
+In the current system, the robot can ask questions and prompt participants, but it 
+cannot engage in discussions with the participants. It is clear that work is necessary 
+to develop the conversational agent in the interaction so that the presence of an 
+experimenter is not required for a captivating engagement. While there is the 
+possiblity to focus the interaction design on group-based interaction with the robot 
+in order to alleviate the necessity of a conversational agent, there is reason to 
+suggest that constructing such a social interaction is not a trivial task. Anectodes 
+from the preliminary studies have shown that some children may criticise another's 
+demonstrations to the robot, which may or may not be as damaging to a child's 
+self-efficacy as when they are criticised in a typical educational context. In addition,
+on occassions where a pair of children came to teach the robot different styles of a 
+particular letter, they did not discuss with each other their different writing styles 
+and the effect on the teaching efficiency. This may suggest that a social context in 
+which verbalising opinions about differences is encouraged is necessary to get children 
+to cooperate in teaching the robot.  
+%- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
+%- awkward silence, speaking over the top of the robot to talk to experimenter....
+%- Children saying the other was bad... (3, 9).
+%- When one child wrote u differently to the other, they didn't discuss :(
+
+How the child's perception of the robot as a learning agent may change over the 
+long-term remains to be seen. On one occasion during the preliminary studies, a 
+child's response to whether the {\sc nao} could write its own name included that it 
+may have problems with the `n', as the child had been correcting the robot on this 
+letter. This suggests that users may project human-like learning features, such as 
+forgetfulness, onto the robot, which may or may not actually be technically present 
+in the learning agent. This may need to be capitalised on when considering how to 
+extend the interaction for the long-term, as the present system with a learning rate 
+such that progress is evident to the user will cause convergence for a letter within a 
+few iterations.
+
+In the scope of open technical questions for enabling long-term interaction, it remains to be seen how shape models
 for letters might be generated which capture the full range of mistakes typical
@@
 
-In terms of the interaction experience, the current experimental setting, while
-technically autonomous, can not robustly recover from situations outside of the
-nominal protocol (presented in Section~\ref{sec4}), and consequently still
-requires the presence of an experimenter. The interaction state machine would
-require to be extended in non-trivial ways to allow for long, fully autonomous,
-interactions with children. Also, further research may discover how to best
-model/limit the learning speed of the robot so that it is noticeably learning
-while not improving so fast as to limit the long-term interaction potential for
-the system, which may turn out to be child-dependent.
-
-On the educational side, open questions include how the handwriting error
+If the system is extended to allow for a wider range of mistakes, a further question 
+then is how the handwriting error
 generation of the system may be abstracted to a higher level of control so that
@@
 difficulties, and empowering the teaching staff to decide for themselves
-instead? And, as a result, the ultimate question for this area of research is
-to address what impact to the outcomes of a long-term handwriting intervention the
-addition of such a teachable robotic agent would have: does it impact the
-motivation of the participants, their self-esteem, and/or the learning gains
-that they experience? We are currently considering running a long-term study
-that would provide better evidences to answer these questions.
+instead?
+
+With some of the challenges towards an engaging long-term handwriting intervention 
+with the teachable robotic partner addressed, further steps can be made towards 
+answering the ultimate question of what impact to the outcomes of interventions the 
+addition of such a teachable robotic agent would have, including with respect to the 
+participants' self-esteem, motivation, or learning gains. % does it impact the
+%motivation of the participants, their self-esteem, and/or the learning gains
+%that they experience? We are currently considering running a long-term study
+%that would provide better evidences to answer these questions.
 
@@
 %Anecdotes which raise questions:
-%- "Would have problems with the 'n'" - (8) projecting human learning characteristics. Another said "programmed to write badly" (4)
-%- Children saying the other was bad... (3, 9). Child saying the other child's was good (5). Child saying the robot was better than him (9).
-%- When one child wrote u differently to the other, they didn't discuss :(
+% Another said "programmed to write badly" (4)
+% Child saying the other child's was good (5). Child saying the robot was better than him (9).
+
 %- so many of them wanted to write the whole word.. robot says "show me a word" and maybe misleading
@@
 %
-%- awkward silence, speaking over the top of the robot to talk to experimenter....
+
 %- child walking around
@@
 
-\section{Impact and Conclusion}
-
-We believe this article introduces three noteworthy contributions: an innovative
+\addtolength{\textheight}{-.0cm}   % This command serves to balance the column lengths
+                                  % on the last page of the document manually. It shortens
+                                  % the textheight of the last page by a suitable amount.
+                                  % This command does not take effect until the next page
+                                  % so it should come on the page before the last. Make
+                                  % sure that you do not shorten the textheight too much.
+
+\section{Impact and Conclusion}\label{sec:conclusions}
+
+We believe that this article introduces three noteworthy contributions: an innovative
 application of data processing and artificial intelligence for the generation and
 learning of hand-written letters suitable for educative purposes; a robotic
-system that has been experimentally proven to provide convincing scaffolding for
+system which has been experimentally proven to provide convincing scaffolding for
 complex human-robot interactions (teacher-learner social interactions, learning by
-demonstration); an initial experimental investigation of what appears to be a
+demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
 new role for robots in education.
@@
     \item developing capabilities for a robot with limited fine motor
-        capabilities, such as the Nao, to engage in the act of handwriting in a
+        capabilities, such as the {\sc nao}, to engage in the act of handwriting in a
         way which is believable for interacting with children. This has been
@@
         handwritten letters established with a central controller which manages
-        the flow of the interaction and turn taking, etc.
+        the flow of the interaction, turn taking and integration of the connected 
+	devices.
 
@@
 the child in a very specific social role. The child is the teacher, the robot is
-the learner: the child must engage in a (meta-)cognitive relation with the robot
+the learner: the child must engage in a (meta-)cognitive relationship with the robot
 to try to understand why the robot fails and how to help it best.  Here, the
 robot is not only an activity facilitator or orchestrator: its physical presence
-and embodiment induce agency and anthropomorphizing, and cognitively engage the
-child into the learning activity, which we predict to lead to higher learning
+and embodiment induce agency and anthropomorphising, and cognitively engage the
+child into the learning activity, which we predict will lead to higher learning
 efficacy.
@@
 Also notable, the robot is not used in the usual context of robotics or computer
-education, but instead in an activity -- handwriting -- that requires fine
+education, but instead in an activity -- handwriting -- which requires fine
 physical skills. In such activities, the embodied nature of the robot makes a
 lot of sense (due to motor mimicry, the arm motion for instance is, \emph{by
-itself}, part of the teaching). Along those lines, we hope to see more research
+itself}, part of the teaching). Along these lines, we hope to see more research
 on non-STEM educational applications of robotics.
@@
 the role for robots in the education landscape. \emph{Learning by teaching} is a
-powerful paradigm because not only its pedagogical efficacy is proven, but it
-also positively impacts the child's motivation and self-esteem. We have
-discovered that it is also a very relevant context of use for robots. Indeed,
-when facing a child with school difficulties, robots can play a role (being the
-``even more ignorant student'') that neither the adults nor the peers (because
-of the social effects it would induce) can convincingly play.
+powerful paradigm because of not only its pedagogical efficacy, but its
+potential to positively impact the child's motivation and self-esteem. We hope that 
+this article shows that this is a very relevant context of use for robots. Indeed,
+when facing a child with school difficulties, robots can play a role of a na\"ive 
+learner which neither the adults nor the peers (because of the social effects it would 
+induce) can convincingly play.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%\section{ACKNOWLEDGMENTS}
-
-%The authors gratefully acknowledge the contribution of National Research Organization and reviewers' comments.
+\section*{Acknowledgments}
+
+This research was supported by the Swiss National Science Foundation through the
+National Centre of Competence in Research Robotics.
 

### 2014-09-29 main.tex
Polishing

@@
 
-Presented is a robotic partner which children can teach handwriting. It is
+This article presents the first known robotic partner which children can teach handwriting. It is
 hypothesised that such a system could not just engage an unmotivated student,
@@
 the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
-reduction with minimal impact. Indeed, the amount of variance in the dataset
-that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
-therefore the proportion of the variance explained by each dimension/eigenvector
-is as shown in (\ref{eq:proportionVar}).
-
-\begin{equation}\label{eq:proportionVar}
-\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
-\end{equation}
+reduction with minimal impact. 
+%Indeed, the amount of variance in the dataset
+%that is explained by each eigenvector ${\bf v}_i$ is $\sqrt{\lambda_i}$, and
+%therefore the proportion of the variance explained by each dimension/eigenvector
+%is as shown in (\ref{eq:proportionVar}).
+%
+%\begin{equation}\label{eq:proportionVar}
+%\%var_i = \frac{\sqrt{\lambda_i}}{\sum_{i=1}^{N}\sqrt{\lambda_i}}\times 100\%
+%\end{equation}
 
@@
 demonstrations from a child for the letter `s' using a learning rate of
-$\alpha=1/2$.
+$\alpha=1/2$.  Note that even poorly-written demonstrations allow the system to improve.
 
@@
         \subfigure{
-            \includegraphics[width=0.8\linewidth]{figures/naoWriting2.png}
+            \includegraphics[width=0.6\linewidth]{figures/naoWriting2.png}
         }%
@@
 
-As noted in the introduction, a conclusion drawn in~\cite{Hoy2011} is that any 
+A conclusion drawn in~\cite{Hoy2011} is that any 
 handwriting intervention studies considered in the systematic review which involved 
@@
  over the long-term if we wish to move towards using the proposed system to answer 
-research questions which involve the measurement of learning gains to gauge effects. 
+research questions which involve the measurement of learning gains to gauge effectiveness. 
 Several challenges are raised in developing such long-term capabilities for the system,
@@
 in order to alleviate the necessity of a conversational agent, there is reason to 
-suggest that constructing such a social interaction is not a trivial task. Anectodes 
+believe that constructing such a social interaction is not a trivial task. Anectodes 
 from the preliminary studies have shown that some children may criticise another's 
@@
 
-How the child's perception of the robot as a learning agent may change over the 
+How the children's perception of the robot as a learning agent may change over the 
 long-term remains to be seen. On one occasion during the preliminary studies, a 
-child's response to whether the {\sc nao} could write its own name included that it 
+child's response to whether or not the {\sc nao} could write its own name included that it 
 may have problems with the `n', as the child had been correcting the robot on this 
@@
 in the learning agent. This may need to be capitalised on when considering how to 
-extend the interaction for the long-term, as the present system with a learning rate 
-such that progress is evident to the user will cause convergence for a letter within a 
+extend the interaction for long time frames, as the present system -- with a learning rate 
+such that progress is evident to the user -- will cause convergence for a letter within a 
 few iterations.
@@
 answering the ultimate question of what impact to the outcomes of interventions the 
-addition of such a teachable robotic agent would have, including with respect to the 
+addition of such a teachable robotic agent would have, including the effect on the 
 participants' self-esteem, motivation, or learning gains. % does it impact the
@@
 
-The strong social impact of early school problems makes research in this field
-a certainly useful challenge for HRI.
+The strong social impact of early educational problems makes research in this field
+an undoubtably meaningful challenge for HRI.
 

### 2014-10-01 main.tex
Polishing

@@
 \title{\LARGE \bf
-``Those who can't do, teach'': a Teachable Robotic Agent for Children Learning Handwriting
+``Those Who Can't Do, Teach'': A Teachable Robotic Agent for Children Learning Handwriting
 }
@@
 \begin{abstract}
-% * <deanna.m.hood@gmail.com> 2014-09-05T11:44:33.364Z:
-%
-% capitalise inside the phrase?
-%
 
@@
 widespread and socially meaningful challenge in education, and provides context
-for robotics in education beyond the well-explored use of teaching coding- and
+for robotics in education beyond the well-explored use of teaching coding and
 robotics-related subjects.
@@
 \end{enumerate}
-
+% * <deanna.m.hood@gmail.com> 2014-10-01T02:59:34.808Z:
+%
+% the article cited is not explained well enough
+%
 Consequently, the learning agent developed has been embodied in a commercially
@@
 
-For the development of a reinforcement learning algorithm in the context of
-handwriting, a parameterisation of letters and their deformities has been sought
+For the development of a learning algorithm in the context of
+handwriting, a parameterisation of letters and their deformities was sought
 which is capable of generating the necessary letter models. Depending on the parameters input to
@@
 PCA has been performed on all of the paths of a particular allograph in the
-dataset at a time, to reduce the $2n$-dimensional space to one of a desired
+dataset individually, to reduce the $2n$-dimensional space to one of a desired
 number of dimensions. $N=10$ has been used for the work presented.
@@
 (\ref{eq:projection}) may also be used
-to generate new shapes based on the parameters ${\bf p}$ which are used: ${\bf
+to generate new shapes based on the parameters ${\bf p}$ which are used. ${\bf
 p}={\bf 0}$ will yield the mean shape, and variations to each of the $N$ values
@@
 are less likely to represent shapes from the dataset of reasonable,
-adult-written letters, and as a result are more likely to represent poor shapes.
+adult-written letters, and as a result are more likely to represent poor shapes.% * <deanna.m.hood@gmail.com> 2014-10-01T04:12:39.275Z:
+%
+% are adults legible?
+%
 Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
@@
 inappropriately. Nevertheless, sufficient capabilities for the shape model to
-generate `poor' letters which are appropriate for simulating a na\"ive learning
+generate `poor' letters which are appropriate for simulating a na\"ive learner
 in the context of handwriting have been demonstrated, using the shape model
@@
 model of a particular letter may convert a set of parameters into a generated
-letter of the same allograph. Similarly, the model may also be used ``in reverse'' 
+letter. Similarly, the model may also be used ``in reverse'' 
 to convert a
@@
     \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
-    responding to user demonstration of shapes for the letter `s' (demonstrations received from two 7-8 year-old children).}
+    responding to user demonstration of shapes for the letter `s' (demonstrations received from two 7-8 year-old children).}% * <deanna.m.hood@gmail.com> 2014-10-01T04:25:20.590Z:
+%
+% confusing
+%
 \end{figure}
@@
 individually yield acceptable shapes, produce parameters ${\bf p}^{(k+1)}$
-which yield an unacceptable shape, especially if the demonstration shape is of a different style to that learnt at time $k$, as there are no restrictions imposed on parameter values.
-The proposed method for adapting to user
-demonstration would not get stuck at such poor shapes, however: with further
+which yield an unacceptable shape. This is especially true if the demonstration
+shape is of a different style to that learnt at time $k$ as there are no
+restrictions imposed on parameter values. The proposed method for adapting to
+the demonstration shape has the ability to recover, however: with further
 demonstrations of the same letter, the system would eventually approach the
@@
 The {\sc nao} humanoid robot, which has been developed by Aldebaran Robotics and 
-designed purposely to look approachable \cite{Gouaillier2008}, has been used for
+purposely designed to look approachable \cite{Gouaillier2008}, has been used for
 this work. It is a commercially affordable biped robot, 58cm tall, with 25
@@
 %because of its inherent ability to only reach discrete points in space, 
-A fine level of control over what the robot is writing is necessary in the
-proposed application of a learning agent in the context of handwriting. Because
+Precise control over what the robot is writing is necessary in the
+proposed application of a learning agent in this context. Because
 of the limited fine motor skills possible with such an affordable robot, in
@@
     \item synchronising the robot's movements with the display of the writing on a
-        tablet so that it seems that the robot is causing the handwriting to
+        tablet so that it appears that the robot is causing the handwriting to
         display because of its actions, and
@@
 robot's motions must still sufficiently match the displayed trajectory in order
-capture the engagement of the child user in the action. Aldebaran's NaoQi API
+capture the engagement of the child participant in the action. Aldebaran's NaoQi API
 has been used for the inverse kinematics of the trajectory following. The Robot
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgments}
-
-This research was supported by the Swiss National Science Foundation through the
-National Centre of Competence in Research Robotics.
+% Anonymized for double-blind review
+%\section*{Acknowledgments}
+
+%This research was supported by the Swiss National Science Foundation through the
+%National Centre of Competence in Research Robotics.
 

### 2014-10-03 main.tex
Last fixes

@@
 %The technical components of the system have been validated, in that children 
-Children aged 6-8 were successfully 1) led to believe that the robot was
-actually writing on the tablet, and 2) able to improve the robot's writing to a
-level which they were satisfied with.
+Children aged 6-8 were successfully led to believe that the robot was
+actually writing on the tablet, and were able to improve the robot's writing to a
+level which they were satisfied with, validating the interaction.
 
@@
 significant step towards an innovative use for robotics which addresses a
-widespread and socially meaningful challenge in education, and provides context
+wide-spread and socially meaningful challenge in education, and provides context
 for robotics in education beyond the well-explored use of teaching coding and
@@
     \item the potential for motor mimicry to yield significant improvements in
-        handwriting interventions \cite{Berninger1997} further supports the case
+        handwriting interventions in which letter formations are demonstrated to participants \cite{Berninger1997} further supports the case
         for investigating the use of a humanoid robot capable of physically
@@
 \end{enumerate}
-% * <deanna.m.hood@gmail.com> 2014-10-01T02:59:34.808Z:
-%
-% the article cited is not explained well enough
-%
+
 Consequently, the learning agent developed has been embodied in a commercially
@@
 When the parameter values are outside of the range observed in the dataset, they
-are less likely to represent shapes from the dataset of reasonable,
-adult-written letters, and as a result are more likely to represent poor shapes.% * <deanna.m.hood@gmail.com> 2014-10-01T04:12:39.275Z:
-%
-% are adults legible?
-%
+are less likely to represent shapes from the dataset of adult-written letters, 
+and as a result are more likely to represent poor shapes.
 Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
@@
     \caption{\label{fig:demonstrationShapes2}Example of the learning algorithm
-    responding to user demonstration of shapes for the letter `s' (demonstrations received from two 7-8 year-old children).}% * <deanna.m.hood@gmail.com> 2014-10-01T04:25:20.590Z:
-%
-% confusing
-%
+    responding (top) to user demonstration of shapes (bottom) for the letter `s' (demonstrations received from two 7-8 year-old children taking turns).}
 \end{figure}
@@
 which yield an unacceptable shape. This is especially true if the demonstration
-shape is of a different style to that learnt at time $k$ as there are no
-restrictions imposed on parameter values. The proposed method for adapting to
-the demonstration shape has the ability to recover, however: with further
+shape is of a different style to that learnt at time $k$, as there are no
+restrictions imposed on parameter values. However, the proposed method for adapting to
+the demonstration shapes has the advantage of being able to recover from such a situation: with further
 demonstrations of the same letter, the system would eventually approach the
-demonstration shape (Figure \ref{fig:eDemo}. As a result, the event of poor-looking 
+demonstration shape (see Figure \ref{fig:eDemo}. As a result, the event of poor-looking 
 intermediate letters
@@
     \caption{\label{fig:eDemo}Example of the learning algorithm
-    responding to user demonstration of shapes for the letter `e', passing through a parameter state which yields a poor letter (demonstrations received from a 7-8 year-old child).}
+    responding (top) to user demonstration of shapes (bottom) for the letter `e', passing through a parameter state which yields a poor letter (demonstrations received from a 7-8 year-old child).}
 \end{figure}
@@
 
-The {\sc nao} humanoid robot, which has been developed by Aldebaran Robotics and 
+The {\sc nao} V4 humanoid robot, which has been developed by Aldebaran Robotics and 
 purposely designed to look approachable \cite{Gouaillier2008}, has been used for
@@
 \end{figure}
-\footnotetext{See
-\url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised writing 
-demonstration. }
+\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
+writing demonstration. }
 
@@
     \item reducing the number of points along the trajectory passed to the
-        robot's motion planner, to improve timing accuracy, and
+        robot's motion planner to improve timing accuracy, and
 
     \item not running computationally expensive tasks on the robot (such as
-        camera publishing) while it is writing, as this interferes with the
+        camera publishing) while it is writing as this interferes with the
         requested timings between points.
@@
 \url{https://github.com/chili-epfl/ros_markers} for more information on the
-fiducial markers used.}, with the camera located in its head, and use that to
+fiducial markers used.}, with the camera located in its head, and to use that to
 determine the relative position of the writing surface (Figure
-\ref{fig:tabletDetection}). When used in an interaction involving a user, this
-allows a user to move the tablet as required for the interaction. As publishing
+\ref{fig:tabletDetection}). When used in an interaction involving a participant, this
+allows a user to move the tablet as required for the interaction. As broadcasting
 the robot's camera has been identified as a computationally expensive task which
@@
 writing process/result to the user, as in Section \ref{sec:tabletSynch}.
-Furthermore, the tablet application has been extended to act as the primary medium for
-capturing user interaction, and publishes the user's demonstrations when user is
+The tablet application has been extended to act as the primary medium for
+capturing participant input, and publishes the user's demonstrations when they are
 satisfied with their writing. The user demonstrations are received by the
-interaction controller, running on a desktop computer. It is responsible for
-getting the {\sc nao} to prompt and respond appropriately to feedback received, using
+interaction controller running on a desktop computer. It is responsible for
+getting the {\sc nao} to prompt and respond appropriately to feedback received using
 a finite state machine to manage the interaction stage and various system
-inputs. The controller also manages the learning algorithm, by inferring the letter which
-user demonstrations are for based on their position on the tablet, and
+inputs.  In the context of learning handwriting, an additional input to the system is a word 
+from which the letters are to be learned, as detected by a fiducial marker on a word card.
+The controller manages the learning algorithm by inferring the letter which
+user demonstrations are intended for based on their position on the tablet, and
 publishes the shapes to be written which are generated by the learning algorithm
 in response to the feedback.
+
+The source code for the teachable robotic handwriting partner has been made 
+available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
 
@@
 illustrates an example interaction sequence between the participant and the
-robot, which consists of the following stages.
+robot which consists of the following stages:
 
@@
 
-    \item The robot responds to the word request verbally, and writes the
-        letters by pointing at the tablet and imitating tracing the letters. The
+    \item The robot responds to the word request verbally and writes the
+        letters by pointing at the tablet and imitating writing the letters. The
         tablet, placed in front of the robot with a vertical, landscape orientation,
@@
         tablet may be moved into the most appropriate position for the child to
-        write on it. Only one letter may be demonstrated at a time, and the
+        write on it. Only one letter may be demonstrated at a time and the
         position of the participant's demonstration on the tablet encodes the
@@
         When the participant is satisfied with the demonstration, a button on
-        the tablet which signals that it is the robot's turn is pressed, and the
+        the tablet which signals that it is the robot's turn is pressed and the
         demonstration is sent to the controller.
@@
 interacted with the system for a total of 65 minutes, with the robot writing 96
-letters, 49 of which in response to demonstrations from the children.
+letters, of which 49 were in response to demonstrations from the children.
 
@@
 the children the opportunity to write around previously-written letters instead
-of just on top.
+of on top.
 
@@
 The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
-interacted with the robot by themselves, and 7 sessions included the remaining
+interacted with the robot individually and 7 sessions included the remaining
 14 students interacting with the robot in pairs. The duration of the sessions
@@
     express doubt in the robot's ability to write without explicitly asking them if
-    the robot was pretending, the children were asking if they believed that the
-    robot would be able to write its name, \emph{{\sc nao}}, which had not previously been
+    the robot was pretending, the children were asked if they believed that the
+    robot would be able to write its name, \emph{{\sc nao}} which had not previously been
     demonstrated. It was reasoned that this would prompt the children to question
@@
     An average of 10.9 demonstration letters (SD = 4.4) were
-    provided to the robot for each session during the interaction. Furthermore,
-    in 9 out of the 14 sessions (64\%), the robot received demonstration letters
+    provided to the robot for each session during the interaction.
+    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
     \emph{after} reaching the test stage of the interaction. The participants'
@@
 
-    \textbf{All children believed that the robot was learning, and that
-        they were the ones teaching it.} This was concluded from their responses
+    \textbf{All children believed that the robot was learning and that
+        they were the ones teaching it.} This was concluded from the responses
         when the children were asked directly. This is in contrast to a prior
@@
 highlights the necessity to engage students in an interaction which will be sustainable
- over the long-term if we wish to move towards using the proposed system to answer 
-research questions which involve the measurement of learning gains to gauge effectiveness. 
+ over the long-term in order to answer 
+research questions which involve the measurement of learning gains. 
 Several challenges are raised in developing such long-term capabilities for the system,
- from both technical and socialogical points of view. %not sure this makes sense
+ from both technical and sociological points of view. %not sure this makes sense
 
@@
 technically autonomous, can not robustly recover from situations outside of the
-nominal protocol (presented in Section~\ref{sec4}), and consequently still
-requires the presence of an experimenter. The interaction state machine would
+nominal protocol presented in Section~\ref{sec4}, and consequently still
+requires the presence of an experimenter. The interaction finite state machine would
 require extension in non-trivial ways to allow for long, fully autonomous
@@
 to develop the conversational agent in the interaction so that the presence of an 
-experimenter is not required for a captivating engagement. While there is the 
+experimenter is not required for a captivating and continuing engagement. While there is the 
 possiblity to focus the interaction design on group-based interaction with the robot 
 in order to alleviate the necessity of a conversational agent, there is reason to 
-believe that constructing such a social interaction is not a trivial task. Anectodes 
+believe that constructing such a social interaction is not a trivial task. Anecdotes 
 from the preliminary studies have shown that some children may criticise another's 
@@
 particular letter, they did not discuss with each other their different writing styles 
-and the effect on the teaching efficiency. This may suggest that a social context in 
-which verbalising opinions about differences is encouraged is necessary to get children 
-to cooperate in teaching the robot.  
+and the effect on the teaching efficiency. This may suggest that a constructed social context in 
+which verbalising opinions about differences is encouraged may be necessary to get children 
+to cooperate in teaching the robot in a group setting.  
 %- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
@@
 for letters might be generated which capture the full range of mistakes typical
-of children learning handwriting: extending the current system capable of
+of children learning handwriting. This includes extending the current system capable of
 incorporating internal proportion and global deformation errors to one which can
 also generate missing subparts of the letter, or break the letter down into
-primitive strokes at will, for example. While we expect that incorporating a
+primitive strokes, for example. While it is expected that incorporating a
 database of letters drawn by children into the shape modeling process would
-facilitate this, the current system has conceptual (a PCA only approach can not
-generate or learn a different shape topology) and technical (no support for
-multi-stroke shapes) limitations which need to be overcome.
-
-If the system is extended to allow for a wider range of mistakes, a further question 
-then is how the handwriting error
+facilitate this, the current system has conceptual -- a PCA-only approach can not
+generate or learn a different shape topology -- and technical -- no support is currently implemented for
+multi-stroke shapes -- limitations which would need to be overcome.
+
+If the system is extended to allow for a wider range of mistakes, a further 
+topic for exploration then is how the handwriting error
 generation of the system may be abstracted to a higher level of control so that
 a teacher may configure it to work with a child on a particular type of
-mistakes, based on the child's performance. Where would the balance lie between
+mistakes based on the child's performance. Where would the balance lie between
 developing autonomous capabilities for the system to determine the child's
-difficulties, and empowering the teaching staff to decide for themselves
+difficulties and empowering the teaching staff to decide for themselves
 instead?
@@
 with the teachable robotic partner addressed, further steps can be made towards 
-answering the ultimate question of what impact to the outcomes of interventions the 
+answering the central question of what impact to the outcomes of interventions the 
 addition of such a teachable robotic agent would have, including the effect on the 
-participants' self-esteem, motivation, or learning gains. % does it impact the
+participants' self-esteem, motivation, and learning gains. % does it impact the
 %motivation of the participants, their self-esteem, and/or the learning gains
@@
 
-\addtolength{\textheight}{-.0cm}   % This command serves to balance the column lengths
+\addtolength{\textheight}{-.5cm}   % This command serves to balance the column lengths
                                   % on the last page of the document manually. It shortens
@@
     \item developing capabilities for a robot with limited fine motor
-        capabilities, such as the {\sc nao}, to engage in the act of handwriting in a
+        capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
         way which is believable for interacting with children. This has been
         accomplished by leveraging simulated handwriting with a synchronised
-        tablet;
+        tablet communicating via ROS;
 
@@
         by using statistical shape models through PCA of observations of the
-        trajectory of the same letter;
+        trajectory of the same letter;% * <deanna.m.hood@gmail.com> 2014-10-03T00:52:47.503Z:
+%
+% this is pretty "done before" so might want to play it down
+%
 
@@
 
-However, we believe that the strongest impact of this work for the human-robot
-interaction community relates to the very \emph{nature} of the interaction
+However, we believe that the strongest impact of this work is for the human-robot
+interaction community and relates to the very \emph{nature} of the interaction
 fostered by this research. The work presented here investigates a particular
-role for a robot in the education of handwriting: not only the robot is actively
-performing the activity (it draws letters), but it does so in a way that engages
-the child in a very specific social role. The child is the teacher, the robot is
+role for a robot in the education of handwriting: not only is the robot actively
+performing the activity by drawing letters, but it does so in a way that engages
+the child in a very specific social role. The child is the teacher in this relationship and the robot is
 the learner: the child must engage in a (meta-)cognitive relationship with the robot
 to try to understand why the robot fails and how to help it best.  Here, the
-robot is not only an activity facilitator or orchestrator: its physical presence
+robot is more than just an activity facilitator or orchestrator -- its physical presence
 and embodiment induce agency and anthropomorphising, and cognitively engage the
@@
 education, but instead in an activity -- handwriting -- which requires fine
-physical skills. In such activities, the embodied nature of the robot makes a
-lot of sense (due to motor mimicry, the arm motion for instance is, \emph{by
-itself}, part of the teaching). Along these lines, we hope to see more research
+physical skills. In such activities, the embodied nature of the robot is appropriate as in interventions where motor mimicry is elicited \cite{Berninger1997} the arm motion for instance is, \emph{by
+itself}, part of the teaching. Along these lines, we hope to see more research
 on non-STEM educational applications of robotics.
@@
 Beyond handwriting, we believe that this work provides a novel perspective on
-the role for robots in the education landscape. \emph{Learning by teaching} is a
+the role for robots in the field of education. \emph{Learning by teaching} is a
 powerful paradigm because of not only its pedagogical efficacy, but its
@@
 this article shows that this is a very relevant context of use for robots. Indeed,
-when facing a child with school difficulties, robots can play a role of a na\"ive 
-learner which neither the adults nor the peers (because of the social effects it would 
-induce) can convincingly play.
-
-The strong social impact of early educational problems makes research in this field
-an undoubtably meaningful challenge for HRI.
+when facing a child with school difficulties, robots can play the role of a na\"ive 
+learner which neither adults nor peers -- because of the social effects it would 
+induce -- can convincingly play.
+
+The strong social impact of early educational problems makes continued research in this field
+an undoubtably meaningful challenge for robotics and human-robot interaction.
 

### 2014-11-12 rebuttal.txt
Partially complete draft

> Reviews of submission #2155: ""Those who can't do, teach": a Teachable
> Robotic Agent for Children Learning Handwriting"

We would like to thank each of the reviewers for contributing such time and their expertise to this review.
>
> ------------------------ Submission 2155, Review 4 ------------------------
>
> Reviewer:           primary
>
> Expertise
>
>    3  (Knowledgeable)
>
> Summary of (Theme-specific) Contributions
>
>    This paper is a good fit for the Technologies theme since the central
>    focus and contribution relates to development of an autonomous
>    interactive system.
>
> Meta Review
>
>    The reviewers found the central focus of the paper compelling.  The paper
>    addresses an important research problem and the autonomous operation of
>    the robot during the teaching process is a significant strength of the
>    paper.  
>
>
>    The reviewers raised several concerns regarding the paper:
>
>    - The coverage of related work in the field of robotics is entirely
>    insufficient for a conference paper.
>
>    - The authors should consider revising the title of the paper, since it
>    could be seen as offensive to educators.
>
>    - Reviewers were divided in their comments regarding the writing style,
>    though all three reviewers had suggestions for improvement.  The authors
>    should make revisions to improve clarity, focus and level of detail in
>    certain sections, as outlined in the reviews.  Increased use of active
>    voice is also recommended.
>
>    - R1 raises a number of concerns regarding the soundness of the
>    methodology.  We encourage the authors to respond to these concerns in
>    their rebuttal comments.

We agree with each of the above points and address the reviewers' remarks below.

>
>    - One of the main contributions claimed by the authors, is the first
>    investigation of the use of robots in learning by teaching.  This
>    narrative will need to be significantly altered due to the presence of
>    prior work in this area, as listed in the reviews.  We recommend that
>    authors outline their plans for the relevant revisions in the rebuttal.

We did not intend to claim such a contribution, but we can understand how the misunderstanding can arise from the second-last paragraph and the missing related robotics work. Both will be modified.

>
> Recommendation
>
>    3  (Overall, I would not argue for or against this paper. I am truly on the fence.)
>
>
> ------------------------ Submission 2155, Review 1 ------------------------
>
> Reviewer:           external
>
> Expertise
>
>    4  (Expert)
>
> Summary of (Theme-specific) Contributions
>
>    This paper describes and attempts to validate aspects of an educational
>    robotic system that permits children to teach handwriting to the robot.
>
>    Author-claimed contributions:
>    1) A relatively inexpensive robot system that can write on a tablet in a
>    “believable” way (i.e., the child attributes the writing to the
>    robot).
>    2) PCA-based method for generating a range of letter styles, some of
>    which are of low quality, eliciting correction.
>    3) A component that converts child demonstrations of handwriting to an
>    incremental change in the parameter vector that the robot uses to
>    generate its letters, allowing the robot to learn from children’s
>    feedback.
>    4) An integrated system that autonomously learns handwriting from
>    children teachers.
>
>    These contributions fit the enabling technologies theme, but they appear
>    to fall short of the studies theme, since the account of the research
>    method is fairly high level (and missing some important information, as
>    discussed later) and it’s not clear that the result of this study is
>    “new understanding, principles, [or] design recommendations for HRI”.
>    Given that the paper fits the primary theme sufficiently, I do not
>    penalize it for falling short of the criteria for the studies theme.
>
> Strengths and Weaknesses
>
>    Strengths:
>
>    - A compelling application and an impressive system that mostly seems
>    well motivated.
>
>    - The topic is important and relevant to HRI.
>
>    - Good coverage of related work on the side of the educational aspect of
>    this work.
>

We concur.

>
>    Weaknesses:
>
>    - Related work lacks any citations of research on teachable robots or
>    agents or even robots or agents that act as educational characters, which
>    is unacceptable. (I’m not counting the apparent self-citation.) A
>    further consequence of this issue is that novelty is not sufficiently
>    addressed by the authors. This work needs to be properly situated.

We agree, and will remedy this in the revision. We will cover the work of others at the intersection of robotics and learning by teaching, and highlight the relevance of our work in the unexplored area of tasks with a physical component.

>
>    - The writing needs major revision, since it’s highly verbose, includes
>    poorly justified assertions, and is generally very difficult to read.
>    Despite the content of the research being very straightforward, I found
>    parsing most sentences/paragraphs of this paper quite frustrating. More
>    information in the Presentation section below.
>
>    - Some of the conclusions made about the system’s validation are poorly
>    justified. More info in the Soundness section.

We will address these points in the sections below.

>
>    - The authors appear to violate double-blindness in up to 3 ways: by
>    providing a URL to their code that contains “EPFL”, an apparent self
>    citation “Learning to write with a robot” from EPFL (given that this
>    paper claims to be the “first known robotic partner which children can
>    teach handwriting”, I assume that this citation is the same project),
>    and an apparent experimenter’s face appearing in Figure 8.

This was an oversight on our side and we apologise for letting it go undetected.

>
> Soundness
>
>    The authors do not assess how educational their system is. I can accept
>    that at this point in the research, which seems sufficient for a
>    conference publication. Instead, they attempt to validate the components
>    of their system. There is much to like in this validation: robot
>    interaction with a good number of children, adjustments to system design
>    based on observations, and autonomous interaction was largely successful
>    (i.e., didn’t need interventions unless robot fell over).
>
>    However, there are considerable issues with the methods and conclusions
>    within this validation.
>
>    (1) The authors claim their system can generate letters with
>    “inappropriate internal proportions” and “global deformations”
>    (which need definitions) based on the analysis described as follows:
>    “It would be reasonable to consider the shapes in Figure 2 in the same
>    general categories.” Calling something reasonable does not make it so.
>    The authors then make the unjustified claim that “sufficient
>    capabilities… have been demonstrated.”

We agree that this was a wording issue on our part and will make reference to the classification methods used in previous work to determine such categories.

>
>    (2) To assess whether the children believed that the letter-writing
>    trajectories shown on the tablet were being created by the robot, the
>    children were asked whether the robot could write its own name. This
>    question does not directly address believability, and there are plausible
>    interpretations of a “yes” answer that do not include the child
>    believing that the robot wrote what he or she saw on the tablet. For
>    instance, the child might think that the robot can write well but did not
>    actually write during the interaction. Thus, believability has not been
>    validated sufficiently. (Also, I recommend never saying that something is
>    generally “proven” when based on a limited sample.)

We agree with the points raised: it is a limitation of the question, which we imposed ourselves to avoid putting words in the children's mouths if we were to ask directly if the robot's writing was believable. Our argument is that at no point in the interaction did any child express that they did not believe that the robot was writing itself, even in a situation where they could have said "well, it's not *really* writing". We accept that we cannot conclude that the children believed it was writing, and will reword the outcome to instead be that no child ever expressed that they did not believe it was writing.

>
>    (3) “For example, for the model shown in Figure 1, the parameters may
>    represent the height of the top half of the letter compared to the bottom
>    half, the width of the overall shape, etc. Consequently, the shape
>    modelling process has produced the desired outcomes of parameterising the
>    shapes in ways which are able to be used to deform them meaningfully.”
>    - The author’s subjective appraisal of what variations are captured by
>    PCA is insufficient to claim the the deformations are meaningful.
>    Further, the word “meaningful” lacks grounding (what exactly does it
>    mean here)?

>
>    Additionally, more information is needed about the evaluation. How was
>    the initial parameter vector for a letter drawn? With what wording were
>    children asked whether they believed “the robot was learning and that
>    they were the ones teaching it”? For the robot-drawn letters that were
>    not “in response to demonstrations from the children”, were they all
>    from new words?
>
> Related Work
>
>    The authors do a good job of citing related work on the educational side
>    of their work. However, the paper must situate itself amongst other work
>    on robots and simulated agents that act as teachers, pupils, or
>    educational companions.
>
>    Relevant work includes Justin Werfel’s paper “Embodied Teachable
>    Agents: Learning by Teaching Robots”, Knox and Stone’s IJSR 2012
>    paper How Humans Teach Agents (which discusses the benefits of using
>    computational agents in lieu of human confederates in studies),
>    Tanaka’s “Children teach a care-receiving robot to promote their
>    learning: Field experiments in a classroom for vocabulary learning.”,
>    and Chase et al.’s “Teachable Agents and the Protege Effect…”.
>
>    On robots that interact educationally with people, there’s Kanda et
>    al.’s “Interactive robots as social partners and peer tutors for
>    children”, Kory and Breazeal’s “Storytelling with robots: Learning
>    companions for preschool children’s language development”, Leyzberg
>    et al.’s “Personalizing robot tutors to individuals’ learning
>    differences”, Chang et al.’s “Exploring the possibility of using
>    humanoid robots as instructional tools for teaching a second language in
>    primary school”, Johnson et al.’s “Design and early evaluation of
>    the rubi-5 sociable robots”, and Movellan et al.’s “Sociable robot
>    improves toddler vocabulary skills”.
>
> Presentation
>
>    The presentation is the largest issue with this paper. Issues with
>    examples are below.
>
>    - highly verbose (and often redundant)-
>
>    I think that this paper could be condensed to a 5-page paper without
>    losing any content. Doing so should also dramatically increase its
>    readability. Some examples of how writing could become more concise and
>    clearer are below.
>
>    Original: “An application which is yet to be explored, however, is that
>    of handwriting intervention.”
>
>    Revised (slightly shorter and with more connection to the previous
>    sentence): “Handwriting intervention is a previously unexplored
>    application of this paradigm.”
>
>    Original: “Presented is the development of the first known teachable
>    agent which is capable of artificially making mistakes typical of
>    children learning handwriting, and correcting them with external
>    feedback. Such a system therefore exhibits the potential to engage
>    children in the learning by teaching paradigm in the context of
>    handwriting.”
>
>    Revised: “We present the development of the first known teachable agent
>    that intentionally makes mistakes typical of children learning
>    handwriting. Through this capability, the robot can be taught by
>    children, who themselves may learn through their teaching.”
>
>    Original: “The robot responds to the word request verbally and writes
>    the letters by pointing at the tablet and imitating writing the letters.
>    The tablet, placed in front of the robot with a vertical, landscape
>    orientation, displays the letters in synchronisation with the robot’s
>    movements.”
>
>    Revised: “The robot writes the letters according to the method
>    described in Section X.”
>
>    An exception is the paragraph “However, we believe that…”, which is
>    concise and clear than the rest of the paper.
>
>    - vague writing -
>
>    “provides context for robotics in education” - What is meant by
>    context here?
>
>    “which is capable of generating the necessary letter models” -
>    Necessary according to what criteria?
>

All points have been well taken; we appreciate the examples provided.

>    “a shape center of 0” - What’s really meant here is that the
>    normalized trajectory points average 0, correct? (If so, this quotation
>    is both vague and incorrect, since the trajectory and the shape it makes
>    are not the same thing.)

We can clarify that we indeed refer to a shape centre of 0, not trajectory average.

>
>    - overuse of actor removal -
>
>    Perhaps in an attempt to strike a scholarly tone, the authors often
>    remove themselves as actors. There is some precedent for this in academic
>    writing, but here (and most places) it leads to ambiguity, a lack of
>    energy in the writing, and difficult-to-parse writing.
>
>    “The following conclusions were successfully drawn” - By whom? Easier
>    to read and more honest: “We drew the following conclusions”
>
>    “It was reasoned” -> “We reasoned”
>
>    “While it is expected that” -> “We expect that”
>
>    Honestly, I don’t actually know for sure who was doing the reasoning or
>    reporting their expectations above. I just assume it’s the authors. But
>    I don’t know because they removed the actor in these sentences.
>
>    - includes numerous poorly justified assertions and some bad logic -
>
>    Some larger examples are already in the Soundness section above, but
>    there are many smaller examples as well.
>
>    “experimentally proven to provide convincing scaffolding” -
>    Convincing according to what metric? Also, scaffolding itself was never
>    even mentioned before this (and thus was not actually assessed).
>
>    “tablet-based application, which children are increasingly recognizing
>    as a disposable technology.” This is a strong claim that lacks any
>    evidence or argumentation. It’s not even clear what it means for an app
>    to be “disposable”.
>
>    In point #2 at the end of the first page, the authors imply that a robot
>    can draw a letter but an app can only show it in a completely drawn state
>    (not draw it along a trajectory at handwriting speed), which is false.
>
>    - many long sentences that are difficult to read -
>
>    “With some of the challenges towards an engaging long- term handwriting
>    intervention with the teachable robotic partner addressed, further steps
>    can be made towards an- swering the central question of what impact to
>    the outcomes of interventions the addition of such a teachable robotic
>    agent would have, including the effect on the participants’
>    self-esteem, motivation, and learning gains.”
>
>    The last two bullets on the final page are much too long and difficult to
>    read.
>
>    Long sentences should be broken up for readability.
>
>    - definitions needed -
>
>    protege effect, inappropriate internal proportions, global deformations
>
> Suggestions
>
>    Please see above for specific suggestions.
>
>    Also, I recommend removing “Those who cannot do, teach” from the
>    title. This phrase is an insult to teachers, and it’s unclear how
>    it’s relevant to this work.

The title was meant to re-purpose the idiom in the context of children with handwriting difficulties having an opportunity to improve through teaching. We appreciate this reviewer bringing to light the potential for this to strike a nerve with teachers and will accept their recommendation.

>
> Recommendation
>
>    This paper describes compelling work on an important project, but it
>    needs to be revised with a fine-tooth comb to be more readable. Further,
>    the paper needs more rigor with regards to its assertions and attempts to
>    validate the system. I encourage the authors to revise and resubmit this
>    interesting research.

We are able to improve the writing style and, as the reviewer noted, the intention was to present new 'enabling technologies'

>
> Overall Rating
>
>    2  (Probably reject: I would argue for rejecting this paper.)
>
>
> ------------------------ Submission 2155, Review 2 ------------------------
>
> Reviewer:           external
>
> Expertise
>
>    4  (Expert)
>
> Summary of (Theme-specific) Contributions
>
>    This paper contributes an autonomous HRI system for children to improve
>    their handwriting by teaching a robot to improve its handwriting.

This is an accurate summary, though children improving handwriting is our motivation, not yet result.
>
> Strengths and Weaknesses
>
>    Originality: This work is original.
>
>    Novelty: This work is novel (although the authors should cite some
>    additional prior work on care-receiving robots; see the "Prior Work"
>    section of this review).
>
>    Relevance: This work is extremely relevant to HRI.
>
> Soundness
>
>    The work is very sound, although it's unclear which parts of the shape
>    modeling algorithm are novel.  This review is written under the
>    assumption that the idea of shape modeling is not novel, but that using
>    the model to generate "bad" examples is.  Otherwise, the system design
>    and evaluation are excellent.

This is accurate and will be clarified in the section on the shape modeling algorithm.

>
> Related Work
>
>    The authors should cite the following, which is directly relevant to
>    their work:
>
>    Tanaka, F., & Matsuzoe, S. (2012). Children Teach a Care-Receiving Robot
>    to Promote Their Learning: Field Experiments in a Classroom for
>    Vocabulary Learning. Journal of Human-Robot Interaction, 1(1).
>    doi:10.5898/jhri.v1i1.12
>
>    More background on handwriting recognition and generation might be
>    helpful for the reader who is not expert in that area.
>
> Presentation
>
>    The presentation is very good, although some of the technical details on
>    synchronization could be omitted in favor of providing more detail on the
>    studies described.  The section on the studies (4.2) could also be split
>    into several sections to improve readability.
>
> Suggestions
>
>    -- the authors should reduce their claims that the idea of the robot as a
>    learner is a novel contribution of this paper, given the citation above.
>    The work is sufficiently interesting without this in any case.
>    -- as the authors mention, it remains to be seen what the effect is of
>    the system on learning handwriting
>    -- as mentioned above, the authors should consider reducing the space
>    dedicated to the synchronization (a technical challenge, to be sure, but
>    not especially interesting from a research perspective) and dedicate more
>    attention to the studies.
>    -- the authors might address how their system can deal with and/or
>    produce mistakes that aren't just deformations; e.g. writing a letter
>    backwards.
>
> Recommendation
>
>    It is always exciting to see a fully-autonomous human-robot interaction
>    study with children.  The poor-handwriting generation algorithm is clever
>    and the results are promising for continuing work in this area.
>
> Overall Rating
>
>    5  (Definite accept: I would argue strongly for accepting this paper.)
>
>
> ------------------------ Submission 2155, Review 3 ------------------------
>
> Reviewer:           external
>
> Expertise
>
>    3  (Knowledgeable)
>
> Summary of (Theme-specific) Contributions
>
>    The authors have developed a system (NAO and a tablet) that can be
>    applied in an interaction with children to enhance their handwriting. The
>    focus of the paper is on the system development, and first observations
>    from the interaction study are provided.
>
> Strengths and Weaknesses
>
>    The paper describes an innovative task in which robots can interact with
>    children for pedagogical purposes. The motivation for this task is very
>    well researched. A fully autonomous system is put into the interaction.
>    Furthermore, even though the authors apply a quite known “learning by
>    teaching paradigm”, they extend the potential of it describing some
>    very interesting observations (second key point). Accordingly, other
>    children were observed to give advice to the child designated as the
>    letter demonstrator. This behavior bears high potential for being
>    analyzed in terms of what knowledge is negotiated by the group of
>    children.

We concur.

>
>    The weaknesses of the paper lay in the part, in which the results of the
>    interaction study are reported. Unfortunately, the presentation lacks any
>    standards. I got the impression that the analyses are ongoing. Only for
>    some observations (duration of a session), descriptive statistics are
>    provided.
>

We have provided also the number of demonstrations for each group, and have refrained from reading further into the data because a full study with large sample sizes has not been completed. The work presented was intended for verification of the technical soundness of the system with children, in line with the theme.

> Soundness
>
>    The paper is well written. The presentation of the results needs to
>    follow a more standardized outline.
>
> Related Work
>
>    I suggest that the authors take Tanaka and Matsuzoe’s (2012) work on
>    learning by teaching paradigm into account.
>
> Presentation
>
>    The presentation of the results needs to be revised. I suggest that the
>    authors specify information about: (i) the participants (what age groups
>    were interacting with the robot) and (ii) the procedure (by referring to
>    Figure 8).
>    Another problem is that as the results are presented now, it seems like
>    no dependent measures were taken. In one observation, the authors refer
>    to the children’s responses but they never mention how many children
>    provided this kind of answer. With respect to the different age groups
>    that interacted, the authors need to either to focus on one in their
>    results or to analyze how the interaction differed in these groups.

It will be more clearly stated that the results presented were from the 7-8yr age group, not those in the pilot study.

>
> Suggestions
>
>
> Recommendation
>
>    While the paper has some weaknesses, it should be included in the
>    technical program as it makes important and interesting contributions to
>    (1) the system design and task that can be used in interaction with
>    children and (2) the learning by teaching paradigm. In addition, I think
>    that the presentation of the results can be revised and improved by the
>    authors.
>
> Overall Rating
>
>    4  (Probably accept: I would argue for accepting this paper.)

### 2014-11-13 rebuttal.txt
Completing, reformatting the rebuttal

@@
-> Reviews of submission #2155: ""Those who can't do, teach": a Teachable
-> Robotic Agent for Children Learning Handwriting"
+We would like to thank each of the reviewers for contributing such time and
+their expertise to this review.
 
-We would like to thank each of the reviewers for contributing such time and their expertise to this review.
->
-> ------------------------ Submission 2155, Review 4 ------------------------
->
-> Reviewer:           primary
->
-> Expertise
->
->    3  (Knowledgeable)
->
-> Summary of (Theme-specific) Contributions
->
->    This paper is a good fit for the Technologies theme since the central
->    focus and contribution relates to development of an autonomous
->    interactive system.
->
-> Meta Review
->
->    The reviewers found the central focus of the paper compelling.  The paper
->    addresses an important research problem and the autonomous operation of
->    the robot during the teaching process is a significant strength of the
->    paper.  
->
->
->    The reviewers raised several concerns regarding the paper:
->
->    - The coverage of related work in the field of robotics is entirely
->    insufficient for a conference paper.
->
->    - The authors should consider revising the title of the paper, since it
->    could be seen as offensive to educators.
->
->    - Reviewers were divided in their comments regarding the writing style,
->    though all three reviewers had suggestions for improvement.  The authors
->    should make revisions to improve clarity, focus and level of detail in
->    certain sections, as outlined in the reviews.  Increased use of active
->    voice is also recommended.
->
->    - R1 raises a number of concerns regarding the soundness of the
->    methodology.  We encourage the authors to respond to these concerns in
->    their rebuttal comments.
+We address hereafter the reviewers' remarks.
 
-We agree with each of the above points and address the reviewers' remarks below.
+The main weakness raised by the reviewers is the lacking literature review.  We
+acknowledge this weakness and we certainly appreciate and value the numerous
+pointers provided by the reviewers. We propose to report in depth on these
+related works in the final version of the article.
 
->
->    - One of the main contributions claimed by the authors, is the first
->    investigation of the use of robots in learning by teaching.  This
->    narrative will need to be significantly altered due to the presence of
->    prior work in this area, as listed in the reviews.  We recommend that
->    authors outline their plans for the relevant revisions in the rebuttal.
+While the application of the 'learning by teaching' paradigm to robotics is not
+new (we did not intend to claim such a contribution anyway, but we can
+understand how the misunderstanding can arise from the second-last paragraph),
+it appears that 'learning by teaching' a task requiring fine physical skills
+like hand-writing is still novel, and of particular significance for embodied
+artifacts like robots.
 
-We did not intend to claim such a contribution, but we can understand how the misunderstanding can arise from the second-last paragraph and the missing related robotics work. Both will be modified.
+Regarding the overall writing style of the paper, the points raised by the
+reviewer 1 are well taken and we appreciate the examples provided. We will
+accordingly reword the article to match academic standards (including the
+removal of overstatements like 'we have proven that...').
 
->
-> Recommendation
->
->    3  (Overall, I would not argue for or against this paper. I am truly on the fence.)
->
->
-> ------------------------ Submission 2155, Review 1 ------------------------
->
-> Reviewer:           external
->
-> Expertise
->
->    4  (Expert)
->
-> Summary of (Theme-specific) Contributions
->
->    This paper describes and attempts to validate aspects of an educational
->    robotic system that permits children to teach handwriting to the robot.
->
->    Author-claimed contributions:
->    1) A relatively inexpensive robot system that can write on a tablet in a
->    “believable” way (i.e., the child attributes the writing to the
->    robot).
->    2) PCA-based method for generating a range of letter styles, some of
->    which are of low quality, eliciting correction.
->    3) A component that converts child demonstrations of handwriting to an
->    incremental change in the parameter vector that the robot uses to
->    generate its letters, allowing the robot to learn from children’s
->    feedback.
->    4) An integrated system that autonomously learns handwriting from
->    children teachers.
->
->    These contributions fit the enabling technologies theme, but they appear
->    to fall short of the studies theme, since the account of the research
->    method is fairly high level (and missing some important information, as
->    discussed later) and it’s not clear that the result of this study is
->    “new understanding, principles, [or] design recommendations for HRI”.
->    Given that the paper fits the primary theme sufficiently, I do not
->    penalize it for falling short of the criteria for the studies theme.
->
-> Strengths and Weaknesses
->
->    Strengths:
->
->    - A compelling application and an impressive system that mostly seems
->    well motivated.
->
->    - The topic is important and relevant to HRI.
->
->    - Good coverage of related work on the side of the educational aspect of
->    this work.
->
+The reviewers also raise several questions regarding the technical validation
+of the system.
 
-We concur.
+The characterization of the mistakes (like "global deformation" and "internal
+proportion") comes from an existing report (reference [2]). We propose to make
+an explicit reference to the classification methods used in this previous work
+to classify and evaluate mistakes generated by our algorithm.
 
->
->    Weaknesses:
->
->    - Related work lacks any citations of research on teachable robots or
->    agents or even robots or agents that act as educational characters, which
->    is unacceptable. (I’m not counting the apparent self-citation.) A
->    further consequence of this issue is that novelty is not sufficiently
->    addressed by the authors. This work needs to be properly situated.
+Reviewer 1 also questions our assessment of generated letters as being
+"meaningful" mistakes to the children: The deformations are meaningful in the
+sense that if a teacher wishes to create initial letters with a particular
+feature (a 'd' with a large loop, for example), it is possible with this
+system. We will clarify that it is the ability to create varied levels of
+deformations which may be ascribed descriptive interpretations (not just
+numerical) that is the desired outcome. We will also mention that the
+interpretation of the deformations has been directly (yet informally) validated
+during a focus group with 10 primary school teachers, prior to the studies.
 
-We agree, and will remedy this in the revision.
-We will cover the work of others at the intersection of robotics and learning by teaching, and highlight the relevance of our work in the unexplored area of tasks with a physical component.
+Regarding the initial parameters used to generate wrong letters during the
+validation studies, the values were drawn from a range chosen to generate
+shapes for letters 'e' and 's' which would elicit correction. For the other
+letters, parameters were fixed, generating shapes which some groups chose to
+correct (e.g. 13/14 for 'n' and 2/14 for 'c').
 
->
->    - The writing needs major revision, since it’s highly verbose, includes
->    poorly justified assertions, and is generally very difficult to read.
->    Despite the content of the research being very straightforward, I found
->    parsing most sentences/paragraphs of this paper quite frustrating. More
->    information in the Presentation section below.
->
->    - Some of the conclusions made about the system’s validation are poorly
->    justified. More info in the Soundness section.
+The question whether the robot is believed to write itself or not is a valid
+concern. The question "Do you think Nao could write its name?", while it does
+not directly check if the robot is believable, has been designed such as to
+avoid putting words in the children's mouths (if we were to ask directly if the
+robot's writing was believable). Our argument is that at no point in the
+interaction did any child express that they did not believe that the robot was
+writing itself, even in a situation where they could have said "well, it's not
+*really* writing". We accept that we cannot conclude that the children believed
+it was writing, and will reword the outcome to instead be that no child ever
+expressed that they did not believe it was writing.
 
-We will address these points in the sections below.
+Reviewer 3 feels that the reporting of experimental result is lacking academic
+standards: while we do already provide the fundamental demographic data and
+experimental result, we have refrained from reading further into the data
+because a full study with large sample sizes has yet to be completed. The work
+presented was intended for verification of the technical soundness of the
+system with children, in line with the theme.
 
->
->    - The authors appear to violate double-blindness in up to 3 ways: by
->    providing a URL to their code that contains “EPFL”, an apparent self
->    citation “Learning to write with a robot” from EPFL (given that this
->    paper claims to be the “first known robotic partner which children can
->    teach handwriting”, I assume that this citation is the same project),
->    and an apparent experimenter’s face appearing in Figure 8.
-
-This was an oversight on our side and we apologise for letting it go undetected.
-
->
-> Soundness
->
->    The authors do not assess how educational their system is. I can accept
->    that at this point in the research, which seems sufficient for a
->    conference publication. Instead, they attempt to validate the components
->    of their system. There is much to like in this validation: robot
->    interaction with a good number of children, adjustments to system design
->    based on observations, and autonomous interaction was largely successful
->    (i.e., didn’t need interventions unless robot fell over).
->
->    However, there are considerable issues with the methods and conclusions
->    within this validation.
->
->    (1) The authors claim their system can generate letters with
->    “inappropriate internal proportions” and “global deformations”
->    (which need definitions) based on the analysis described as follows:
->    “It would be reasonable to consider the shapes in Figure 2 in the same
->    general categories.” Calling something reasonable does not make it so.
->    The authors then make the unjustified claim that “sufficient
->    capabilities… have been demonstrated.”
-
-We agree that this was a wording issue on our part and will make reference to the classification methods used in previous work to determine such categories.
-
->
->    (2) To assess whether the children believed that the letter-writing
->    trajectories shown on the tablet were being created by the robot, the
->    children were asked whether the robot could write its own name. This
->    question does not directly address believability, and there are plausible
->    interpretations of a “yes” answer that do not include the child
->    believing that the robot wrote what he or she saw on the tablet. For
->    instance, the child might think that the robot can write well but did not
->    actually write during the interaction. Thus, believability has not been
->    validated sufficiently. (Also, I recommend never saying that something is
->    generally “proven” when based on a limited sample.)
-
-We agree with the points raised: it is a limitation of the question, which we imposed ourselves to avoid putting words in the children's mouths if we were to ask directly if the robot's writing was believable.
-Our argument is that at no point in the interaction did any child express that they did not believe that the robot was writing itself, even in a situation where they could have said "well, it's not *really* writing".
-We accept that we cannot conclude that the children believed it was writing, and will reword the outcome to instead be that no child ever expressed that they did not believe it was writing.
-
->
->    (3) “For example, for the model shown in Figure 1, the parameters may
->    represent the height of the top half of the letter compared to the bottom
->    half, the width of the overall shape, etc. Consequently, the shape
->    modelling process has produced the desired outcomes of parameterising the
->    shapes in ways which are able to be used to deform them meaningfully.”
->    - The author’s subjective appraisal of what variations are captured by
->    PCA is insufficient to claim the the deformations are meaningful.
->    Further, the word “meaningful” lacks grounding (what exactly does it
->    mean here)?
-
->
->    Additionally, more information is needed about the evaluation. How was
->    the initial parameter vector for a letter drawn? With what wording were
->    children asked whether they believed “the robot was learning and that
->    they were the ones teaching it”? For the robot-drawn letters that were
->    not “in response to demonstrations from the children”, were they all
->    from new words?
->
-> Related Work
->
->    The authors do a good job of citing related work on the educational side
->    of their work. However, the paper must situate itself amongst other work
->    on robots and simulated agents that act as teachers, pupils, or
->    educational companions.
->
->    Relevant work includes Justin Werfel’s paper “Embodied Teachable
->    Agents: Learning by Teaching Robots”, Knox and Stone’s IJSR 2012
->    paper How Humans Teach Agents (which discusses the benefits of using
->    computational agents in lieu of human confederates in studies),
->    Tanaka’s “Children teach a care-receiving robot to promote their
->    learning: Field experiments in a classroom for vocabulary learning.”,
->    and Chase et al.’s “Teachable Agents and the Protege Effect…”.
->
->    On robots that interact educationally with people, there’s Kanda et
->    al.’s “Interactive robots as social partners and peer tutors for
->    children”, Kory and Breazeal’s “Storytelling with robots: Learning
->    companions for preschool children’s language development”, Leyzberg
->    et al.’s “Personalizing robot tutors to individuals’ learning
->    differences”, Chang et al.’s “Exploring the possibility of using
->    humanoid robots as instructional tools for teaching a second language in
->    primary school”, Johnson et al.’s “Design and early evaluation of
->    the rubi-5 sociable robots”, and Movellan et al.’s “Sociable robot
->    improves toddler vocabulary skills”.
->
-> Presentation
->
->    The presentation is the largest issue with this paper. Issues with
->    examples are below.
->
->    - highly verbose (and often redundant)-
->
->    I think that this paper could be condensed to a 5-page paper without
->    losing any content. Doing so should also dramatically increase its
->    readability. Some examples of how writing could become more concise and
->    clearer are below.
->
->    Original: “An application which is yet to be explored, however, is that
->    of handwriting intervention.”
->
->    Revised (slightly shorter and with more connection to the previous
->    sentence): “Handwriting intervention is a previously unexplored
->    application of this paradigm.”
->
->    Original: “Presented is the development of the first known teachable
->    agent which is capable of artificially making mistakes typical of
->    children learning handwriting, and correcting them with external
->    feedback. Such a system therefore exhibits the potential to engage
->    children in the learning by teaching paradigm in the context of
->    handwriting.”
->
->    Revised: “We present the development of the first known teachable agent
->    that intentionally makes mistakes typical of children learning
->    handwriting. Through this capability, the robot can be taught by
->    children, who themselves may learn through their teaching.”
->
->    Original: “The robot responds to the word request verbally and writes
->    the letters by pointing at the tablet and imitating writing the letters.
->    The tablet, placed in front of the robot with a vertical, landscape
->    orientation, displays the letters in synchronisation with the robot’s
->    movements.”
->
->    Revised: “The robot writes the letters according to the method
->    described in Section X.”
->
->    An exception is the paragraph “However, we believe that…”, which is
->    concise and clear than the rest of the paper.
->
->    - vague writing -
->
->    “provides context for robotics in education” - What is meant by
->    context here?
->
->    “which is capable of generating the necessary letter models” -
->    Necessary according to what criteria?
->
-
-All points have been well taken; we appreciate the examples provided.
-
->    “a shape center of 0” - What’s really meant here is that the
->    normalized trajectory points average 0, correct? (If so, this quotation
->    is both vague and incorrect, since the trajectory and the shape it makes
->    are not the same thing.)
-
-We can clarify that we indeed refer to a shape centre of 0, not trajectory average.
-
->
->    - overuse of actor removal -
->
->    Perhaps in an attempt to strike a scholarly tone, the authors often
->    remove themselves as actors. There is some precedent for this in academic
->    writing, but here (and most places) it leads to ambiguity, a lack of
->    energy in the writing, and difficult-to-parse writing.
->
->    “The following conclusions were successfully drawn” - By whom? Easier
->    to read and more honest: “We drew the following conclusions”
->
->    “It was reasoned” -> “We reasoned”
->
->    “While it is expected that” -> “We expect that”
->
->    Honestly, I don’t actually know for sure who was doing the reasoning or
->    reporting their expectations above. I just assume it’s the authors. But
->    I don’t know because they removed the actor in these sentences.
->
->    - includes numerous poorly justified assertions and some bad logic -
->
->    Some larger examples are already in the Soundness section above, but
->    there are many smaller examples as well.
->
->    “experimentally proven to provide convincing scaffolding” -
->    Convincing according to what metric? Also, scaffolding itself was never
->    even mentioned before this (and thus was not actually assessed).
->
->    “tablet-based application, which children are increasingly recognizing
->    as a disposable technology.” This is a strong claim that lacks any
->    evidence or argumentation. It’s not even clear what it means for an app
->    to be “disposable”.
->
->    In point #2 at the end of the first page, the authors imply that a robot
->    can draw a letter but an app can only show it in a completely drawn state
->    (not draw it along a trajectory at handwriting speed), which is false.
->
->    - many long sentences that are difficult to read -
->
->    “With some of the challenges towards an engaging long- term handwriting
->    intervention with the teachable robotic partner addressed, further steps
->    can be made towards an- swering the central question of what impact to
->    the outcomes of interventions the addition of such a teachable robotic
->    agent would have, including the effect on the participants’
->    self-esteem, motivation, and learning gains.”
->
->    The last two bullets on the final page are much too long and difficult to
->    read.
->
->    Long sentences should be broken up for readability.
->
->    - definitions needed -
->
->    protege effect, inappropriate internal proportions, global deformations
->
-> Suggestions
->
->    Please see above for specific suggestions.
->
->    Also, I recommend removing “Those who cannot do, teach” from the
->    title. This phrase is an insult to teachers, and it’s unclear how
->    it’s relevant to this work.
-
-The title was meant to re-purpose the idiom in the context of children with handwriting difficulties having an opportunity to improve through teaching.
-We appreciate this reviewer bringing to light the potential for this to strike a nerve with teachers and will accept their recommendation.
-
->
-> Recommendation
->
->    This paper describes compelling work on an important project, but it
->    needs to be revised with a fine-tooth comb to be more readable. Further,
->    the paper needs more rigor with regards to its assertions and attempts to
->    validate the system. I encourage the authors to revise and resubmit this
->    interesting research.
-
-We are able to improve the writing style and, as the reviewer noted, the intention was to present new 'enabling technologies'
-
->
-> Overall Rating
->
->    2  (Probably reject: I would argue for rejecting this paper.)
->
->
-> ------------------------ Submission 2155, Review 2 ------------------------
->
-> Reviewer:           external
->
-> Expertise
->
->    4  (Expert)
->
-> Summary of (Theme-specific) Contributions
->
->    This paper contributes an autonomous HRI system for children to improve
->    their handwriting by teaching a robot to improve its handwriting.
-
-This is an accurate summary, though children improving handwriting is our motivation, not yet result.
->
-> Strengths and Weaknesses
->
->    Originality: This work is original.
->
->    Novelty: This work is novel (although the authors should cite some
->    additional prior work on care-receiving robots; see the "Prior Work"
->    section of this review).
->
->    Relevance: This work is extremely relevant to HRI.
->
-> Soundness
->
->    The work is very sound, although it's unclear which parts of the shape
->    modeling algorithm are novel.  This review is written under the
->    assumption that the idea of shape modeling is not novel, but that using
->    the model to generate "bad" examples is.  Otherwise, the system design
->    and evaluation are excellent.
-
-This is accurate and will be clarified in the section on the shape modeling algorithm.
-
->
-> Related Work
->
->    The authors should cite the following, which is directly relevant to
->    their work:
->
->    Tanaka, F., & Matsuzoe, S. (2012). Children Teach a Care-Receiving Robot
->    to Promote Their Learning: Field Experiments in a Classroom for
->    Vocabulary Learning. Journal of Human-Robot Interaction, 1(1).
->    doi:10.5898/jhri.v1i1.12
->
->    More background on handwriting recognition and generation might be
->    helpful for the reader who is not expert in that area.
->
-> Presentation
->
->    The presentation is very good, although some of the technical details on
->    synchronization could be omitted in favor of providing more detail on the
->    studies described.  The section on the studies (4.2) could also be split
->    into several sections to improve readability.
->
-> Suggestions
->
->    -- the authors should reduce their claims that the idea of the robot as a
->    learner is a novel contribution of this paper, given the citation above.
->    The work is sufficiently interesting without this in any case.
->    -- as the authors mention, it remains to be seen what the effect is of
->    the system on learning handwriting
->    -- as mentioned above, the authors should consider reducing the space
->    dedicated to the synchronization (a technical challenge, to be sure, but
->    not especially interesting from a research perspective) and dedicate more
->    attention to the studies.
->    -- the authors might address how their system can deal with and/or
->    produce mistakes that aren't just deformations; e.g. writing a letter
->    backwards.
->
-> Recommendation
->
->    It is always exciting to see a fully-autonomous human-robot interaction
->    study with children.  The poor-handwriting generation algorithm is clever
->    and the results are promising for continuing work in this area.
->
-> Overall Rating
->
->    5  (Definite accept: I would argue strongly for accepting this paper.)
->
->
-> ------------------------ Submission 2155, Review 3 ------------------------
->
-> Reviewer:           external
->
-> Expertise
->
->    3  (Knowledgeable)
->
-> Summary of (Theme-specific) Contributions
->
->    The authors have developed a system (NAO and a tablet) that can be
->    applied in an interaction with children to enhance their handwriting. The
->    focus of the paper is on the system development, and first observations
->    from the interaction study are provided.
->
-> Strengths and Weaknesses
->
->    The paper describes an innovative task in which robots can interact with
->    children for pedagogical purposes. The motivation for this task is very
->    well researched. A fully autonomous system is put into the interaction.
->    Furthermore, even though the authors apply a quite known “learning by
->    teaching paradigm”, they extend the potential of it describing some
->    very interesting observations (second key point). Accordingly, other
->    children were observed to give advice to the child designated as the
->    letter demonstrator. This behavior bears high potential for being
->    analyzed in terms of what knowledge is negotiated by the group of
->    children.
-
-We concur.
-
->
->    The weaknesses of the paper lay in the part, in which the results of the
->    interaction study are reported. Unfortunately, the presentation lacks any
->    standards. I got the impression that the analyses are ongoing. Only for
->    some observations (duration of a session), descriptive statistics are
->    provided.
->
-
-We have provided also the number of demonstrations for each group, and have refrained from reading further into the data because a full study with large sample sizes has not been completed.
-The work presented was intended for verification of the technical soundness of the system with children, in line with the theme.
-
-> Soundness
->
->    The paper is well written. The presentation of the results needs to
->    follow a more standardized outline.
->
-> Related Work
->
->    I suggest that the authors take Tanaka and Matsuzoe’s (2012) work on
->    learning by teaching paradigm into account.
->
-> Presentation
->
->    The presentation of the results needs to be revised. I suggest that the
->    authors specify information about: (i) the participants (what age groups
->    were interacting with the robot) and (ii) the procedure (by referring to
->    Figure 8).
->    Another problem is that as the results are presented now, it seems like
->    no dependent measures were taken. In one observation, the authors refer
->    to the children’s responses but they never mention how many children
->    provided this kind of answer. With respect to the different age groups
->    that interacted, the authors need to either to focus on one in their
->    results or to analyze how the interaction differed in these groups.
-
-It will be more clearly stated that the results presented were from the 7-8yr age group, not those in the pilot study.
-
->
-> Suggestions
->
->
-> Recommendation
->
->    While the paper has some weaknesses, it should be included in the
->    technical program as it makes important and interesting contributions to
->    (1) the system design and task that can be used in interaction with
->    children and (2) the learning by teaching paradigm. In addition, I think
->    that the presentation of the results can be revised and improved by the
->    authors.
->
-> Overall Rating
->
->    4  (Probably accept: I would argue for accepting this paper.)
+Finally, following the reviewers' suggestion, we propose the change the article
+title: it was meant to re-purpose the idiom "Those who cannot do, teach" in the
+context of children with handwriting difficulties having an opportunity to
+improve through teaching. We appreciate this reviewer bringing to light the
+potential for this to strike a nerve with teachers.

### 2014-11-13 rebuttal_sorted.txt
additional comments, removed compliments

> Reviews of submission #2155: ""Those who can't do, teach": a Teachable
> Robotic Agent for Children Learning Handwriting"

We would like to thank each of the reviewers for contributing such time and their expertise to this review.
We address the reviewers' remarks below.

>    - One of the main contributions claimed by the authors, is the first
>    investigation of the use of robots in learning by teaching.  This
>    narrative will need to be significantly altered due to the presence of
>    prior work in this area, as listed in the reviews.  We recommend that
>    authors outline their plans for the relevant revisions in the rebuttal.

>    -- the authors should reduce their claims that the idea of the robot as a
>    learner is a novel contribution of this paper, given the citation above.
>    The work is sufficiently interesting without this in any case.

We did not intend to claim such a contribution, but we can understand how the misunderstanding can arise from the second-last paragraph and the missing related robotics work. Both will be modified.

>    - Related work lacks any citations of research on teachable robots or
>    agents or even robots or agents that act as educational characters, which
>    is unacceptable. (I’m not counting the apparent self-citation.) A
>    further consequence of this issue is that novelty is not sufficiently
>    addressed by the authors. This work needs to be properly situated.

We agree and greatly appreciate the numerous provided pointers to the literature. 
After accordingly reconsidering the literature on learning by teaching in robotics -- that we will appropriately present --, it
appears that learning by teaching applied to a task with a physical component is still 100% novel.

>    The presentation is the largest issue with this paper. Issues with
>    examples are below.
>
>    - highly verbose (and often redundant)-
>
>    I think that this paper could be condensed to a 5-page paper without
>    losing any content. Doing so should also dramatically increase its
>    readability. Some examples of how writing could become more concise and
>    clearer are below.

>    - vague writing -
>
>    “provides context for robotics in education” - What is meant by
>    context here?
>
>    “which is capable of generating the necessary letter models” -
>    Necessary according to what criteria?

All points have been well taken and the feedback will be incorporated to improve readability.

>    Also, I recommend removing “Those who cannot do, teach” from the
>    title. This phrase is an insult to teachers, and it’s unclear how
>    it’s relevant to this work.

The title was meant to re-purpose the idiom in the context of children with handwriting difficulties having an opportunity to improve through teaching. We appreciate this reviewer bringing to light the potential for this to strike a nerve with teachers and will accept their recommendation.

>    The weaknesses of the paper lay in the part, in which the results of the
>    interaction study are reported. Unfortunately, the presentation lacks any
>    standards. I got the impression that the analyses are ongoing. Only for
>    some observations (duration of a session), descriptive statistics are
>    provided.

We have provided also the number of demonstrations for each group, and have refrained from reading further into the data because a full study with large sample sizes has not been completed. The work presented was intended for verification of the technical soundness of the system with children, in line with the theme.

>    The authors do not assess how educational their system is. I can accept
>    that at this point in the research, which seems sufficient for a
>    conference publication. Instead, they attempt to validate the components
>    of their system. There is much to like in this validation: robot
>    interaction with a good number of children, adjustments to system design
>    based on observations, and autonomous interaction was largely successful
>    (i.e., didn’t need interventions unless robot fell over).
>
>    However, there are considerable issues with the methods and conclusions
>    within this validation.
>
>    (1) The authors claim their system can generate letters with
>    “inappropriate internal proportions” and “global deformations”
>    (which need definitions) based on the analysis described as follows:
>    “It would be reasonable to consider the shapes in Figure 2 in the same
>    general categories.” Calling something reasonable does not make it so.
>    The authors then make the unjustified claim that “sufficient
>    capabilities… have been demonstrated.”

We agree that this was a wording issue on our part and will make reference to the classification methods used in previous work to determine such categories, and the confirmation that was received by teachers that the deformations are similar to childrens'.

>    (2) To assess whether the children believed that the letter-writing
>    trajectories shown on the tablet were being created by the robot, the
>    children were asked whether the robot could write its own name. This
>    question does not directly address believability, and there are plausible
>    interpretations of a “yes” answer that do not include the child
>    believing that the robot wrote what he or she saw on the tablet. For
>    instance, the child might think that the robot can write well but did not
>    actually write during the interaction. Thus, believability has not been
>    validated sufficiently. (Also, I recommend never saying that something is
>    generally “proven” when based on a limited sample.)

We agree with the points raised: it is a limitation of the question, which we imposed ourselves to avoid putting words in the children's mouths if we were to ask directly if the robot's writing was believable. Our argument is that at no point in the interaction did any child express that they did not believe that the robot was writing itself, even in a situation where they could have said "well, it's not *really* writing". We accept that we cannot conclude that the children believed it was writing, and will reword the outcome to instead be that no child ever expressed that they did not believe it was writing.

>    (3) “For example, for the model shown in Figure 1, the parameters may
>    represent the height of the top half of the letter compared to the bottom
>    half, the width of the overall shape, etc. Consequently, the shape
>    modelling process has produced the desired outcomes of parameterising the
>    shapes in ways which are able to be used to deform them meaningfully.”
>    - The author’s subjective appraisal of what variations are captured by
>    PCA is insufficient to claim the the deformations are meaningful.
>    Further, the word “meaningful” lacks grounding (what exactly does it
>    mean here)?

The deformations are meaningful in the sense that if a teacher wishes to create initial letters with a particular feature (a 'd' with a large loop, for example), it is possible with this system. We will clarify that it is the ability to create varied levels of deformations which may be ascribed descriptive interpretations (not just numerical) that is the desired outcome.

>    Additionally, more information is needed about the evaluation. How was
>    the initial parameter vector for a letter drawn? With what wording were
>    children asked whether they believed “the robot was learning and that
>    they were the ones teaching it”?

Initial parameters were drawn from a range chosen to generate shapes for letters 'e' and 's' which would elicit correction. For the other letters, parameters were fixed, generating shapes which some groups chose to correct (e.g. 13/14 for 'n' and 2/14 for 'c'). We agree that more detail is to be included about the wording of the questions to support the claims, and can include the information on both.

>    The authors do a good job of citing related work on the educational side
>    of their work. However, the paper must situate itself amongst other work
>    on robots and simulated agents that act as teachers, pupils, or
>    educational companions.
>
>    Relevant work includes Justin Werfel’s paper “Embodied Teachable
>    Agents: Learning by Teaching Robots”, Knox and Stone’s IJSR 2012
>    paper How Humans Teach Agents (which discusses the benefits of using
>    computational agents in lieu of human confederates in studies),
>    Tanaka’s “Children teach a care-receiving robot to promote their
>    learning: Field experiments in a classroom for vocabulary learning.”,
>    and Chase et al.’s “Teachable Agents and the Protege Effect…”.
>
>    On robots that interact educationally with people, there’s Kanda et
>    al.’s “Interactive robots as social partners and peer tutors for
>    children”, Kory and Breazeal’s “Storytelling with robots: Learning
>    companions for preschool children’s language development”, Leyzberg
>    et al.’s “Personalizing robot tutors to individuals’ learning
>    differences”, Chang et al.’s “Exploring the possibility of using
>    humanoid robots as instructional tools for teaching a second language in
>    primary school”, Johnson et al.’s “Design and early evaluation of
>    the rubi-5 sociable robots”, and Movellan et al.’s “Sociable robot
>    improves toddler vocabulary skills”.

Again, we agree and will comply, and would like to thank the reviewer for their time in compiling this list.

>    - The authors appear to violate double-blindness in up to 3 ways: by
>    providing a URL to their code that contains “EPFL”, an apparent self
>    citation “Learning to write with a robot” from EPFL (given that this
>    paper claims to be the “first known robotic partner which children can
>    teach handwriting”, I assume that this citation is the same project),
>    and an apparent experimenter’s face appearing in Figure 8.

This was an oversight on our side and we apologise for letting it go undetected.

>    “a shape center of 0” - What’s really meant here is that the
>    normalized trajectory points average 0, correct? (If so, this quotation
>    is both vague and incorrect, since the trajectory and the shape it makes
>    are not the same thing.)

We can clarify that we indeed refer to a shape with its centre at the origin, not 0-average trajectory.

>    - overuse of actor removal -
>
>    Perhaps in an attempt to strike a scholarly tone, the authors often
>    remove themselves as actors. There is some precedent for this in academic
>    writing, but here (and most places) it leads to ambiguity, a lack of
>    energy in the writing, and difficult-to-parse writing.
>
>    “The following conclusions were successfully drawn” - By whom? Easier
>    to read and more honest: “We drew the following conclusions”
>
>    “It was reasoned” -> “We reasoned”
>
>    “While it is expected that” -> “We expect that”
>
>    Honestly, I don’t actually know for sure who was doing the reasoning or
>    reporting their expectations above. I just assume it’s the authors. But
>    I don’t know because they removed the actor in these sentences.
>
>    - includes numerous poorly justified assertions and some bad logic -
>
>    Some larger examples are already in the Soundness section above, but
>    there are many smaller examples as well.
>
>    “experimentally proven to provide convincing scaffolding” -
>    Convincing according to what metric? Also, scaffolding itself was never
>    even mentioned before this (and thus was not actually assessed).
>
>    “tablet-based application, which children are increasingly recognizing
>    as a disposable technology.” This is a strong claim that lacks any
>    evidence or argumentation. It’s not even clear what it means for an app
>    to be “disposable”.
>
>    In point #2 at the end of the first page, the authors imply that a robot
>    can draw a letter but an app can only show it in a completely drawn state
>    (not draw it along a trajectory at handwriting speed), which is false.
>
>    - many long sentences that are difficult to read -
>
>    “With some of the challenges towards an engaging long- term handwriting
>    intervention with the teachable robotic partner addressed, further steps
>    can be made towards an- swering the central question of what impact to
>    the outcomes of interventions the addition of such a teachable robotic
>    agent would have, including the effect on the participants’
>    self-esteem, motivation, and learning gains.”
>
>    The last two bullets on the final page are much too long and difficult to
>    read.
>
>    Long sentences should be broken up for readability.
>
>    - definitions needed -
>
>    protege effect, inappropriate internal proportions, global deformations

We agree with each of the points made; they will be addressed.

>    The work is very sound, although it's unclear which parts of the shape
>    modeling algorithm are novel.  This review is written under the
>    assumption that the idea of shape modeling is not novel, but that using
>    the model to generate "bad" examples is.  Otherwise, the system design
>    and evaluation are excellent.

This is accurate and will be clarified in the section on the shape modeling algorithm.

>    -- as mentioned above, the authors should consider reducing the space
>    dedicated to the synchronization (a technical challenge, to be sure, but
>    not especially interesting from a research perspective) and dedicate more
>    attention to the studies.

We believe the technical details to be relevant for those wishing to replicate the new technology presented.

>    -- the authors might address how their system can deal with and/or
>    produce mistakes that aren't just deformations; e.g. writing a letter
>    backwards.

We agree that this is interesting future work; it has been mentioned on page 7.

>    The presentation of the results needs to be revised. I suggest that the
>    authors specify information about: (i) the participants (what age groups
>    were interacting with the robot) and (ii) the procedure (by referring to
>    Figure 8).
>    Another problem is that as the results are presented now, it seems like
>    no dependent measures were taken. In one observation, the authors refer
>    to the children’s responses but they never mention how many children
>    provided this kind of answer. With respect to the different age groups
>    that interacted, the authors need to either to focus on one in their
>    results or to analyze how the interaction differed in these groups.

It will be more clearly stated that the results presented were from the 7-8yr age group only, not those aged 6-7 in the pilot study.

>    For the robot-drawn letters that were
>    not “in response to demonstrations from the children”, were they all
>    from new words?

Yes, we will clarify.

### 2014-11-14 rebuttal.txt
small changes

@@
 acknowledge this weakness and we certainly appreciate and value the numerous
-pointers provided by the reviewers. We propose to report in depth on these
+pointers provided by the reviewers. We propose to report on and situate ourselves amongst these
 related works in the final version of the article.
@@
 While the application of the 'learning by teaching' paradigm to robotics is not
-new (we did not intend to claim such a contribution anyway, but we can
+new (we did not intend to claim such a contribution, but we can
 understand how the misunderstanding can arise from the second-last paragraph),
-it appears that 'learning by teaching' a task requiring fine physical skills
-like hand-writing is still novel, and of particular significance for embodied
+it appears that 'learning by teaching' a task requiring physical skills
+(especially fine physical skills, as in handwriting) is still novel, and of particular significance for embodied
 artifacts like robots.
 
-Regarding the overall writing style of the paper, the points raised by the
+Regarding the overall writing style of the paper, the points raised by
 reviewer 1 are well taken and we appreciate the examples provided. We will
@@
 an explicit reference to the classification methods used in this previous work
-to classify and evaluate mistakes generated by our algorithm.
+to classify and evaluate mistakes generated by our algorithm. We will also mention that the
+ deformations have been directly (yet informally) validated
+during a focus group with primary school teachers, prior to the studies.
 
-Reviewer 1 also questions our assessment of generated letters as being
-"meaningful" mistakes to the children: The deformations are meaningful in the
+Reviewer 1 also questions our assessment of generated letter models as being
+"meaningful": The deformations are meaningful in the
 sense that if a teacher wishes to create initial letters with a particular
@@
 deformations which may be ascribed descriptive interpretations (not just
-numerical) that is the desired outcome. We will also mention that the
-interpretation of the deformations has been directly (yet informally) validated
-during a focus group with 10 primary school teachers, prior to the studies.
+numerical) that is the desired outcome.
 
@@
 
-The question whether the robot is believed to write itself or not is a valid
+The question whether the robot is believed to write by itself or not is a valid
 concern. The question "Do you think Nao could write its name?", while it does
@@
 
-Reviewer 3 feels that the reporting of experimental result is lacking academic
+Reviewer 3 feels that the reporting of results is lacking academic
 standards: while we do already provide the fundamental demographic data and
-experimental result, we have refrained from reading further into the data
+verification results, we have refrained from reading further into the data
 because a full study with large sample sizes has yet to be completed. The work
 presented was intended for verification of the technical soundness of the
-system with children, in line with the theme.
+system with children, in line with the 'enabling technologies' theme.
 
-Finally, following the reviewers' suggestion, we propose the change the article
+Finally, following the reviewers' suggestion, we propose to change the article
 title: it was meant to re-purpose the idiom "Those who cannot do, teach" in the

### 2014-11-27 rebuttal_sorted.txt
Respond to r1 'meaningful' concerns

@@
 >    mean here)?
-
+DONE
 The deformations are meaningful in the sense that if a teacher wishes to create initial letters with a particular feature (a 'd' with a large loop, for example), it is possible with this system.

### 2014-11-27 main.tex
Respond to r1 'meaningful' concerns

@@
 
-%(DH) is it too soon to claim learning by teaching benefits in the title...? 
-%(DH) the paper is not about "learning handwriting", it's about the robot.
 \title{\LARGE \bf
-``Those Who Can't Do, Teach'': A Teachable Robotic Agent for Children Learning Handwriting
+A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself %make better
 }
 
-% \numberofauthors{3} 
-% \author{
-% \alignauthor
-% Deanna Hood\\
-% Séverin Lemaignan\\
-% Pierre Dillenbourg\\
-%    \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
-%    \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
-%    \affaddr{CH-1015 Lausanne, Switzerland}\\
-%    \email{firstname.lastname@epfl.ch}
+\numberofauthors{3} 
+\author{
+\alignauthor
+Deanna Hood\\
+Séverin Lemaignan\\
+Pierre Dillenbourg\\
+   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
+   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
+   %\affaddr{CH-1015 Lausanne, Switzerland}\\
+   \email{firstname.lastname@epfl.ch}
 % \alignauthor
@@
 %    \affaddr{Girona, Spain}
-% }
+}
 
@@
 the height of the top half of the letter compared to the bottom half, the width
-of the overall shape, etc. Consequently, the shape modelling process has
-produced the desired outcomes of parameterising the shapes in ways which are
-able to be used to deform them meaningfully.
+of the overall shape, etc. The ability to create varied levels of deformations
+which may be ascribed descriptive interpretations (not just numerical) is an
+advantage of this method, given its context of use. If a teacher wishes to
+create initial letters with a particular feature (a wide `s' or a `d' with a
+large loop, for example), it is possible with this system.
 

### 2014-11-27 rebuttal_sorted.txt
R1 shape centre clarification

@@
 >    are not the same thing.)
-
+DONE
 We can clarify that we indeed refer to a shape with its centre at the origin, not 0-average trajectory.

### 2014-11-27 main.tex
R1 shape centre clarification
R1 robot letter not in response to corrections

@@
 where $x_i$ and $y_i$ represent the coordinates of each of the points along the
-path. The observation shapes are normalised such that they have a shape
-centre of ${\bf 0}$ and a unit maximum dimension.
+path. The observation shapes are normalised to have a unit maximum dimension 
+and centre at the origin.
 
@@
         autonomous interaction.} The interaction setup including the teachable
-        robotic agent withstood the interaction for a total of 160 minutes, with
-        the robot writing 335 letters, 152 of which in response to
-        demonstrations received from the 21 children. During this time, technical 
+        robotic agent withstood the interaction for a total of 160 minutes. During this
+        time the robot wrote 335 letters, 152 of which in response to
+        demonstrations received from the 21 children and the remaining while writing 
+        new words. During this time, technical 
 	intervention was only required for the three instances that the robot fell 

### 2014-11-27 main.tex
R2 make clearer that shape models weren't our contribution

@@
 We believe that this article introduces three noteworthy contributions: an innovative
-application of data processing and artificial intelligence for the generation and
+application of data processing and artificial intelligence for the
 learning of hand-written letters suitable for educative purposes; a robotic
@@
 
-    \item developing a system for generating poorly written letters appropriate
-        for simulating a na\"ive learner in the context of handwriting, achieved
-        by using statistical shape models through PCA of observations of the
-        trajectory of the same letter;% * <deanna.m.hood@gmail.com> 2014-10-03T00:52:47.503Z:
-%
-% this is pretty "done before" so might want to play it down
-%
-
     \item developing an algorithm capable of incorporating user feedback and
-        demonstrations in order to adapt the generated handwriting quality so as
+        demonstrations in order to adapt artificially generated handwriting quality so as
         to simulate a teachable agent, which has been implemented by maintaining
-        a learning algorithm in the parameter space of the shape models and
+        a learning algorithm in the parameter space of the PCA-based shape models and
         converging towards the parameters of user demonstrations; and

### 2014-11-27 rebuttal_sorted.txt
R1 robot letter not in response to corrections
R2 make clearer that shape models weren't our contribution
R1 initial parameters

@@
 >    Additionally, more information is needed about the evaluation. How was
->    the initial parameter vector for a letter drawn? With what wording were
+>    the initial parameter vector for a letter drawn? 
+DONE
+
+>    With what wording were
 >    children asked whether they believed “the robot was learning and that
@@
 >    and evaluation are excellent.
-
+DONE
 This is accurate and will be clarified in the section on the shape modeling algorithm.
@@
 >    from new words?
-
+DONE
 Yes, we will clarify.

### 2014-11-27 main.tex
R1 initial parameters
R1 abstract 'context of robotics outside coding' concern

@@
 insight into children's use of the novel system. 
-%The technical components of the system have been validated, in that children 
-Children aged 6-8 were successfully led to believe that the robot was
-actually writing on the tablet, and were able to improve the robot's writing to a
-level which they were satisfied with, validating the interaction.
-
-Furthermore, the system represents a
-significant step towards an innovative use for robotics which addresses a
-wide-spread and socially meaningful challenge in education, and provides context
-for robotics in education beyond the well-explored use of teaching coding and
-robotics-related subjects.
+Children aged 6-8 were successfully able to engage with the robot and to improve its 
+writing to a level which they were satisfied with. The validation of the interaction
+represents a significant step towards an innovative use for robotics which addresses a
+widespread and socially meaningful challenge in education.
+
+%, and provides context
+%for robotics in education beyond the well-explored use of teaching coding and
+%robotics-related subjects.
 
@@
 14 students interacting with the robot in pairs. The duration of the sessions
-was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). % * <deanna.m.hood@gmail.com> 2014-09-05T09:25:41.865Z:
-%
-% We prompted them when time was short, didn't we? Or did they just say test
-% whenever they wanted to...
-%
+was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). 
+Initial parameters were drawn from a range purposely chosen to generate shapes 
+for letters 'e' and 's' which would elicit correction. For the other letters, 
+parameters were fixed, generating shapes which some groups chose to correct 
+(e.g. 13/14 for 'n' and 2/14 for 'c').
 

### 2014-11-27 main.tex
Don't allude to LBT novelty

@@
 physical skills. In such activities, the embodied nature of the robot is appropriate as in interventions where motor mimicry is elicited \cite{Berninger1997} the arm motion for instance is, \emph{by
-itself}, part of the teaching. Along these lines, we hope to see more research
+itself}, part of the teaching. Furthermore, when facing a child with school 
+difficulties, robots can play the role of a na\"ive learner which neither adults 
+nor peers -- because of the social effects it would induce -- can convincingly 
+play. Along these lines, we hope to see more research
 on non-STEM educational applications of robotics.
 
-Beyond handwriting, we believe that this work provides a novel perspective on
-the role for robots in the field of education. \emph{Learning by teaching} is a
-powerful paradigm because of not only its pedagogical efficacy, but its
-potential to positively impact the child's motivation and self-esteem. We hope that 
-this article shows that this is a very relevant context of use for robots. Indeed,
-when facing a child with school difficulties, robots can play the role of a na\"ive 
-learner which neither adults nor peers -- because of the social effects it would 
-induce -- can convincingly play.
+% Beyond handwriting, we believe that this work provides a novel perspective on
+% the role for robots in the field of education. \emph{Learning by teaching} is a
+% powerful paradigm because of not only its pedagogical efficacy, but its
+% potential to positively impact the child's motivation and self-esteem. We hope that 
+% this article shows that this is a very relevant context of use for robots. Indeed,
+% when facing a child with school difficulties, robots can play the role of a na\"ive 
+% learner which neither adults nor peers -- because of the social effects it would 
+% induce -- can convincingly play.
 

### 2014-11-27 main.tex
R1 'necessary letter models' statement

@@
 For the development of a learning algorithm in the context of
-handwriting, a parameterisation of letters and their deformities was sought
-which is capable of generating the necessary letter models. Depending on the parameters input to
-the letter models, different quality shapes should be generated. The system can
-therefore be configured to improve its writing by modifying the parameters used
-to generate the letters, based on feedback from the reinforcement learning
-partner. To this end, a method which can generate a model from real-world data
-has been employed in order to capture realistic variations in letters.
+handwriting, a parameterisation of letters and their deformities was sought such 
+that different quality shapes can be generated, depending on the parameters input to
+the letter models. This allows the system to be configured to improve its writing 
+by modifying the parameters used to generate the letters, based on feedback from the 
+reinforcement learning partner as addressed in Section \ref{sec:learningAlg}. 
+%To this end, a method which can generate a model from real-world data
+%has been employed in order to capture realistic variations in letters.
 
@@
 
-\subsection{Responding to Feedback}
+\subsection{Responding to Feedback}\label{sec:learningAlg}
 

### 2014-12-02 main.tex
Clarity and conciseness of technical sections

@@
 
-This article presents the first known robotic partner which children can teach handwriting. It is
-hypothesised that such a system could not just engage an unmotivated student,
-but could also present the opportunity for children to experience the typical
-benefits encountered during human-led handwriting interventions, such as motor
-mimicry. Moreover, this system allows for exploring the potential for the
+This article presents the first known robotic partner which children can teach handwriting. 
+The system allows for the
 \emph{learning by teaching} paradigm to be employed in the interaction, so as to
 stimulate meta-cognition, empathy and increased self-esteem in the child user. 
+It is
+hypothesised that use of a humanoid robot in such a system could not just engage an unmotivated student,
+but could also present the opportunity for children to experience physically-induced
+benefits encountered during human-led handwriting interventions, such as motor
+mimicry.
 
@@
 humanoid robot with limited fine motor capabilities has been configured as a
-suitably embodied handwriting partner. Shape models derived from principal
-component analysis of a dataset of letter trajectories have been generated, and allow
-the robot to draw purposefully deformed letters. Learning how to write
-characters well is then achieved by incorporating feedback from user
-demonstrations, which allows the system to learn the optimal parameters for the
+suitably embodied handwriting partner. Statistical shape models derived from principal
+component analysis of a dataset of adult-written letter trajectories allow
+the robot to draw purposefully deformed letters. By incorporating feedback from user
+demonstrations, the system is then able to learn the optimal parameters for the
 appropriate shape models.
@@
 shy away from expressing what they know \cite{Medwell2008}.
-%A conclusion drawn
-%in \cite{Hoy2011} is that any handwriting intervention studies considered in the
-%systematic review which involved fewer than two practice sessions per week and
-%fewer than a total of 20 practice sessions, including homework, were found to
-%demonstrate ineffective results. This highlights the necessity to engage
-%students in an interaction that will be sustainable over the long-term. 
 Successful interventions for children with handwriting difficulties involve the
@@
 
-%Engel-Yeger, Nagauker-Yanuv and Rosenblum \cite{Engel-Yeger2009} have shown the
-%link between handwriting difficulties and low self-efficacy, the belief in
-%one's capabilities to complete a task. Bandura \cite{Bandura1990} maintains
-%that self-efficacy constitutes the basis for the choice of whether or not to
-%attempt a task. Indeed, third graders receiving intervention for their
-%handwriting skills in \cite{Berninger1997} spoke of how they avoid writing
-%because of how it is illegible to others. This mindset of believing that one is
-%unable to write may lead to a developmental arrest in the acquisition of this
-%skill, which may make intervention more difficult in the future. Consequently,
-%it is of importance to engage students in activities in which their
-%self-efficacy and self-motivation is restored.
-
 The \emph{learning by teaching} paradigm, which engages the target student in
@@
 meta-cognitive, and educational benefits in a range of disciplines
-\cite{Rohrbeck2003}. An application which is yet to be explored, however, is
-that of handwriting intervention. One reason why this has not been investigated
-to date may be that in order to engage a child in the learning by teaching
-paradigm, there must be an appropriately unskilled peer for them to tutor. In
-the context where the target child is the lowest performer in their class, this
-may present a logistical constraint. In some cases, it may be appropriate for a
-peer or teacher to simulate a na\"ive learner for the target child to teach,
-however for an activity where one's skill level is visually evident -- as is the
-case in handwriting -- this acting is likely to be eventually detected. As such,
+\cite{Rohrbeck2003}. The application of the paradigm to handwriting intervention
+is previously unexplored. One reason for this may due to the requirement of 
+an appropriately unskilled peer for the target child to tutor, which may present
+a logistical constraint if the target child is the lowest performer in their class. 
+In some cases, it may be appropriate for a
+peer or teacher to simulate a na\"ive learner for the target child to teach.
+For handwriting, where one's skill level is visually evident, however, 
+this acting is likely to be eventually detected. As such,
 there is motivation for the use of a teachable agent which can be configured for
@@
 
-Presented is the development of the first known teachable agent which is capable
-of artificially making mistakes typical of children learning handwriting, and
-correcting them with external feedback. Such a system therefore exhibits the potential
-to engage children in the learning by teaching paradigm in the context of
-handwriting.
-
+We present the development of the first known teachable agent
+that intentionally makes mistakes typical of children learning
+handwriting. Through this capability, the robot can be taught by
+children, who themselves may learn through their teaching.
+
+%this part will be rearranged once prev work is involved:
 The teachable agent developed has the potential to be embedded as a simulated 
@@
 For the development of a learning algorithm in the context of
-handwriting, a parameterisation of letters and their deformities was sought such 
+handwriting, a parameterisation of letters and their deformities has been sought such 
 that different quality shapes can be generated, depending on the parameters input to
 the letter models. This allows the system to be configured to improve its writing 
-by modifying the parameters used to generate the letters, based on feedback from the 
-reinforcement learning partner as addressed in Section \ref{sec:learningAlg}. 
+by modifying the parameters based on feedback from the 
+reinforcement learning partner, as will be addressed in Section \ref{sec:learningAlg}. 
 %To this end, a method which can generate a model from real-world data
@@
 each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
-identify the location of salient features of the shapes which are robust to unanticipated user input,
+identify the location of salient features of the shapes which are robust to 
+unanticipated user input (such as shapes drawn backwards),
 the features are currently taken as $n$ uniformly spaced points along the shape
@@
 contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
-calculated as in (\ref{eq:paramCalc}). The $2n\times N$ matrix ${\bf \Phi }$ is
-an orthogonal matrix composed of the eigenvectors ${\bf v}_i$ corresponding to
+calculated as in (\ref{eq:paramCalc}). 
+${\bf \Phi }$ is
+an orthogonal $2n\times N$ matrix composed of the eigenvectors ${\bf v}_i$ corresponding to
 the largest $N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
-observations, as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}. As such,
-each shape may be approximated by the mean shape plus a sum of the top $N$
-eigenvectors, weighted by the parameter vector ${\bf p}$.
+observations, as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}. 
+If there is correlation between the points in the observations, there will be
+eigenvalues of the covariance matrix which are close to zero. As such, removing
+the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
+reduction with minimal impact.
 
@@
 
-If there is correlation between the points in the observations, there will be
-eigenvalues of the covariance matrix which are close to zero. As such, removing
-the associated eigenvectors from ${\bf \Phi}$ allows for dimensionality
-reduction with minimal impact. 
+PCA has been performed on all of the paths of a particular allograph in the
+dataset individually, to reduce the $2n$-dimensional space for that shape to one 
+with $N=10$ dimensions.
+As such,
+each shape may be approximated by the mean shape of the allograph plus a sum of the top 10
+eigenvectors, weighted by the parameter vector ${\bf p}$. 
 %Indeed, the amount of variance in the dataset
@@
 
+(\ref{eq:projection}) may also be used
+to generate new shapes based on the parameters ${\bf p}$ which are used. ${\bf
+p}={\bf 0}$ will yield the mean shape, and variations to each of the $N$ values
+in ${\bf p}$ will cause a change in the shape represented by the corresponding
+eigenvector (Figure \ref{fig:deviations_sPrint}). 
 For the dataset presented in Figure \ref{fig:deviations_sPrint}, the
@@
 %
-PCA has been performed on all of the paths of a particular allograph in the
-dataset individually, to reduce the $2n$-dimensional space to one of a desired
-number of dimensions. $N=10$ has been used for the work presented.
-
-(\ref{eq:projection}) may also be used
-to generate new shapes based on the parameters ${\bf p}$ which are used. ${\bf
-p}={\bf 0}$ will yield the mean shape, and variations to each of the $N$ values
-in ${\bf p}$ will cause a change in the shape represented by the corresponding
-eigenvector (Figure \ref{fig:deviations_sPrint}).
 
@@
 Interestingly, although the parameters are the result of an \emph{unsupervised} 
-statistical shape analysis, they still represent variations which could have
+shape analysis, they still represent variations which could have
 been intuitively identified by a manual parameterisation. For example, for the
@@
 which may be ascribed descriptive interpretations (not just numerical) is an
-advantage of this method, given its context of use. If a teacher wishes to
+advantage of this method, given its intended use with humans. If a teacher wishes to
 create initial letters with a particular feature (a wide `s' or a `d' with a
-large loop, for example), it is possible with this system.
+large loop, for example), it is possible.
 
@@
 
-After determining the appropriate number of dimensions ($N$) for the shape
-models, new letters can be generated by varying the parameter values in this
-$N$-dimensional space in accordance with (\ref{eq:projection}). By choosing
+As aforementioned, new letters can be generated by varying the parameter values 
+for a shape model in accordance with (\ref{eq:projection}). By choosing
 parameter values which lie within the observed range in the dataset, it is
@@
 
+%todo
 In \cite{Chandra2013}, it was found that children aged 4-6 years participating
@@
 
-It was shown in Section \ref{sec:writingGeneration} how the statistical shape
-model of a particular letter may convert a set of parameters into a generated
-letter. Similarly, the model may also be used ``in reverse'' 
-to convert a
-letter into its parameters, given the model. The parameters of user-drawn
-letters may therefore be used in order to incorporate the capabilities for the
-learning algorithm to adapt to the user's feedback via demonstration.
+In addition to generating letters by varying input parameters, the statistical 
+shape model of Section \ref{sec:writingGeneration} may also be used 
+to determine a particular letter's parameters, given the model. The parameters of user-drawn
+letters may therefore be used in order implement a 
+learning algorithm which adapts to the user's feedback via demonstration letters.
 
@@
 demonstration ${\bf x}_{demo}$, the associated parameters may be determined as in
-(\ref{eq:param}).
-
+(\ref{eq:param}), which will reconstruct an approximate shape.
+
+%really this is the same as eq 3
 \begin{equation}\label{eq:param}
@@
 
-The parameters which are determined for a shape in (\ref{eq:param}) will not
-reconstruct the shape exactly if $N<2n$, but rather will reconstruct the closest
-point in the $N$-dimensional space which the eigenvectors span.
+%The parameters which are determined for a shape in (\ref{eq:param}) will not
+%reconstruct the shape exactly if $N<2n$, but rather will reconstruct the closest
+%point in the $N$-dimensional space which the eigenvectors span.
 
@@
 demonstrations from a child for the letter `s' using a learning rate of
-$\alpha=1/2$.  Note that even poorly-written demonstrations allow the system to improve.
+$\alpha=1/2$. Observe that even poorly-written demonstrations allow the system to improve.
 
@@
 In order to develop a teachable agent that is appropriate for engaging a child
-through the learning by teaching paradigm, 
+in the learning by teaching paradigm, 
 %- that is, that it is an embodied agent, capable of eliciting motor mimicry,
@@
 Precise control over what the robot is writing is necessary in the
-proposed application of a learning agent in this context. Because
+proposed application of a handwriting. Because
 of the limited fine motor skills possible with such an affordable robot, in
@@
 {\sc nao} has been configured to use simulated handwriting with a synchronised tablet
-to achieve this level of control. The necessary components of implementing the
-proposed teachable robotic agent are, therefore:
-
-\begin{enumerate}
-    \item developing capabilities for the robot to trace handwriting ``in the air'',
-
-    \item synchronising the robot's movements with the display of the writing on a
-        tablet so that it appears that the robot is causing the handwriting to
-        display because of its actions, and
-
-    \item integrating the writing behaviour with the handwriting learning
-        algorithm presented in Section \ref{sec:learningAlgorithm} to create a
-        \emph{learning by teaching} interaction with the agent. 
-\end{enumerate}
-
-These steps are presented in the sections which follow.
-
-\subsection{Robot Trajectory Following}
+to achieve this level of control.
+
+The development of the necessary components for embedding the handwriting learning
+algorithm presented in Section \ref{sec:learningAlgorithm} in the humanoid agent
+are presented in the sections which follow.
+
+\subsection{Robot Trajectory Following Movements}
 
@@
 \url{http://wiki.ros.org/nao_robot}.} has been used for integration of the {\sc nao}
-with external reference frames, such as the tablet's location, using the $tf$ transformation library \cite{Foote2013}.
+with external reference frames, such as the tablet's location, 
+using the $tf$ transformation library \cite{Foote2013}.
 
 When using simulated handwriting, it is no longer necessary that the robot
-engages in the typical style of handwriting, with a writing instrument at a desk.
+engages in the typical style of handwriting of using a writing instrument at a desk.
 By instead having the robot point at a vertical writing surface to cause the
@@
         robot's motion with the trajectory displayed on the tablet is not as
-        critical, because the finger is not expected to touch the tablet exactly
-        at the trajectory point, in contrast to a pen tip.
+        critical. This is because a pen tip would be expected to touch the
+        tablet exactly at the trajectory point, while a fingertip may not.
         % This means that orientation degrees of freedom can be freed without significant adverse effects.
@@
 
-After getting the robot to trace writing trajectories, the next step towards
-simulated handwriting is getting the trajectories of the robot's `writing' to
-display on an Android tablet.
-
-ROS has been used for the communication between the devices used in the system,
+%After getting the robot to trace writing trajectories, the next step towards
+%simulated handwriting is getting the trajectories of the robot's `writing' to
+%display on an Android tablet.
+
+To enable the robot's `writing' to display while the robot is tracing
+trajectories, ROS has been used for the communication between the devices,
 including the Android tablet\footnote{For more information about ROS on Android
@@
 a ROS topic and display the trajectory as an
-animation. Synchronisation between the tablet and the robot has been achieved by:
-
-\begin{itemize}
-
-    \item sending a requested start time accompanying the trajectory, which is
-        sufficiently in the future, to account for varying transmission delays
-        to the nodes on different devices,
-
-    \item synchronising all clocks with NTP servers such that the ROS time used
-        for responding to the requested start time is the same at all nodes,
-
-    \item reducing the number of points along the trajectory passed to the
-        robot's motion planner to improve timing accuracy, and
-
-    \item not running computationally expensive tasks on the robot (such as
-        camera publishing) while it is writing as this interferes with the
-        requested timings between points.
-
-\end{itemize}
+animation. Synchronisation between the tablet and the robot has been achieved by
+using NTP servers to synchronise device clocks; passing only the necessary number of points (7)
+to the robot's motion planner to improve timing accuracy; and not running 
+computationally expensive tasks on the robot (such as camera publishing) while it 
+is writing.
+
+% \begin{itemize}
+
+%     \item sending a requested start time accompanying the trajectory, which is
+%         sufficiently in the future, to account for varying transmission delays
+%         to the nodes on different devices,
+
+%     \item synchronising all clocks with NTP servers such that the ROS time used
+%         for responding to the requested start time is the same at all nodes,
+
+%     \item reducing the number of points along the trajectory passed to the
+%         robot's motion planner to improve timing accuracy, and
+
+%     \item not running computationally expensive tasks on the robot (such as
+%         camera publishing) while it is writing as this interferes with the
+%         requested timings between points.
+
+% \end{itemize}
 
@@
 \ref{fig:tabletDetection}). When used in an interaction involving a participant, this
-allows a user to move the tablet as required for the interaction. As broadcasting
-the robot's camera has been identified as a computationally expensive task which
-can disrupt the robot's timing of synchronised writing, it is only done when the
-robot is not writing, and the tablet is assumed to be stationary during the
-writing process.
+allows a user to move the tablet as required for the interaction. The tablet is 
+assumed to be stationary during the writing process as detecting the tablet interferes
+with the robot's adherance to writing synchronisation.
 
@@
 
-\subsection{Integration into a Robotic Agent}
+\subsection{Integration into a Teachable Robotic Agent}
 
@@
 The tablet application has been extended to act as the primary medium for
-capturing participant input, and publishes the user's demonstrations when they are
-satisfied with their writing. The user demonstrations are received by the
+capturing participant input, and submits the user's demonstrations when they are
+satisfied with their writing.
+
+The user demonstrations are received by the
 interaction controller running on a desktop computer. It is responsible for
@@
 a finite state machine to manage the interaction stage and various system
-inputs.  In the context of learning handwriting, an additional input to the system is a word 
-from which the letters are to be learned, as detected by a fiducial marker on a word card.
-The controller manages the learning algorithm by inferring the letter which
-user demonstrations are intended for based on their position on the tablet, and
-publishes the shapes to be written which are generated by the learning algorithm
-in response to the feedback.
+inputs. In the context of learning handwriting, an additional input to the system 
+is a word from which the letters are to be learned, which is detected by a fiducial 
+marker on the card displaying the word.
+The controller provides inputs to the learning algorithm including the word to learn
+and the user demonstrations, by inferring the letter which the demonstrations are 
+intended for based on their position on the tablet. The output shapes from the 
+learning algorithm are sent by the controller to the devices which are to be write them.
 
@@
 
+%make line colours not colour dependent
 \begin{figure}[ht]
@@
 
-    \node at (0,0)[cmpt, fill=Cyan!50] (tactile) {tactile interaction \\ manager};
+    \node at (0,0)[cmpt, fill=Cyan!50, text width=2.7cm] (tactile) {tactile interaction \\ manager};
     \node[cmpt, fill=Cyan!50, left=of tactile] (display) {display \\ manager};
 
-    \node [cmpt, fill=Green!50, below=of tactile] (shape) {shape position \\ manager};
+    \node [cmpt, fill=Green!50, below=of tactile, text width=2.7cm] (shape) {shape position \\ manager};
     \node [cmpt, fill=Green!50, left=of shape] (learner) {letter \\ learner};
@@
     \node [cmpt, fill=YellowOrange!50, left=of tablet] (camera) {nao camera};
-    \node [cmpt, fill=YellowOrange!50, below=1cm of tablet] (pose) {robot state publisher};
+    \node [cmpt, fill=YellowOrange!50, below=0.6cm of tablet] (pose) {robot state publisher};
 
@@
 
-    \path (shape) edge [->, redarrow] node[label, left, align=right] {letter to write \\ + time \\ + position} (display);
+    \path (shape) edge [->, redarrow] node[label, left, align=left] {letter \\to write \\ + time \\ + position} (display);
     \path (shape) edge [->,redarrow] node[label, right] {letter to write \\ + time \\ + position in\\tablet frame} (writer);
@@
 handwriting intervention. 
+%Preliminary studies has been conducted to evaluate 
+%the feasibility of the system as a technical tool for such investigations.
 
@@
     \item The participant shows the robot one of seven different 3-letter words
-        to write, which, combined, consist of 7 different letters (`c', `e',
+        to write, are made up of 7 possible letters (`c', `e',
         `n', `o', `s', `u', `w'). Fiducial markers which are printed on the word
@@
     \item The robot responds to the word request verbally and writes the
-        letters by pointing at the tablet and imitating writing the letters. The
-        tablet, placed in front of the robot with a vertical, landscape orientation,
-        displays the letters in synchronisation with the robot's movements.
+        letters according to the method described in Section \ref{sec:tabletSynch}.
 
@@
         how to write the letter which they feel needs to be corrected. The
-        demonstration is performed by drawing on the tablet with a stylus. The
         tablet may be moved into the most appropriate position for the child to
-        write on it. Only one letter may be demonstrated at a time and the
+        write on it with the stylus. Only one letter may be demonstrated at a time and the
         position of the participant's demonstration on the tablet encodes the
@@
         When the participant is satisfied with the demonstration, a button on
-        the tablet which signals that it is the robot's turn is pressed and the
-        demonstration is sent to the controller.
-
-    \item The controller produces an adapted letter for the robot to write in
+        the tablet which signals that it is the robot's turn is pressed.
+
+    \item The robot writes an adapted letter in 
         response to the participant's feedback, and the interaction iterates,
@@
 A pilot study at the first school consisted of four groups of
-approximately 8 english-speaking children, aged 6-7 years. The children
+approximately 8 english-speaking children each, aged 6-7 years. The children
 interacted with the system for a total of 65 minutes, with the robot writing 96
-letters, of which 49 were in response to demonstrations from the children.
+letters. 49 of these letters were in response to demonstrations from the children 
+and the remaining were from when new words were requested.
 
@@
 observed giving advice to the child designated as the letter demonstrator,
-potentially giving rise to the higher level paradigm of learning by
+potentially giving rise to a higher level paradigm of learning by
 \emph{teaching to teach}. As a consequence of this observation, the study which
@@
 number of children interacting with the robot.
-%in order to investigate the potential of the system to not only be used to set
-%the context of children tutoring the robot, but also children interacting as
-%peer tutors with each other.
 
@@
         time the robot wrote 335 letters, 152 of which in response to
-        demonstrations received from the 21 children and the remaining while writing 
-        new words. During this time, technical 
+        demonstrations received from the 21 children. During this time, technical 
 	intervention was only required for the three instances that the robot fell 

### 2014-12-02 main.tex
Improve conciceness in sections 4 and 5

@@
 handwriting intervention. 
-%Preliminary studies has been conducted to evaluate 
-%the feasibility of the system as a technical tool for such investigations.
+Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
+have been conducted to evaluate the feasibility and technical soundness of the 
+interaction system proposed as a tool for such investigations.
 
@@
 
-The interaction context which has been developed as a framework for addressing
-relevant research questions is one where participants are asked to improve the robot's
-handwriting by correcting its letters. Figure~\ref{fig:pilotInteraction}
+%The interaction context which has been developed as a framework for addressing
+%relevant research questions is 
+%Participants are asked to improve the robot's
+%handwriting by correcting the letters it writes on the tablet. 
+Figure~\ref{fig:pilotInteraction}
 illustrates an example interaction sequence between the participant and the
@@
 \end{enumerate}
-
-%To allow the system to take input from the user on which words to draw,
-%fiducial markers were placed on cards which were detectable by a
-%previously-developed ROS node processing a camera stream. A node which
-%processed the fiducial markers detected was then created to convert the card
-%detected into an appropriate message for the controller.
 
@@
 
-\subsection{Outcomes of Preliminary Studies}
-
-Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
-have been conducted to evaluate the feasibility and technical soundness of the 
-interaction system proposed.
+\subsection{Outcomes of Preliminary Study 1}
 
@@
 
-The study at the second school involved 21 french-speaking students aged 7-8 years: 7 children
+\subsection{Outcomes of Preliminary Study 2}
+The study at the second school involved 21 french-speaking students aged 7-8 years. 7 children
 interacted with the robot individually and 7 sessions included the remaining
-14 students interacting with the robot in pairs. The duration of the sessions
-was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3). 
+14 students interacting with the robot in pairs.
 Initial parameters were drawn from a range purposely chosen to generate shapes 
@@
 parameters were fixed, generating shapes which some groups chose to correct 
-(e.g. 13/14 for 'n' and 2/14 for 'c').
-
-The following conclusions were successfully drawn about the system as a result
-of the study at the second school.
-
-    \textbf{The simulated robotic writing was believed by the children in all
-    cases.} There were, at times, 
-    % * <deanna.m.hood@gmail.com> 2014-09-05T11:59:03.640Z:
-    %
-    % how many
-    %
+(e.g. 13/14 for 'n' and 2/14 for 'c'). The duration of the sessions
+was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).
+
+%The following conclusions were successfully drawn about the system as a result
+%of the study at the second school.
+
+It has been concluded following the second study that the system has 
+been validated as a technically sound autonomous interaction. 
+The interaction setup including the teachable
+robotic agent withstood the interaction which lasted for a total of 160 minutes. 
+During this time the robot wrote 335 letters, 152 of which in response to
+demonstrations received from the 21 children. Technical 
+intervention was only required for the three instances that the robot fell 
+later in the day. Otherwise, the technical components of the system operated 
+autonomously and as expected over the sessions.
+
+Furthermore, no child indicated that they did not attribute the writing
+to the robot. There were, at times, 
     questions about the robot's writing method at the beginning of the interaction,
     but when advised that the robot ``tells the tablet what it wants to write,''
-    this was accepted by the children. To allow the children an opportunity to
-    express doubt in the robot's ability to write without explicitly asking them if
-    the robot was pretending, the children were asked if they believed that the
-    robot would be able to write its name, \emph{{\sc nao}} which had not previously been
-    demonstrated. It was reasoned that this would prompt the children to question
-    the point of the robot actually \emph{writing} if they had any suspicion that
-    the robot was pretending, but this was never the case. In the event where the
-    robot's writing was not correctly synchronised with the tablet, this did not affect the
-    response of the child. If older children participate in the interaction study --
+    this was accepted by the children. 
+%     To allow the children an opportunity to
+%     express doubt in the robot's ability to write without explicitly asking them if
+%     the robot was pretending, the children were asked if they believed that the
+%     robot would be able to write its name, \emph{{\sc nao}} which had not previously been
+%     demonstrated. It was reasoned that this would prompt the children to question
+%     the point of the robot actually \emph{writing} if they had any suspicion that
+%     the robot was pretending, but this was never the case. 
+    On the rare occasion that the
+    robot's writing was not correctly synchronised with the tablet, this did
+    not appear to influence the children's impression. 
+    If older children participate in the interaction study --
     which may be likely as children with lasting handwriting difficulties are included
@@
     believability of the robot's writing scheme. However, for 6-8 year olds the
-    proposed setup has been proven viable.
-
-    \textbf{The children were engaged in teaching the robot.} % * <deanna.m.hood@gmail.com> 2014-09-05T09:54:48.069Z:
-    %
-    % maybe this is too strong as a 'conclusion' and should just be an observation. plus what does this even mean.. the child walking around the room was 'engaged' too...?
-    %
-    An average of 10.9 demonstration letters (SD = 4.4) were
+    proposed setup appears sufficient.
+
+Regarding the engagement of the children in teaching the robot, 
+    an average of 10.9 demonstration letters (SD = 4.4) were
     provided to the robot for each session during the interaction.
@@
     the participants had become intrinsically motivated to engage in the
-    interaction.% * <deanna.m.hood@gmail.com> 2014-09-05T10:30:45.293Z:
-    %
-    % I guess it could have also come from us sitting there watching them
-    %
-
-    \textbf{All children believed that the robot was learning and that
-        they were the ones teaching it.} This was concluded from the responses
-        when the children were asked directly. This is in contrast to a prior
-        feasibility study for a version of the interaction which only allowed
-        for touch-based feedback, not user demonstrations, in which three of the
-        seven adult participants did not feel that it was their input which
-        helped the robot improve.
-        % * <deanna.m.hood@gmail.com> 2014-09-05T09:46:49.117Z:
-    %
-    % probably can't just casually mention this study without going into more detail...
-    %
+    interaction.
+
+%     \textbf{All children believed that the robot was learning and that
+%         they were the ones teaching it.} This was concluded from the responses
+%         when the children were asked directly. This is in contrast to a prior
+%         feasibility study for a version of the interaction which only allowed
+%         for touch-based feedback, not user demonstrations, in which three of the
+%         seven adult participants did not feel that it was their input which
+%         helped the robot improve.
 
@@
 
-    \textbf{The system has been validated as a technically sound
-        autonomous interaction.} The interaction setup including the teachable
-        robotic agent withstood the interaction for a total of 160 minutes. During this
-        time the robot wrote 335 letters, 152 of which in response to
-        demonstrations received from the 21 children. During this time, technical 
-	intervention was only required for the three instances that the robot fell 
-	later in the day. Otherwise, the technical components of the system operated 
-	autonomously and as expected over the sessions.
-        %, with only verbal interaction for prompting being required from an observing researcher.
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{Towards Long-term Interventions}\label{sec:futureWork}
-%why is this title going into the margins....
-
-A conclusion drawn in~\cite{Hoy2011} is that any 
-handwriting intervention studies considered in the systematic review which involved 
+\section{Towards Long-term Studies}\label{sec:futureWork}
+%How to break this section up?
+
+A conclusion drawn in a systematic review handwriting intervention studies \cite{Hoy2011} 
+is that any of the studies considered which involved 
 fewer than two practice sessions per week and fewer than a total of 20 practice 
@@
 highlights the necessity to engage students in an interaction which will be sustainable
- over the long-term in order to answer 
-research questions which involve the measurement of learning gains. 
+ over the long-term if 
+research questions which involve the measurement of learning gains are to be addressed. 
 Several challenges are raised in developing such long-term capabilities for the system,
@@
 incorporating internal proportion and global deformation errors to one which can
-also generate missing subparts of the letter, or break the letter down into
-primitive strokes, for example. While it is expected that incorporating a
+also generate missing subparts of the letter, or write letters backwards, for example. 
+While it is expected that incorporating a
 database of letters drawn by children into the shape modeling process would
@@
 
-With some of the challenges towards an engaging long-term handwriting intervention 
-with the teachable robotic partner addressed, further steps can be made towards 
-answering the central question of what impact to the outcomes of interventions the 
-addition of such a teachable robotic agent would have, including the effect on the 
+With some of these challenges addressed, further steps can be made towards 
+answering the overarching question of what impact the 
+addition of such a teachable robotic agent would have on handwriting interventions, including the effect on the 
 participants' self-esteem, motivation, and learning gains. % does it impact the
@@
 % Anonymized for double-blind review
-%\section*{Acknowledgments}
-
-%This research was supported by the Swiss National Science Foundation through the
-%National Centre of Competence in Research Robotics.
+\section*{Acknowledgments}
+
+This research was supported by the Swiss National Science Foundation through the
+National Centre of Competence in Research Robotics.
 

### 2014-12-07 main.tex
First attempt at prev work

@@
 \title{\LARGE \bf
-A Teachable Robotic Agent for Children Learning Handwriting, Capable of Simulated Handwriting Itself %make better
+Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
 }
@@
 children, who themselves may learn through their teaching.
+
+Teachable computer-based agents have previously been used to encourage the ``protégé effect'',
+wherein students invest more effort into learning when it is for a teachable agent 
+than for themselves \cite{Chase2009}. Furthermore, robotic learning agents which 
+employ the learning by teaching paradigm have been developed in settings such as 
+vocabulary learning to take advantage of the engagement benefits in education. 
+This differs from the established work which has focused exclusively on
+on a robot learning physical skills for the benefit of the robot -- to play table 
+tennis, for example -- not the human teacher. Indeed, as the handwriting that
+the proposed robotic partner engages in is simulated and only for interaction 
+purposes, it does not have not depend on capabilities to improve its writing.
+
+We present the first known teachable agent which is capable
+of artificially making mistakes typical of children learning handwriting, and
+correcting them with external feedback. Such a system therefore exhibits the potential
+to engage children in the learning by teaching paradigm in the context of
+handwriting. Furthermore our work is concerned with learning of a physical skill, 
+and so a robot has been used as the teachable agent to exploit its embodied nature.
+
+Consequently, the learning agent developed has been embodied in a commercially
+affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
+leveraging synchronisation with a tablet display to simulate fine motor skills
+otherwise infeasible for the robot. 
+This use of a humanoid robot capable of physically demonstrating handwriting 
+trajectories to its child learning partner is supported in this context by the potential 
+for motor mimicry to yield significant improvements in handwriting interventions 
+in which letter formations are demonstrated to participants \cite{Berninger1997}.
+
+As the robot is pretending to write for the purpose of the interaction and is 
+therefore not able to improve on its physical skills itself, 
+This work represents the first teachable robotic agent which is 
+being taught a physical skill for the benefit of the human teacher, through the
+learning by teaching paradigm.
 

### 2014-12-07 main.tex
First draft of previous robotics work

--- 2014-12-02 main.tex
@@
 is previously unexplored. One reason for this may due to the requirement of 
-an appropriately unskilled peer for the target child to tutor, which may present
+an appropriately unskilled peer for the target child to tutor, as this may present
 a logistical constraint if the target child is the lowest performer in their class. 
@@
 
-%this part will be rearranged once prev work is involved:
-The teachable agent developed has the potential to be embedded as a simulated 
-computer-based agent, however there are three main points which have motivated 
-the use of a robot instead as the teachable agent in the presented work:
-
-\begin{enumerate}
-    \item the engagement and ``protégé effect'' elicited by teaching an embodied
-        agent is anticipated to be stronger than that associated with a
-        tablet-based application, which children are increasingly recognising as
-        disposable technology,% * <deanna.m.hood@gmail.com> 2014-09-08T11:07:10.004Z:
-%
-% ... citation needed?
-%
-
-    \item observing a teachable agent respond to what it has been taught
-        is a significant step in the learning by teaching
-        paradigm \cite{Okita2006}, and therefore it may be significant for the agent to respond
-        with a physical writing \emph{process}, rather than simply a product, and
-
-    \item the potential for motor mimicry to yield significant improvements in
-        handwriting interventions in which letter formations are demonstrated to participants \cite{Berninger1997} further supports the case
-        for investigating the use of a humanoid robot capable of physically
-        demonstrating handwriting trajectories to its child learning partner.
-\end{enumerate}
-
-Consequently, the learning agent developed has been embodied in a commercially
-affordable {\sc nao} humanoid robot. Its writing capabilities have been implemented by
-leveraging synchronisation with a tablet display to simulate fine motor skills
-otherwise infeasible for the robot.
+Teachable computer-based agents have previously been used to encourage the 
+``protégé effect'', wherein students invest more effort into learning when it
+is for a teachable agent than for themselves \cite{Chase2009}. As we are 
+concerned with learning of a physical skill, the learning agent developed has 
+been embodied in a humanoid robot which is capable of physically demonstrating 
+handwriting trajectories to its child learning partner.
+This is supported by the potential for motor mimicry to yield significant 
+improvements in handwriting interventions in which letter formations are 
+demonstrated to participants \cite{Berninger1997}.
+
+A robotic learning agent which employs the learning by teaching paradigm has 
+previously been developed by Tanaka and Matsuzoe \cite{Tanaka2012}. In their
+system, children learn vocabulary by teaching the {\sc nao} robot to act out 
+verbs. The robot is tele-operated and mimics the actions that the children
+teach it, but with no long-term memory or learning algorithm in place.
+Our work instead focuses on an autonomous robotic partner which the child 
+can teach a physical skill.
+This differs from the established work of robots learning physical skills
+from demonstrations, which has focused exclusively on
+the robot learning physical skills for the benefit of the robot -- to play table 
+tennis, for example -- not the human teacher \cite{Werfel2014}.
+
+%Indeed, as a commercially affordable robot is being used, the handwriting that
+%it engages in is in fact emph{simulated}, for interaction purposes, by 
+%leveraging synchronisation with a tablet display. Hence the system does not 
+%have, nor does it depend on, capabilities to improve its physical skills for
+%its own benefit.
+
+Due to the intended use in a school environment, a commercially
+affordable {\sc nao} humanoid robot has been used. Its writing capabilities 
+have been implemented by leveraging synchronisation with a tablet display to
+simulate fine motor skills otherwise infeasible for the robot.
 

### 2014-12-10 main.tex
Rephrase the preliminary new 'Related work' part

@@
 
-A robotic learning agent which employs the learning by teaching paradigm has 
-previously been developed by Tanaka and Matsuzoe \cite{Tanaka2012}. In their
+Werfel suggests in~\cite{Werfel2014} that, until now, most of the work investigating how
+humans can teach robots (in particular, physical skills) focuses on the robot's
+benefits, and not so much on the learning experienced by the human tutor. Our
+work focuses on this later aspect. A robotic learning agent which employs the learning by teaching paradigm has 
+previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
 system, children learn vocabulary by teaching the {\sc nao} robot to act out 
@@
 teach it, but with no long-term memory or learning algorithm in place.
-Our work instead focuses on an autonomous robotic partner which the child 
-can teach a physical skill.
-This differs from the established work of robots learning physical skills
-from demonstrations, which has focused exclusively on
-the robot learning physical skills for the benefit of the robot -- to play table 
-tennis, for example -- not the human teacher \cite{Werfel2014}.
+
+Our work significantly extends this line of work in two direction, first by
+proposing an autonomous robotic partner, second by investigating the scaffolding
+of children' acquisition of a challenging physical skill (handwriting).
 

### 2014-12-10 main.tex
Removed a bit of passive voice + make other sentences simpler

@@
 
-%%% HRI 2015 -> double-blind review process
-
-%Despite the social motivation for the use of a teachable agent for the
-%engagement and support of children with handwriting difficulties, to date no
-%such technology is known to have been developed.
-
-%(DH) abstract probably too long...
-%(DH) do we have to be specific somewhere about what stage of handwriting we're targeting..?
-
-This article presents the first known robotic partner which children can teach handwriting. 
-The system allows for the
-\emph{learning by teaching} paradigm to be employed in the interaction, so as to
-stimulate meta-cognition, empathy and increased self-esteem in the child user. 
-It is
-hypothesised that use of a humanoid robot in such a system could not just engage an unmotivated student,
-but could also present the opportunity for children to experience physically-induced
-benefits encountered during human-led handwriting interventions, such as motor
-mimicry.
-
-By leveraging simulated handwriting on a synchronised tablet display, a {\sc nao}
-humanoid robot with limited fine motor capabilities has been configured as a
-suitably embodied handwriting partner. Statistical shape models derived from principal
-component analysis of a dataset of adult-written letter trajectories allow
-the robot to draw purposefully deformed letters. By incorporating feedback from user
-demonstrations, the system is then able to learn the optimal parameters for the
-appropriate shape models.
-
-Preliminary in situ studies have been conducted with primary school classes to obtain
-insight into children's use of the novel system. 
-Children aged 6-8 were successfully able to engage with the robot and to improve its 
-writing to a level which they were satisfied with. The validation of the interaction
-represents a significant step towards an innovative use for robotics which addresses a
+This article presents a novel robotic partner which children can teach
+handwriting.  The system relies on the \emph{learning by teaching} paradigm to
+build an interaction, so as to stimulate meta-cognition, empathy and
+increased self-esteem in the child user.  We hypothesise that use of a
+humanoid robot in such a system could not just engage an unmotivated student,
+but could also present the opportunity for children to experience
+physically-induced benefits encountered during human-led handwriting
+interventions, such as motor mimicry.
+
+By leveraging simulated handwriting on a synchronised tablet display, a {\sc
+nao} humanoid robot with limited fine motor capabilities has been configured as
+a suitably embodied handwriting partner. Statistical shape models derived from
+principal component analysis of a dataset of adult-written letter trajectories
+allow the robot to draw purposefully deformed letters. By incorporating feedback
+from user demonstrations, the system is then able to learn the optimal
+parameters for the appropriate shape models.
+
+Preliminary in situ studies have been conducted with primary school classes to
+obtain insight into children's use of the novel system.  Children aged 6-8
+successfully engaged with the robot and improved its writing to a level which
+they were satisfied with. The validation of the interaction represents a
+significant step towards an innovative use for robotics which addresses a
 widespread and socially meaningful challenge in education.
-
-%, and provides context
-%for robotics in education beyond the well-explored use of teaching coding and
-%robotics-related subjects.
 
@@
 meta-cognitive, and educational benefits in a range of disciplines
-\cite{Rohrbeck2003}. The application of the paradigm to handwriting intervention
-is previously unexplored. One reason for this may due to the requirement of 
-an appropriately unskilled peer for the target child to tutor, as this may present
-a logistical constraint if the target child is the lowest performer in their class. 
-In some cases, it may be appropriate for a
+\cite{Rohrbeck2003}. To our best knowledge, the application of the paradigm to
+handwriting intervention remains however unexplored. One reason for this may due
+to the requirement of an appropriately unskilled peer for the target child to
+tutor, as this may present a logistical constraint if the target child is the
+lowest performer in their class.  In some cases, it may be appropriate for a
 peer or teacher to simulate a na\"ive learner for the target child to teach.
-For handwriting, where one's skill level is visually evident, however, 
-this acting is likely to be eventually detected. As such,
-there is motivation for the use of a teachable agent which can be configured for
-a variety of skill levels, and for which children do not have preconceptions
-about its handwriting ability.
-
-We present the development of the first known teachable agent
+For handwriting, where one's skill level is visually evident, however, this
+acting is likely to be eventually detected. As such, there is motivation for the
+use of a teachable agent which can be configured for a variety of skill levels,
+and for which children do not have preconceptions about its handwriting ability.
+
+We present the development of a novel teachable agent
 that intentionally makes mistakes typical of children learning
@@
 ``protégé effect'', wherein students invest more effort into learning when it
-is for a teachable agent than for themselves \cite{Chase2009}. As we are 
+is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
 concerned with learning of a physical skill, the learning agent developed has 
@@
 improvements in handwriting interventions in which letter formations are 
-demonstrated to participants \cite{Berninger1997}.
+demonstrated to participants~\cite{Berninger1997}.
 
@@
 
-%Indeed, as a commercially affordable robot is being used, the handwriting that
-%it engages in is in fact emph{simulated}, for interaction purposes, by 
-%leveraging synchronisation with a tablet display. Hence the system does not 
-%have, nor does it depend on, capabilities to improve its physical skills for
-%its own benefit.
-
 Due to the intended use in a school environment, a commercially
@@
 contributions made to the study of human-robot interaction, in discussing the
-use of the first-of-its-kind system with primary school children and its potential as a tool for
+use of the system with primary school children and its potential as a tool for
 addressing wider pedagogical research questions in education.
@@
 that different quality shapes can be generated, depending on the parameters input to
-the letter models. This allows the system to be configured to improve its writing 
+the letter models. This allows to configure the system such as to improve its writing 
 by modifying the parameters based on feedback from the 
-reinforcement learning partner, as will be addressed in Section \ref{sec:learningAlg}. 
-%To this end, a method which can generate a model from real-world data
-%has been employed in order to capture realistic variations in letters.
+reinforcement learning partner (Section~\ref{sec:learningAlg}).
 
@@
 
-One approach for a shape model which can appropriately represent realistic
-variations in shapes is statistical shape
-modelling. Statistical shape modelling is an application of principle component
-analysis (PCA), where a linear transform which de-correlates data vectors is
-found \cite{Stegmann2002} and allows for dimensionality reduction.
+We use statistical shape modelling as an approach for a shape model which can
+appropriately represent realistic variations in shapes. Statistical shape
+modelling is an application of principle component analysis (PCA), where a
+linear transform which de-correlates data vectors is found~\cite{Stegmann2002}
+and allows for dimensionality reduction.
 
@@
 
-The projection from the original $2n$-dimensional feature space $(n=70)$ to a reduced
-$N$-dimensional space is found as in (\ref{eq:projection}), where ${\bf p}$
+Equation (\ref{eq:projection}) represents the projection from the original 
+$2n$-dimensional feature space $(n=70)$ to a reduced $N$-dimensional space, where ${\bf p}$
 contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
@@
 the height of the top half of the letter compared to the bottom half, the width
-of the overall shape, etc. The ability to create varied levels of deformations
+of the overall shape, etc. The ability to generate varied levels of deformations
 which may be ascribed descriptive interpretations (not just numerical) is an
-advantage of this method, given its intended use with humans. If a teacher wishes to
-create initial letters with a particular feature (a wide `s' or a `d' with a
-large loop, for example), it is possible.
+advantage of this method, given its intended use with humans: It is for instance
+possible for a teacher to create initial letters with a particular feature (a wide
+`s' or a `d' with a large loop, for example).
 
@@
 
-As aforementioned, new letters can be generated by varying the parameter values 
+As explained, new letters can be generated by varying the parameter values 
 for a shape model in accordance with (\ref{eq:projection}). By choosing
@@
 %todo
-In \cite{Chandra2013}, it was found that children aged 4-6 years participating
+In~\cite{Chandra2013}, it was found that children aged 4-6 years participating
 in a handwriting peer tutoring pilot study most often made mistakes classified
@@
 would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
-the same general categories. Using a database of children's letters when
+the same general categories.
+
+Using a database of children's letters when
 available may yield potential for parameterising other mistakes made by
 children, such as merging strokes or decomposing a shape into multiple subparts
-inappropriately. Nevertheless, sufficient capabilities for the shape model to
-generate `poor' letters which are appropriate for simulating a na\"ive learner
-in the context of handwriting have been demonstrated, using the shape model
-generated from PCA on a dataset of only adults' writing.
+inappropriately. Nevertheless, our current shape model
+generated from PCA on a dataset of only adults' writing has shown to be
+initial well-suited to generate `poor' letters which are appropriate for 
+simulating a na\"ive learner.
 
@@
 
-The statistical shape model may be used to determine the parameters of a
+The statistical shape model is used to determine the parameters of a
 demonstration shape by projecting the features of the observed shape into the
@@
 In order to develop a teachable agent that is appropriate for engaging a child
-in the learning by teaching paradigm, 
-%- that is, that it is an embodied agent, capable of eliciting motor mimicry,
-%and capable of causing its teacher to reflect on the process that has been used
-%to respond to handwriting feedback -
-capabilities for the robot to engage in handwriting and interactive turn-taking have been established.
+in the learning by teaching paradigm, we have established capabilities for the robot 
+to engage in handwriting and interactive turn-taking.
 
@@
 
-%Because of the challenges in getting the {\sc nao} to write trajectories smoothly
-%because of its inherent ability to only reach discrete points in space, 
 Precise control over what the robot is writing is necessary in the
@@
 of the limited fine motor skills possible with such an affordable robot, in
-addition to the absence of force feedback and other technical necessities, the
-{\sc nao} has been configured to use simulated handwriting with a synchronised tablet
+addition to the absence of force feedback and other technical necessities, we
+have configured the {\sc nao} to use simulated handwriting with a synchronised tablet
 to achieve this level of control.
@@
 engages in the typical style of handwriting of using a writing instrument at a desk.
-By instead having the robot point at a vertical writing surface to cause the
-trajectory to appear (as in Figure \ref{fig:naoWriting}), several advantages are
-presented:
+Having the robot point at a vertical writing surface to cause the
+trajectory to appear (as in Figure \ref{fig:naoWriting}) has several
+advantages:
 
@@
         tablet exactly at the trajectory point, while a fingertip may not.
-        % This means that orientation degrees of freedom can be freed without significant adverse effects.
 
@@
      \begin{center}
-        %\subfigure{
-        %    \includegraphics[width=0.4\textwidth]{figures/naoWriting1.png}
-        %}%
-        \subfigure{
-            \includegraphics[width=0.6\linewidth]{figures/naoWriting2.png}
-        }%
-%
+            \includegraphics[width=0.7\linewidth]{figures/naoWriting2.png}
     \end{center}
@@
 
-Therefore, the system presented utilises the context where the robot is
+We have therefore designed the system in such a way that the robot is
 simulating handwriting by pointing at the tablet\footnote{Teachers interviewed
@@
 To enable the robot's `writing' to display while the robot is tracing
-trajectories, ROS has been used for the communication between the devices,
+trajectories, ROS is used for the communication between the devices,
 including the Android tablet\footnote{For more information about ROS on Android
@@
     \centering
-    \includegraphics[width=0.35\textwidth]{figures/chilitagDetection_cameraOverlay.png}
+    \includegraphics[width=0.9\columnwidth]{figures/chilitagDetection_cameraOverlay.png}
     \caption{\label{fig:tabletDetection}Detection of the tablet using a fiducial
@@
 (Figure~\ref{fig:archi}). The robot and Android tablet application present the
-writing process/result to the user, as in Section \ref{sec:tabletSynch}.
+writing process/result to the user, as explained in the previous section.
 The tablet application has been extended to act as the primary medium for
@@
 intended for based on their position on the tablet. The output shapes from the 
-learning algorithm are sent by the controller to the devices which are to be write them.
+learning algorithm are sent by the controller to the devices which write them.
 
@@
 handwriting intervention. 
-Preliminary studies at two schools in the Geneva area, involving more than 50 children, 
+Preliminary studies at two schools in the Geneva area, involving above 50 children, 
 have been conducted to evaluate the feasibility and technical soundness of the 
@@
         %conducting the interaction
-        When the participant is satisfied with the demonstration, a button on
-        the tablet which signals that it is the robot's turn is pressed.
+        When the participant is satisfied with the demonstration, they press a button on
+        the tablet which signals that it is the robot's turn.
 
@@
 for letters 'e' and 's' which would elicit correction. For the other letters, 
-parameters were fixed, generating shapes which some groups chose to correct 
+parameters were fixed, generating shapes which some groups still chose to correct 
 (e.g. 13/14 for 'n' and 2/14 for 'c'). The duration of the sessions
@@
 
-Furthermore, no child indicated that they did not attribute the writing
-to the robot. There were, at times, 
+Furthermore, no child indicated that they did not believe that the robot was writing
+by itself. There were, at times, 
     questions about the robot's writing method at the beginning of the interaction,
@@
     In 9 out of the 14 sessions (64\%), the robot received demonstration letters
-    \emph{after} reaching the test stage of the interaction. The participants'
+    even \emph{after} reaching the test stage of the interaction. The participants'
     teaching after the test word had been written and evaluated -- the only
@@
 
-A conclusion drawn in a systematic review handwriting intervention studies \cite{Hoy2011} 
+A conclusion drawn in a systematic review of handwriting intervention studies~\cite{Hoy2011} 
 is that any of the studies considered which involved 
@@
  over the long-term if 
-research questions which involve the measurement of learning gains are to be addressed. 
+we want to address research questions which involve the measurement of learning gains. 
 Several challenges are raised in developing such long-term capabilities for the system,
@@
 letter. This suggests that users may project human-like learning features, such as 
-forgetfulness, onto the robot, which may or may not actually be technically present 
+forgetfulness, onto the robot, which can be implemented 
 in the learning agent. This may need to be capitalised on when considering how to 
@@
 learning of hand-written letters suitable for educative purposes; a robotic
-system which has been experimentally proven to provide convincing scaffolding for
+system which has been experimentally shown to provide convincing scaffolding for
 complex human-robot interactions (teacher-learner social interactions, learning by
@@
 the child in a very specific social role. The child is the teacher in this relationship and the robot is
-the learner: the child must engage in a (meta-)cognitive relationship with the robot
+the learner: the child must engage in a (meta-) cognitive relationship with the robot
 to try to understand why the robot fails and how to help it best.  Here, the
@@
 
-The strong social impact of early educational problems makes continued research in this field
-an undoubtably meaningful challenge for robotics and human-robot interaction.
+And the strong social impact of early educational problems makes continued research in this field
+an undoubtedly meaningful challenge for robotics and human-robot interaction.
 

### 2014-12-10 main.tex
Re-anonymized + new title proposal

@@
 \title{\LARGE \bf
-Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
+% what about:
+When Children Teach a Robot to Write
+% ?
 }
 
-\numberofauthors{3} 
-\author{
-\alignauthor
-Deanna Hood\\
-Séverin Lemaignan\\
-Pierre Dillenbourg\\
-   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
-   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
-   %\affaddr{CH-1015 Lausanne, Switzerland}\\
-   \email{firstname.lastname@epfl.ch}
-% \alignauthor
-% Rafael Garcia\\
-%    \affaddr{Computer Vision and Robotics Group (ViCOROB)}\\
-%    \affaddr{University of Girona}\\
-%    \affaddr{Girona, Spain}
-}
+\numberofauthors{1} 
+%\author{
+%\alignauthor
+%Deanna Hood, Séverin Lemaignan, Pierre Dillenbourg\\
+%   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
+%   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
+%   %\affaddr{CH-1015 Lausanne, Switzerland}\\
+%   \email{firstname.lastname@epfl.ch}
+%}
 
@@
 \end{figure}
-\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
+%\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
+\footnotetext{See \url{[anonymized]} for a video of the synchronised 
 writing demonstration. }
@@
 The source code for the teachable robotic handwriting partner has been made 
-available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
+%available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
+available at \url{[anonymized]}.
 

### 2014-12-10 main.tex
Rewrite paragraph on mistake classification

@@
 
-%todo
-In~\cite{Chandra2013}, it was found that children aged 4-6 years participating
-in a handwriting peer tutoring pilot study most often made mistakes classified
-as inappropriate \emph{internal proportions} or \emph{global deformations}. It
-would be reasonable to consider the shapes in Figure \ref{fig:sampleLetters} in
-the same general categories.
-
-Using a database of children's letters when
-available may yield potential for parameterising other mistakes made by
-children, such as merging strokes or decomposing a shape into multiple subparts
-inappropriately. Nevertheless, our current shape model
-generated from PCA on a dataset of only adults' writing has shown to be
-initial well-suited to generate `poor' letters which are appropriate for 
-simulating a na\"ive learner.
+In~\cite{Chandra2013}, Chandra found that children aged 4-6 years participating
+in a handwriting peer tutoring pilot study most often made mistakes
+qualitatively classified as inappropriate \emph{internal proportions} or
+\emph{global deformations}. As exemplified in Figure \ref{fig:sampleLetters},
+the shapes generated by the system exhibit the same kind of deformities. Chandra
+identifies other, less common, mistakes that involve topological changes (like
+letters being broken in subparts, extra strokes, etc.). Using a database of
+children's letters when available may yield potential for better parameterizing
+these other mistakes. However, as an initial approximation, the shape models
+generated from PCA on a dataset of only adults' writing have shown to be
+well-suited to generate `poor' letters that children were able to recognize and
+successfully improve.
 

### 2014-12-11 main.tex
Forgot a bit of anonymity...
copyedit

@@
 \title{\LARGE \bf
+Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
 % what about:
-When Children Teach a Robot to Write
+% When Children Teach a Robot to Write
 % ?
@@
 \cite{Rohrbeck2003}. To our best knowledge, the application of the paradigm to
-handwriting intervention remains however unexplored. One reason for this may due
+handwriting intervention remains, however, unexplored. One reason for this may due
 to the requirement of an appropriately unskilled peer for the target child to
@@
 benefits, and not so much on the learning experienced by the human tutor. Our
-work focuses on this later aspect. A robotic learning agent which employs the learning by teaching paradigm has 
+work focuses on this latter aspect. A robotic learning agent which employs the learning by teaching paradigm has 
 previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
@@
 
-Our work significantly extends this line of work in two direction, first by
-proposing an autonomous robotic partner, second by investigating the scaffolding
-of children' acquisition of a challenging physical skill (handwriting).
+Our work significantly extends this line of work in two directions, first by
+proposing an autonomous robotic partner, second by investigating the context
+of children's acquisition of a challenging physical skill (handwriting).
 
@@
 that different quality shapes can be generated, depending on the parameters input to
-the letter models. This allows to configure the system such as to improve its writing 
+the letter models. This allows us to configure the system such as to improve its writing 
 by modifying the parameters based on feedback from the 
@@
 which may be ascribed descriptive interpretations (not just numerical) is an
-advantage of this method, given its intended use with humans: It is for instance
+advantage of this method, given its intended use with humans. It is, for instance,
 possible for a teacher to create initial letters with a particular feature (a wide
@@
 letters being broken in subparts, extra strokes, etc.). Using a database of
-children's letters when available may yield potential for better parameterizing
+children's letters when available may yield potential for better parameterising
 these other mistakes. However, as an initial approximation, the shape models
 generated from PCA on a dataset of only adults' writing have shown to be
-well-suited to generate `poor' letters that children were able to recognize and
+well-suited to generate `poor' letters that children were able to recognise and
 successfully improve.
@@
 handwriting intervention. 
-Preliminary studies at two schools in the Geneva area, involving above 50 children, 
+Preliminary studies at two schools in the Geneva area, involving over 50 children, 
 have been conducted to evaluate the feasibility and technical soundness of the 
@@
 letter. This suggests that users may project human-like learning features, such as 
-forgetfulness, onto the robot, which can be implemented 
-in the learning agent. This may need to be capitalised on when considering how to 
+forgetfulness, onto the robot, whether or not they are technically present.
+This may need to be capitalised on when considering how to 
 extend the interaction for long time frames, as the present system -- with a learning rate 
@@
 
-And the strong social impact of early educational problems makes continued research in this field
+The strong social impact of early educational problems makes continued research in this field
 an undoubtedly meaningful challenge for robotics and human-robot interaction.
@@
 % Anonymized for double-blind review
-\section*{Acknowledgments}
-
-This research was supported by the Swiss National Science Foundation through the
-National Centre of Competence in Research Robotics.
+%\section*{Acknowledgments}
+%
+%This research was supported by the Swiss National Science Foundation through the
+%National Centre of Competence in Research Robotics.
 

### 2014-12-11 main.tex
Change 'has been's to 'is'

@@
 is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
-concerned with learning of a physical skill, the learning agent developed has 
-been embodied in a humanoid robot which is capable of physically demonstrating 
+concerned with learning of a physical skill, the learning agent developed is 
+embodied in a humanoid robot which is capable of physically demonstrating 
 handwriting trajectories to its child learning partner.
@@
 
-For the development of a learning algorithm in the context of
-handwriting, a parameterisation of letters and their deformities has been sought such 
+A parameterisation of letters and their deformities was sought such 
 that different quality shapes can be generated, depending on the parameters input to
@@
 
-PCA has been performed on a set of letter paths captured from a digital pen,
+PCA is performed on a set of letter paths captured from a digital pen,
 using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
@@
 
-PCA has been performed on all of the paths of a particular allograph in the
+PCA is performed on all of the paths of a particular allograph in the
 dataset individually, to reduce the $2n$-dimensional space for that shape to one 
@@
 towards those of the demonstration. In the results presented in this work, the
-linear update equation shown in (\ref{eq:update}) has been used, where ${\bf p}$ is the
+linear update equation shown in (\ref{eq:update}) is used, where ${\bf p}$ is the
 learned parameter vector at time step $k$, and $\alpha$ is the learning rate,
@@
 The {\sc nao} V4 humanoid robot, which has been developed by Aldebaran Robotics and 
-purposely designed to look approachable \cite{Gouaillier2008}, has been used for
+purposely designed to look approachable \cite{Gouaillier2008}, is used for
 this work. It is a commercially affordable biped robot, 58cm tall, with 25
@@
 capture the engagement of the child participant in the action. Aldebaran's NaoQi API
-has been used for the inverse kinematics of the trajectory following. The Robot
+is used for the inverse kinematics of the trajectory following. The Robot
 Operating System (ROS)\footnote{The ROS stack for {\sc nao} is available at:
-\url{http://wiki.ros.org/nao_robot}.} has been used for integration of the {\sc nao}
+\url{http://wiki.ros.org/nao_robot}.} is used for integration of the {\sc nao}
 with external reference frames, such as the tablet's location, 
@@
 a ROS topic and display the trajectory as an
-animation. Synchronisation between the tablet and the robot has been achieved by
+animation. Synchronisation between the tablet and the robot is achieved by
 using NTP servers to synchronise device clocks; passing only the necessary number of points (7)
@@
         capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
-        way which is believable for interacting with children. This has been
+        way which is believable for interacting with children. This is
         accomplished by leveraging simulated handwriting with a synchronised

### 2014-12-12 rebuttal_sorted.txt
R1 abstract 'context of robotics outside coding' concern
R1 'necessary letter models' statement
additional related work (in own section)

@@
 >    The work is sufficiently interesting without this in any case.
-
+DONE
 We did not intend to claim such a contribution, but we can understand how the misunderstanding can arise from the second-last paragraph and the missing related robotics work. Both will be modified.
@@
 >    addressed by the authors. This work needs to be properly situated.
-
+DONE
 We agree and greatly appreciate the numerous provided pointers to the literature. 
@@
 >    context here?
+DONE
+
 >
@@
 >    Necessary according to what criteria?
+DONE
 
@@
 >    it’s relevant to this work.
-
 The title was meant to re-purpose the idiom in the context of children with handwriting difficulties having an opportunity to improve through teaching.
@@
 >    generally “proven” when based on a limited sample.)
-
+DONE
 We agree with the points raised: it is a limitation of the question, which we imposed ourselves to avoid putting words in the children's mouths if we were to ask directly if the robot's writing was believable.
@@
 >    they were the ones teaching it”? 
-
+DONE
 Initial parameters were drawn from a range chosen to generate shapes for letters 'e' and 's' which would elicit correction.
@@
 >    improves toddler vocabulary skills”.
-
+DONE
 Again, we agree and will comply, and would like to thank the reviewer for their time in compiling this list.
@@
 >    and an apparent experimenter’s face appearing in Figure 8.
-
+DONE
 This was an oversight on our side and we apologise for letting it go undetected.
@@
 >
+
 >    “tablet-based application, which children are increasingly recognizing
@@
 >    to be “disposable”.
+DONE
 >
@@
 >
+DONE
+
 >    - many long sentences that are difficult to read -
@@
 >
->    protege effect, inappropriate internal proportions, global deformations
+>    protege effect, 
+DONE
+
+>    inappropriate internal proportions, global deformations
 
@@
 >    attention to the studies.
-
+DONE
 We believe the technical details to be relevant for those wishing to replicate the new technology presented.
@@
 >    results or to analyze how the interaction differed in these groups.
-
+DONE
 It will be more clearly stated that the results presented were from the 7-8yr age group only, not those aged 6-7 in the pilot study.

### 2014-12-12 main.tex
additional related work (in own section)

@@
 
+%Due to the intended use in a school environment, a commercially
+%affordable {\sc nao} humanoid robot has been used. Its writing capabilities 
+%have been implemented by leveraging synchronisation with a tablet display to
+%simulate fine motor skills otherwise infeasible for the robot.
+
+Within this article, Section \ref{sec:learningAlgorithm} presents the novel work in the area of
+artificial intelligence to develop a learning algorithm suitable for a teachable
+agent in the context of handwriting. Section \ref{sec:robotWriting} details the
+extension of this algorithm to an embodied robotic learning agent, including the
+new approach for achieving simulated fine motor skills on commercially
+affordable humanoid robots such as the {\sc nao}. Section \ref{sec:experiment} explores the 
+contributions made to the study of human-robot interaction, in discussing the
+use of the system with primary school children and its potential as a tool for
+addressing wider pedagogical research questions in education.
+Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the content and impact of the article's contributions.
+
+\section{Related work}
 Teachable computer-based agents have previously been used to encourage the 
@@
 improvements in handwriting interventions in which letter formations are 
-demonstrated to participants~\cite{Berninger1997}.
-
-Werfel suggests in~\cite{Werfel2014} that, until now, most of the work investigating how
-humans can teach robots (in particular, physical skills) focuses on the robot's
-benefits, and not so much on the learning experienced by the human tutor. Our
-work focuses on this latter aspect. A robotic learning agent which employs the learning by teaching paradigm has 
+demonstrated to participants~\cite{Berninger1997}. Furthermore, when compared
+to screen-based agents, robotic partners have been shown in some contexts to 
+increase users' compliance with tasks~\cite{Bainbridge2011}, maintain more 
+effective long-term relationships~\cite{Kidd2008}, and produce greater 
+learning gains when acting as tutors~\cite{Leyzberg2012}: benefits which we
+hope will transfer into this application.
+
+Robots have been used as teachers or social partners to promote children's
+learning in a range of contexts, most commonly langauge skills~\cite{Han2010}, 
+but also contexts such as logic puzzles~\cite{Leyzberg2014} and in music 
+classes~\cite{Han2009}.
+Werfel suggests in~\cite{Werfel2014} that, until now, most of the work 
+investigating how humans can instead teach robots (language \cite{Saunders2010} or 
+table tennis \cite{Mulling2013}, for example) focuses on the robot's
+benefits rather than the learning experienced by the human tutor. Our
+work concentrates on this latter aspect.
+
+A robotic learning agent which 
+employs the learning by teaching paradigm has 
 previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
@@
 teach it, but with no long-term memory or learning algorithm in place.
-
-Our work significantly extends this line of work in two directions, first by
-proposing an autonomous robotic partner, second by investigating the context
+Our project significantly extends this line of work in two ways. First, by
+proposing a robotic partner which is fully autonomous in its learning,
+and second, by investigating the context
 of children's acquisition of a challenging physical skill (handwriting).
-
-Due to the intended use in a school environment, a commercially
-affordable {\sc nao} humanoid robot has been used. Its writing capabilities 
-have been implemented by leveraging synchronisation with a tablet display to
-simulate fine motor skills otherwise infeasible for the robot.
-
-Within this article, Section \ref{sec:learningAlgorithm} presents the novel work in the area of
-artificial intelligence to develop a learning algorithm suitable for a teachable
-agent in the context of handwriting. Section \ref{sec:robotWriting} details the
-extension of this algorithm to an embodied robotic learning agent, including the
-new approach for achieving simulated fine motor skills on commercially
-affordable humanoid robots. Section \ref{sec:experiment} explores the 
-contributions made to the study of human-robot interaction, in discussing the
-use of the system with primary school children and its potential as a tool for
-addressing wider pedagogical research questions in education.
-Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the content and impact of the article's contributions.
 

### 2014-12-12 rebuttal_sorted.txt
update title

@@
 >    it’s relevant to this work.
+DONE
 The title was meant to re-purpose the idiom in the context of children with handwriting difficulties having an opportunity to improve through teaching.

### 2014-12-12 main.tex
update title
R1 scaffolding conclusion comment

@@
 \title{\LARGE \bf
-Children Teach a Robot to Write: A Teachable Robotic Agent which Engages in Simulated Handwriting %still not sure
-% what about:
-% When Children Teach a Robot to Write
-% ?
+When Children Teach a Robot to Write: An Autonomous Teachable Humanoid Which Uses Simulated Handwriting
 }
@@
 
-We believe that this article introduces three noteworthy contributions: an innovative
-application of data processing and artificial intelligence for the
-learning of hand-written letters suitable for educative purposes; a robotic
-system which has been experimentally shown to provide convincing scaffolding for
-complex human-robot interactions (teacher-learner social interactions, learning by
-demonstration, simulated robotic fine motor skills); and an initial experimental investigation of what appears to be a
-new role for robots in education.
-
-Specifically, the technical challenges involved in developing a teachable
-robotic agent in the context of handwriting which have been addressed in this
-work include:
-
-\begin{itemize}
-
-    \item developing capabilities for a robot with limited fine motor
-        capabilities, in particular the {\sc nao} robot, to engage in the act of handwriting in a
-        way which is believable for interacting with children. This is
-        accomplished by leveraging simulated handwriting with a synchronised
-        tablet communicating via ROS;
-
-    \item developing an algorithm capable of incorporating user feedback and
-        demonstrations in order to adapt artificially generated handwriting quality so as
-        to simulate a teachable agent, which has been implemented by maintaining
-        a learning algorithm in the parameter space of the PCA-based shape models and
-        converging towards the parameters of user demonstrations; and
-
-    \item integrating the system into a working interaction suitable for
-        engaging children in the learning by teaching paradigm, accomplished by
-        fusing the robotic drawing capabilities and the learning algorithm for
-        handwritten letters established with a central controller which manages
-        the flow of the interaction, turn taking and integration of the connected 
-	devices.
-
-\end{itemize}
+We believe that this article introduces three noteworthy contributions: an 
+innovative application of artificial intelligence for the learning of 
+hand-written letters suitable for educative purposes; a method for a 
+commercially affordable humanoid, in particular the {\sc nao} robot, to exhibit
+simulated fine motor capabilities; and a working autonomous interaction 
+suitable for engaging children in complex human-robot interactions, such as 
+teacher-learner social interactions and learning from demonstration.
 

### 2014-12-12 rebuttal_sorted.txt
R1 scaffolding conclusion comment
R1 Chandra definitions

@@
 >    capabilities… have been demonstrated.”
-
+DONE
 We agree that this was a wording issue on our part and will make reference to the classification methods used in previous work to determine such categories, and the confirmation that was received by teachers that the deformations are similar to childrens'.
@@
 >    I don’t know because they removed the actor in these sentences.
+DONE
+
 >
@@
 >
+DONE
 
@@
 >    inappropriate internal proportions, global deformations
+DONE
 

### 2014-12-12 main.tex
R1 photo anonymisation
R1 Chandra definitions

@@
 in a handwriting peer tutoring pilot study most often made mistakes
-qualitatively classified as inappropriate \emph{internal proportions} or
-\emph{global deformations}. As exemplified in Figure \ref{fig:sampleLetters},
-the shapes generated by the system exhibit the same kind of deformities. Chandra
-identifies other, less common, mistakes that involve topological changes (like
-letters being broken in subparts, extra strokes, etc.). Using a database of
+qualitatively classified as \emph{internal proportions} (inappropriate 
+proportion of the different strokes within a letter), or \emph{global 
+deformations} (overall deformation in the appearance of the letter). As 
+exemplified in Figure \ref{fig:sampleLetters}, the shapes generated by the 
+system exhibit the same kind of deformities. Chandra identifies other, less 
+common, mistakes which involve topological changes, such as letters being 
+broken into subparts or mirrored. Using a database of
 children's letters when available may yield potential for better parameterising
@@
 generated from PCA on a dataset of only adults' writing have shown to be
-well-suited to generate `poor' letters that children were able to recognise and
-successfully improve.
+well-suited to generate `poor' letters that children were able to identify as
+such and successfully improve.
 
@@
             \label{fig:first}
-            \includegraphics[width=0.2\textwidth]{figures/1card.png}
+            \includegraphics[width=0.2\textwidth]{figures/1anon.jpg}
         }~
@@
            \label{fig:second}
-           \includegraphics[width=0.2\textwidth]{figures/2word.png}
+           \includegraphics[width=0.2\textwidth]{figures/2anon.jpg}
         }\\ %  ------- End of the first row ----------------------%
@@
             \label{fig:third}
-            \includegraphics[width=0.2\textwidth]{figures/4correct.png}
+            \includegraphics[width=0.2\textwidth]{figures/3anon.jpg}
         }~
@@
             \label{fig:fourth}
-            \includegraphics[width=0.2\textwidth]{figures/5iterateAsk.png}
+            \includegraphics[width=0.2\textwidth]{figures/4anon.jpg}
         }%

### 2014-12-12 main.tex
R5 LfD physical skills similarity concerns

@@
 learning in a range of contexts, most commonly langauge skills~\cite{Han2010}, 
-but also contexts such as logic puzzles~\cite{Leyzberg2014} and in music 
-classes~\cite{Han2009}.
+but also applications such as logic puzzles~\cite{Leyzberg2014}, in music 
+classes~\cite{Han2009}, and physical skills such as caligraphy \cite{Matsui2013}.
 Werfel suggests in~\cite{Werfel2014} that, until now, most of the work 
@@
 benefits rather than the learning experienced by the human tutor. Our
-work concentrates on this latter aspect.
+work concentrates on this latter aspect. We note that our work differs from those
+where a robot develops physical skills through `learning 
+from demonstration' from humans, as the agent we present is only simulating 
+fine motor skills for interaction purposes.
 

### 2014-12-12 main.tex
various changes

@@
 path. The observation shapes are normalised to have a unit maximum dimension 
-and centre at the origin.
+and {\bf 0} mean.
 
@@
     (right) of varying the first three parameters (each row) of a shape model.
-     The extent to which each
-parameter is varied is dependent on the eigenvalue $\lambda$ corresponding to
+     Parameter variation is dependent on the eigenvalue $\lambda$ corresponding to
 the parameter's eigenvector. The percentage of the total variance in the dataset
@@
 demonstration shape by projecting the features of the observed shape into the
-lower-dimensional space determined by the model. Mathematically, given a
-demonstration ${\bf x}_{demo}$, the associated parameters may be determined as in
-(\ref{eq:param}), which will reconstruct an approximate shape.
-
-%really this is the same as eq 3
-\begin{equation}\label{eq:param}
-{\bf p}_{demo} ={\bf \Phi}^T ({\bf{x}_{demo}}-\bf{\bar{x}})
-\end{equation}
-
-%The parameters which are determined for a shape in (\ref{eq:param}) will not
-%reconstruct the shape exactly if $N<2n$, but rather will reconstruct the closest
-%point in the $N$-dimensional space which the eigenvectors span.
+lower-dimensional space determined by the model. Mathematically, the parameters
+associated with a demonstration ${\bf x}_{demo}$ are determined as in
+(\ref{eq:paramCalc}) with ${\bf x}={\bf x}_{demo}$, and will reconstruct the 
+closest approximate shape.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section{An Embodied Handwriting Learning Agent with the NAO Humanoid Robot}
+\section{Embodiment of the Learning Agent with the NAO Humanoid Robot}
 \label{sec:robotWriting}
@@
 
-As a result of the pilot study, two key observations were acted on. The first
+As a result of the pilot study, we acted on two key observations. The first
 was that children appeared to have a difficult time providing demonstrations to
@@
 
-It has been concluded following the second study that the system has 
+We have concluded following the second study that the system has 
 been validated as a technically sound autonomous interaction. 
@@
     the participants had become intrinsically motivated to engage in the
-    interaction.
+    interaction, as we anticipated.
 
@@
 nominal protocol presented in Section~\ref{sec4}, and consequently still
-requires the presence of an experimenter. The interaction finite state machine would
+requires the supervision of an experimenter. The interaction finite state machine would
 require extension in non-trivial ways to allow for long, fully autonomous
@@
 possiblity to focus the interaction design on group-based interaction with the robot 
-in order to alleviate the necessity of a conversational agent, there is reason to 
+in order to alleviate the necessity of a conversational agent, we find reason to 
 believe that constructing such a social interaction is not a trivial task. Anecdotes 
@@
 demonstrations to the robot, which may or may not be as damaging to a child's 
-self-efficacy as when they are criticised in a typical educational context. In addition,
-on occassions where a pair of children came to teach the robot different styles of a 
-particular letter, they did not discuss with each other their different writing styles 
-and the effect on the teaching efficiency. This may suggest that a constructed social context in 
-which verbalising opinions about differences is encouraged may be necessary to get children 
-to cooperate in teaching the robot in a group setting.  
+self-efficacy as when they are criticised in a typical educational context.
+
+%In addition,
+%on occassions where a pair of children came to teach the robot different styles of a 
+%particular letter, they did not discuss with each other their different writing styles 
+%and the effect on the teaching efficiency. This may suggest that a constructed social context in 
+%which verbalising opinions about differences is encouraged may be necessary to get children 
+%to cooperate in teaching the robot in a group setting.  
 %- "Would have problems with the 'n'" - (8) projecting human learning characteristics.
@@
 long-term remains to be seen. On one occasion during the preliminary studies, a 
-child's response to whether or not the {\sc nao} could write its own name included that it 
+child's response to whether or not the {\sc nao} could write its own name (not
+previously demonstrated) included that it 
 may have problems with the `n', as the child had been correcting the robot on this 
-letter. This suggests that users may project human-like learning features, such as 
-forgetfulness, onto the robot, whether or not they are technically present.
+letter. We believe that the user was projecting human-like learning features, such as 
+forgetfulness, onto the robot, although they were not technically present in the system.
 This may need to be capitalised on when considering how to 
-extend the interaction for long time frames, as the present system -- with a learning rate 
+extend the interaction for long-term use, as the present system -- with a learning rate 
 such that progress is evident to the user -- will cause convergence for a letter within a 
@@
 
-In the scope of open technical questions for enabling long-term interaction, it remains to be seen how shape models
-for letters might be generated which capture the full range of mistakes typical
-of children learning handwriting. This includes extending the current system capable of
-incorporating internal proportion and global deformation errors to one which can
-also generate missing subparts of the letter, or write letters backwards, for example. 
-While it is expected that incorporating a
-database of letters drawn by children into the shape modeling process would
-facilitate this, the current system has conceptual -- a PCA-only approach can not
-generate or learn a different shape topology -- and technical -- no support is currently implemented for
-multi-stroke shapes -- limitations which would need to be overcome.
+We expect that incorporating a
+database of letters drawn by children into the shape modeling process will
+facilitate generating shape models which capture a wider range of mistakes typical
+of children learning handwriting. However, the current system has conceptual -- 
+a PCA-only approach can not generate or learn a different shape topology -- and 
+technical -- no support is currently implemented for shapes which require pen
+lifting between strokes -- limitations which would need to be overcome.
 

### 2014-12-12 main.tex
Rephrase the related work section

@@
 \section{Related work}
+
 Teachable computer-based agents have previously been used to encourage the
-``protégé effect'', wherein students invest more effort into learning when it
-is for a teachable agent than for themselves~\cite{Chase2009}. As we are 
-concerned with learning of a physical skill, the learning agent developed is 
-embodied in a humanoid robot which is capable of physically demonstrating 
-handwriting trajectories to its child learning partner.
-This is supported by the potential for motor mimicry to yield significant 
-improvements in handwriting interventions in which letter formations are 
-demonstrated to participants~\cite{Berninger1997}. Furthermore, when compared
-to screen-based agents, robotic partners have been shown in some contexts to 
-increase users' compliance with tasks~\cite{Bainbridge2011}, maintain more 
-effective long-term relationships~\cite{Kidd2008}, and produce greater 
-learning gains when acting as tutors~\cite{Leyzberg2012}: benefits which we
-hope will transfer into this application.
+``protégé effect'', wherein students invest more effort into learning when it is
+for a teachable agent than for themselves~\cite{Chase2009}.  As we are concerned
+with learning of a physical skill, the learning agent developed is embodied in a
+humanoid robot which is capable of physically demonstrating handwriting
+trajectories to its child learning partner.  This is supported by the potential
+for motor mimicry to yield significant improvements in handwriting interventions
+in which letter formations are demonstrated to
+participants~\cite{Berninger1997}. Furthermore, when compared to screen-based
+agents, robotic partners have been shown in some contexts to increase users'
+compliance with tasks~\cite{Bainbridge2011}, maintain more effective long-term
+relationships~\cite{Kidd2008}, and produce greater learning gains when acting as
+tutors~\cite{Leyzberg2012} that can be adapted to each
+learner~\cite{Leyzberg2014}.
 
 Robots have been used as teachers or social partners to promote children's
-learning in a range of contexts, most commonly langauge skills~\cite{Han2010}, 
-but also applications such as logic puzzles~\cite{Leyzberg2014}, in music 
-classes~\cite{Han2009}, and physical skills such as caligraphy \cite{Matsui2013}.
-Werfel suggests in~\cite{Werfel2014} that, until now, most of the work 
-investigating how humans can instead teach robots (language \cite{Saunders2010} or 
-table tennis \cite{Mulling2013}, for example) focuses on the robot's
-benefits rather than the learning experienced by the human tutor. Our
-work concentrates on this latter aspect. We note that our work differs from those
-where a robot develops physical skills through `learning 
-from demonstration' from humans, as the agent we present is only simulating 
-fine motor skills for interaction purposes.
+learning in a range of contexts, most commonly related to language
+skills~\cite{Han2010}, and less often to physical skills (such as
+calligraphy~\cite{Matsui2013}).  Looking at the converse (humans \emph{teaching}
+robots), Werfel notes in~\cite{Werfel2014} that most of the work focuses on the
+robot's benefits (in terms of language~\cite{Saunders2010} or
+physical~\cite{Mulling2013} skills, for example) rather than the learning
+experienced by the human tutor itself.  Our work concentrates on this latter
+aspect: by demonstrating handwriting to a robot, we aim at improving the
+\emph{child} performances. Note that our work must be distinguished from
+traditional ``learning from demonstration'' approaches, as the agent we present
+is only simulating fine motor skills for interaction purposes.
 
-A robotic learning agent which 
-employs the learning by teaching paradigm has 
+A robotic learning agent which employs the learning by teaching paradigm has
 previously been developed by Tanaka and Matsuzoe~\cite{Tanaka2012}. In their
 system, children learn vocabulary by teaching the {\sc nao} robot to act out
-verbs. The robot is tele-operated and mimics the actions that the children
-teach it, but with no long-term memory or learning algorithm in place.
-Our project significantly extends this line of work in two ways. First, by
-proposing a robotic partner which is fully autonomous in its learning,
-and second, by investigating the context
-of children's acquisition of a challenging physical skill (handwriting).
+verbs. The robot is tele-operated and mimics the actions that the children teach
+it, but with no long-term memory or learning algorithm in place.  Our project
+significantly extends this line of work in two ways. First, by investigating the
+context of children's acquisition of a challenging physical skill (handwriting),
+and second by proposing a robotic partner which is fully autonomous in its
+learning.
 

### 2014-12-12 main.tex
final changes throughout

@@
 addressing wider pedagogical research questions in education.
-Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the content and impact of the article's contributions.
+Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the impact of the article's contributions.
 
@@
 relationships~\cite{Kidd2008}, and produce greater learning gains when acting as
-tutors~\cite{Leyzberg2012} that can be adapted to each
-learner~\cite{Leyzberg2014}.
+tutors~\cite{Leyzberg2012}.
 
@@
 physical~\cite{Mulling2013} skills, for example) rather than the learning
-experienced by the human tutor itself.  Our work concentrates on this latter
+experienced by the human tutor themselves.  Our work concentrates on this latter
 aspect: by demonstrating handwriting to a robot, we aim at improving the
-\emph{child} performances. Note that our work must be distinguished from
-traditional ``learning from demonstration'' approaches, as the agent we present
-is only simulating fine motor skills for interaction purposes.
+\emph{child's} performance. Note that our work must be distinguished from
+``learning from demonstration'' approaches to robots learning physical skills, 
+as the agent we present is only simulating fine motor skills for interaction 
+purposes.
 
@@
 
-A parameterisation of letters and their deformities was sought such 
+A parameterisation of letters and their deformities is used such 
 that different quality shapes can be generated, depending on the parameters input to
-the letter models. This allows us to configure the system such as to improve its writing 
+the letter models. This allows us to configure the system to improve its writing 
 by modifying the parameters based on feedback from the 
@@
 
-We use statistical shape modelling as an approach for a shape model which can
+We use statistical shape modelling for generating a shape model which can
 appropriately represent realistic variations in shapes. Statistical shape
@@
 unanticipated user input (such as shapes drawn backwards),
-the features are currently taken as $n$ uniformly spaced points along the shape
+the features are currently taken as $n=70$ uniformly spaced points along the shape
 path. The
@@
 Equation (\ref{eq:projection}) represents the projection from the original 
-$2n$-dimensional feature space $(n=70)$ to a reduced $N$-dimensional space, where ${\bf p}$
+$2n$-dimensional feature space to a reduced $N$-dimensional space, where ${\bf p}$
 contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
@@
 the largest $N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
-observations, as shown in (\ref{eq:transformCalc}) \cite{Stegmann2002}. 
+observations~\cite{Stegmann2002}, as shown in (\ref{eq:transformCalc}). 
 If there is correlation between the points in the observations, there will be
@@
 with $N=10$ dimensions.
-As such,
-each shape may be approximated by the mean shape of the allograph plus a sum of the top 10
+Each shape is then approximated by the mean shape of the allograph plus a sum of the top 10
 eigenvectors, weighted by the parameter vector ${\bf p}$. 
@@
 
-(\ref{eq:projection}) may also be used
+Equation (\ref{eq:projection}) may also be used
 to generate new shapes based on the parameters ${\bf p}$ which are used. ${\bf
@@
 modelling approach to produce compact parameterisation of shapes.
-
-%Clusters within paths of a particular letter have been identified using K-means
-%clustering to group different styles of writing the letter (\emph{allographs}),
-%such that the parameters in the resulting model are only representative of the
-%specific allograph of the letter in the dataset. 
-% * <deanna.m.hood@gmail.com> 2014-09-03T13:05:23.576Z:
-%
-% in the end this was pointless so maybe not worth mentioning
-%
 
@@
 advantage of this method, given its intended use with humans. It is, for instance,
-possible for a teacher to create initial letters with a particular feature (a wide
+possible for a teacher to create letters -- which will be used as a starting point
+for the system -- with a particular feature (a wide
 `s' or a `d' with a large loop, for example).
@@
 from a distribution with
-standard deviation of $3\sqrt\lambda_i$ rather than the $\sqrt\lambda_i$
+standard deviation of $3\sqrt\lambda_i$, rather than the $\sqrt\lambda_i$
 standard deviation observed in the dataset.
@@
 
-For the statistical shape model employed by the system, the method for
+The method we employ for
 responding to user demonstrations is to move the learning algorithm's parameters
@@
 which yield an unacceptable shape. This is especially true if the demonstration
-shape is of a different style to that learnt at time $k$, as there are no
+shape is of a different style to that learnt at time $k$ (see 
+Figure~\ref{fig:eDemo}), as there are no
 restrictions imposed on parameter values. However, the proposed method for adapting to
@@
 demonstrations of the same letter, the system would eventually approach the
-demonstration shape (see Figure \ref{fig:eDemo}. As a result, the event of poor-looking 
+demonstration shape. As a result, the event of poor-looking 
 intermediate letters
@@
 
-The {\sc nao} V4 humanoid robot, which has been developed by Aldebaran Robotics and 
-purposely designed to look approachable \cite{Gouaillier2008}, is used for
+The {\sc nao} V4 humanoid robot, which has been purposely designed by 
+Aldebaran Robotics to look approachable \cite{Gouaillier2008}, is used for
 this work. It is a commercially affordable biped robot, 58cm tall, with 25
@@
 networking between the tablet and the robot, such as the overheads associated
-with connections, ports, message formats, etc. have been simplified.
+with connections, ports, etc. have been simplified.
 
@@
 intended for based on their position on the tablet. The output shapes from the 
-learning algorithm are sent by the controller to the devices which write them.
+learning algorithm are then sent again to the devices which write them.
 
@@
     \item The participant shows the robot one of seven different 3-letter words
-        to write, are made up of 7 possible letters (`c', `e',
+        to write, made up of 7 possible letters (`c', `e',
         `n', `o', `s', `u', `w'). Fiducial markers which are printed on the word
@@
 Initial parameters were drawn from a range purposely chosen to generate shapes 
-for letters 'e' and 's' which would elicit correction. For the other letters, 
+for letters `e' and `s' which would elicit correction. For the other letters, 
 parameters were fixed, generating shapes which some groups still chose to correct 
-(e.g. 13/14 for 'n' and 2/14 for 'c'). The duration of the sessions
+(e.g. 13/14 for `n' and 2/14 for `c'). The duration of the sessions
 was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).
@@
 we want to address research questions which involve the measurement of learning gains. 
-Several challenges are raised in developing such long-term capabilities for the system,
- from both technical and sociological points of view. %not sure this makes sense
+Several challenges are raised in developing such long-term capabilities for the system.
 
@@
 
-With some of these challenges addressed, further steps can be made towards 
-answering the overarching question of what impact the 
-addition of such a teachable robotic agent would have on handwriting interventions, including the effect on the 
-participants' self-esteem, motivation, and learning gains. % does it impact the
-%motivation of the participants, their self-esteem, and/or the learning gains
-%that they experience? We are currently considering running a long-term study
-%that would provide better evidences to answer these questions.
+Addressing these challenges will take us further towards answering if 
+the addition of a teachable robotic agent to handwriting interventions 
+would benefit the participants' self-esteem, motivation, and learning gains.
 
@@
 
-\addtolength{\textheight}{-.5cm}   % This command serves to balance the column lengths
+\addtolength{\textheight}{-11.2cm}   % This command serves to balance the column lengths
                                   % on the last page of the document manually. It shortens
@@
 
-We believe that this article introduces three noteworthy contributions: an 
+We believe this article introduces three noteworthy contributions: an 
 innovative application of artificial intelligence for the learning of 

### 2014-12-12 main.tex
Revert "R1 scaffolding conclusion comment"
This reverts commit ff8c0552d5f85ff625d1f4f1d37b20aae701e09a.

@@
 
-\addtolength{\textheight}{-11.2cm}   % This command serves to balance the column lengths
+\addtolength{\textheight}{-6.3cm}   % This command serves to balance the column lengths
                                   % on the last page of the document manually. It shortens
@@
 
-We believe this article introduces three noteworthy contributions: an 
-innovative application of artificial intelligence for the learning of 
-hand-written letters suitable for educative purposes; a method for a 
-commercially affordable humanoid, in particular the {\sc nao} robot, to exhibit
-simulated fine motor capabilities; and a working autonomous interaction 
-suitable for engaging children in complex human-robot interactions, such as 
-teacher-learner social interactions and learning from demonstration.
+We believe that this article introduces three noteworthy contributions: an
+innovative application of data processing and artificial intelligence for the
+learning of hand-written letters suitable for educative purposes; a robotic
+system which was able to provide scaffolding for complex human-robot
+interactions (teacher-learner social interactions, learning by demonstration,
+simulated robotic fine motor skills) during two preliminaries studies; and an
+initial experimental investigation of what appears to be a new role for robots
+in education.
 
-However, we believe that the strongest impact of this work is for the human-robot
-interaction community and relates to the very \emph{nature} of the interaction
-fostered by this research. The work presented here investigates a particular
-role for a robot in the education of handwriting: not only is the robot actively
-performing the activity by drawing letters, but it does so in a way that engages
-the child in a very specific social role. The child is the teacher in this relationship and the robot is
-the learner: the child must engage in a (meta-) cognitive relationship with the robot
-to try to understand why the robot fails and how to help it best.  Here, the
-robot is more than just an activity facilitator or orchestrator -- its physical presence
-and embodiment induce agency and anthropomorphising, and cognitively engage the
-child into the learning activity, which we predict will lead to higher learning
-efficacy.
+Specifically, the technical challenges involved in developing a teachable
+robotic agent in the context of handwriting which have been addressed in this
+work include:
+
+\begin{itemize}
+
+    \item developing capabilities for a robot with limited fine motor
+        capabilities, in particular the {\sc nao} robot, to engage in the act of
+        handwriting in a way which is believable for interacting with children.
+        This is accomplished by leveraging simulated handwriting with a
+        synchronised tablet communicating via ROS;
+
+    \item developing an algorithm capable of incorporating user feedback and
+        demonstrations in order to adapt artificially generated handwriting
+        quality so as to simulate a teachable agent, which has been implemented
+        by maintaining a learning algorithm in the parameter space of the
+        PCA-based shape models and converging towards the parameters of user
+        demonstrations; and
+
+    \item integrating the system into a working interaction suitable for
+        engaging children in the learning by teaching paradigm, accomplished by
+        fusing the robotic drawing capabilities and the learning algorithm for
+        handwritten letters established with a central controller which manages
+        the flow of the interaction, turn taking and integration of the
+        connected devices.
+
+\end{itemize}
+
+However, we believe that the strongest impact of this work is for the
+human-robot interaction community and relates to the very \emph{nature} of the
+interaction fostered by this research. The work presented here investigates a
+particular role for a robot in the education of handwriting: not only is the
+robot actively performing the activity by drawing letters, but it does so in a
+way that engages the child in a very specific social role. The child is the
+teacher in this relationship and the robot is the learner: the child must engage
+in a (meta-) cognitive relationship with the robot to try to understand why the
+robot fails and how to help it best.  Here, the robot is more than just an
+activity facilitator or orchestrator -- its physical presence and embodiment
+induce agency and anthropomorphising, and cognitively engage the child into the
+learning activity, which we predict will lead to higher learning efficacy.
 

### 2014-12-12 main.tex
[cosmetic] lines wrapping

@@
 
-Handwriting difficulties in children at an early age often negatively affect
-the academic performance of the students \cite{Christensen2005}, in addition to
+Handwriting difficulties in children at an early age often negatively affect the
+academic performance of the students \cite{Christensen2005}, in addition to
 their self-esteem being adversely affected \cite{Malloy1995}, causing them to
-shy away from expressing what they know \cite{Medwell2008}.
-Successful interventions for children with handwriting difficulties involve the
-student in many sessions where they are engaged in physically practising the
-skill \cite{Hoy2011}. However, the link between handwriting difficulties and low
+shy away from expressing what they know \cite{Medwell2008}.  Successful
+interventions for children with handwriting difficulties involve the student in
+many sessions where they are engaged in physically practising the skill
+\cite{Hoy2011}. However, the link between handwriting difficulties and low
 self-efficacy \cite{Engel-Yeger2009} results in children who are unmotivated to
@@
 \cite{Rohrbeck2003}. To our best knowledge, the application of the paradigm to
-handwriting intervention remains, however, unexplored. One reason for this may due
-to the requirement of an appropriately unskilled peer for the target child to
-tutor, as this may present a logistical constraint if the target child is the
+handwriting intervention remains, however, unexplored. One reason for this may
+due to the requirement of an appropriately unskilled peer for the target child
+to tutor, as this may present a logistical constraint if the target child is the
 lowest performer in their class.  In some cases, it may be appropriate for a
@@
 
-We present the development of a novel teachable agent
-that intentionally makes mistakes typical of children learning
-handwriting. Through this capability, the robot can be taught by
-children, who themselves may learn through their teaching.
+We present the development of a novel teachable agent that intentionally makes
+mistakes typical of children learning handwriting. Through this capability, the
+robot can be taught by children, who themselves may learn through their
+teaching.
 
-%Due to the intended use in a school environment, a commercially
-%affordable {\sc nao} humanoid robot has been used. Its writing capabilities 
-%have been implemented by leveraging synchronisation with a tablet display to
-%simulate fine motor skills otherwise infeasible for the robot.
-
-Within this article, Section \ref{sec:learningAlgorithm} presents the novel work in the area of
-artificial intelligence to develop a learning algorithm suitable for a teachable
-agent in the context of handwriting. Section \ref{sec:robotWriting} details the
-extension of this algorithm to an embodied robotic learning agent, including the
-new approach for achieving simulated fine motor skills on commercially
-affordable humanoid robots such as the {\sc nao}. Section \ref{sec:experiment} explores the 
-contributions made to the study of human-robot interaction, in discussing the
-use of the system with primary school children and its potential as a tool for
-addressing wider pedagogical research questions in education.
-Finally, Section \ref{sec:futureWork} addresses the challenges which are faced in extending this system to a level suitable for long-term studies, and Section \ref{sec:conclusions} concludes by reiterating the impact of the article's contributions.
+Within this article, Section \ref{sec:learningAlgorithm} presents the novel work
+in the area of artificial intelligence to develop a learning algorithm suitable
+for a teachable agent in the context of handwriting. Section
+\ref{sec:robotWriting} details the extension of this algorithm to an embodied
+robotic learning agent, including the new approach for achieving simulated fine
+motor skills on commercially affordable humanoid robots such as the {\sc nao}.
+Section \ref{sec:experiment} explores the contributions made to the study of
+human-robot interaction, in discussing the use of the system with primary school
+children and its potential as a tool for addressing wider pedagogical research
+questions in education. Finally, Section \ref{sec:futureWork} addresses the
+challenges which are faced in extending this system to a level suitable for
+long-term studies, and Section \ref{sec:conclusions} concludes by reiterating
+the impact of the article's contributions.
 
@@
 
-A parameterisation of letters and their deformities is used such 
-that different quality shapes can be generated, depending on the parameters input to
-the letter models. This allows us to configure the system to improve its writing 
-by modifying the parameters based on feedback from the 
-reinforcement learning partner (Section~\ref{sec:learningAlg}).
+A parameterisation of letters and their deformities is used such that different
+quality shapes can be generated, depending on the parameters input to the letter
+models. This allows us to configure the system to improve its writing by
+modifying the parameters based on feedback from the reinforcement learning
+partner (Section~\ref{sec:learningAlg}).
 
@@
 
-PCA is performed on a set of letter paths captured from a digital pen,
-using the UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of
-each letter (2 repetitions from 60 adult users). While it may be appropriate in future work to
-identify the location of salient features of the shapes which are robust to 
-unanticipated user input (such as shapes drawn backwards),
-the features are currently taken as $n=70$ uniformly spaced points along the shape
-path. The
-points are arranged into an observation vector presented in (\ref{eq:obsVec}),
-where $x_i$ and $y_i$ represent the coordinates of each of the points along the
-path. The observation shapes are normalised to have a unit maximum dimension 
-and {\bf 0} mean.
+PCA is performed on a set of letter paths captured from a digital pen, using the
+UJI Pen Characters 2 dataset \cite{Llorens2008} with 120 instances of each
+letter (2 repetitions from 60 adult users). While it may be appropriate in
+future work to identify the location of salient features of the shapes which are
+robust to unanticipated user input (such as shapes drawn backwards), the
+features are currently taken as $n=70$ uniformly spaced points along the shape
+path. The points are arranged into an observation vector presented in
+(\ref{eq:obsVec}), where $x_i$ and $y_i$ represent the coordinates of each of
+the points along the path. The observation shapes are normalised to have a unit
+maximum dimension and {\bf 0} mean.
 
@@
 Equation (\ref{eq:projection}) represents the projection from the original
-$2n$-dimensional feature space to a reduced $N$-dimensional space, where ${\bf p}$
-contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
-calculated as in (\ref{eq:paramCalc}). 
-${\bf \Phi }$ is
-an orthogonal $2n\times N$ matrix composed of the eigenvectors ${\bf v}_i$ corresponding to
-the largest $N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
-observations~\cite{Stegmann2002}, as shown in (\ref{eq:transformCalc}). 
-If there is correlation between the points in the observations, there will be
+$2n$-dimensional feature space to a reduced $N$-dimensional space, where ${\bf
+p}$ contains the coordinates in the $N$-dimensional space with ${\bf 0}$-origin,
+calculated as in (\ref{eq:paramCalc}).  ${\bf \Phi }$ is an orthogonal $2n\times
+N$ matrix composed of the eigenvectors ${\bf v}_i$ corresponding to the largest
+$N$ eigenvalues ($\lambda_i$) of the covariance matrix of the
+observations~\cite{Stegmann2002}, as shown in (\ref{eq:transformCalc}).  If
+there is correlation between the points in the observations, there will be
 eigenvalues of the covariance matrix which are close to zero. As such, removing
@@
 
-PCA is performed on all of the paths of a particular allograph in the
-dataset individually, to reduce the $2n$-dimensional space for that shape to one 
-with $N=10$ dimensions.
-Each shape is then approximated by the mean shape of the allograph plus a sum of the top 10
-eigenvectors, weighted by the parameter vector ${\bf p}$. 
+PCA is performed on all of the paths of a particular allograph in the dataset
+individually, to reduce the $2n$-dimensional space for that shape to one with
+$N=10$ dimensions.  Each shape is then approximated by the mean shape of the
+allograph plus a sum of the top 10 eigenvectors, weighted by the parameter
+vector ${\bf p}$.
+
 %Indeed, the amount of variance in the dataset
@@
 
-Equation (\ref{eq:projection}) may also be used
-to generate new shapes based on the parameters ${\bf p}$ which are used. ${\bf
-p}={\bf 0}$ will yield the mean shape, and variations to each of the $N$ values
-in ${\bf p}$ will cause a change in the shape represented by the corresponding
-eigenvector (Figure \ref{fig:deviations_sPrint}). 
-For the dataset presented in Figure \ref{fig:deviations_sPrint}, the
-eigenvectors associated with the 3 largest eigenvalues explain 78.5\% of the
-variance in the dataset, illustrating the capability of the statistical shape
-modelling approach to produce compact parameterisation of shapes.
+Equation (\ref{eq:projection}) may also be used to generate new shapes based on
+the parameters ${\bf p}$ which are used. ${\bf p}={\bf 0}$ will yield the mean
+shape, and variations to each of the $N$ values in ${\bf p}$ will cause a change
+in the shape represented by the corresponding eigenvector (Figure
+\ref{fig:deviations_sPrint}).  For the dataset presented in Figure
+\ref{fig:deviations_sPrint}, the eigenvectors associated with the 3 largest
+eigenvalues explain 78.5\% of the variance in the dataset, illustrating the
+capability of the statistical shape modelling approach to produce compact
+parameterisation of shapes.
 
@@
 Interestingly, although the parameters are the result of an \emph{unsupervised}
-shape analysis, they still represent variations which could have
-been intuitively identified by a manual parameterisation. For example, for the
-model shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent
-the height of the top half of the letter compared to the bottom half, the width
-of the overall shape, etc. The ability to generate varied levels of deformations
+shape analysis, they still represent variations which could have been
+intuitively identified by a manual parameterisation. For example, for the model
+shown in Figure \ref{fig:deviations_sPrint}, the parameters may represent the
+height of the top half of the letter compared to the bottom half, the width of
+the overall shape, etc. The ability to generate varied levels of deformations
 which may be ascribed descriptive interpretations (not just numerical) is an
-advantage of this method, given its intended use with humans. It is, for instance,
-possible for a teacher to create letters -- which will be used as a starting point
-for the system -- with a particular feature (a wide
-`s' or a `d' with a large loop, for example).
+advantage of this method, given its intended use with humans. It is, for
+instance, possible for a teacher to create letters -- which will be used as a
+starting point for the system -- with a particular feature (a wide `s' or a `d'
+with a large loop, for example).
 
@@
 
-As explained, new letters can be generated by varying the parameter values 
-for a shape model in accordance with (\ref{eq:projection}). By choosing
-parameter values which lie within the observed range in the dataset, it is
-possible to produce letters which are more likely to be reasonable looking.
-When the parameter values are outside of the range observed in the dataset, they
-are less likely to represent shapes from the dataset of adult-written letters, 
-and as a result are more likely to represent poor shapes.
-Figure \ref{fig:sampleLetters} illustrates sample letters generated from the
-models of `e' and `g' by selecting random values for the first 5 parameters 
-from a distribution with
-standard deviation of $3\sqrt\lambda_i$, rather than the $\sqrt\lambda_i$
-standard deviation observed in the dataset.
+As explained, new letters can be generated by varying the parameter values for a
+shape model in accordance with (\ref{eq:projection}). By choosing parameter
+values which lie within the observed range in the dataset, it is possible to
+produce letters which are more likely to be reasonable looking.  When the
+parameter values are outside of the range observed in the dataset, they are less
+likely to represent shapes from the dataset of adult-written letters, and as a
+result are more likely to represent poor shapes.  Figure \ref{fig:sampleLetters}
+illustrates sample letters generated from the models of `e' and `g' by selecting
+random values for the first 5 parameters from a distribution with standard
+deviation of $3\sqrt\lambda_i$, rather than the $\sqrt\lambda_i$ standard
+deviation observed in the dataset.
 
@@
 system exhibit the same kind of deformities. Chandra identifies other, less
-common, mistakes which involve topological changes, such as letters being 
-broken into subparts or mirrored. Using a database of
-children's letters when available may yield potential for better parameterising
-these other mistakes. However, as an initial approximation, the shape models
-generated from PCA on a dataset of only adults' writing have shown to be
-well-suited to generate `poor' letters that children were able to identify as
-such and successfully improve.
+common, mistakes which involve topological changes, such as letters being broken
+into subparts or mirrored. Using a database of children's letters when available
+may yield potential for better parameterising these other mistakes. However, as
+an initial approximation, the shape models generated from PCA on a dataset of
+only adults' writing have shown to be well-suited to generate `poor' letters
+that children were able to identify as such and successfully improve.
 
@@
 In addition to generating letters by varying input parameters, the statistical
-shape model of Section \ref{sec:writingGeneration} may also be used 
-to determine a particular letter's parameters, given the model. The parameters of user-drawn
-letters may therefore be used in order implement a 
-learning algorithm which adapts to the user's feedback via demonstration letters.
+shape model of Section \ref{sec:writingGeneration} may also be used to determine
+a particular letter's parameters, given the model. The parameters of user-drawn
+letters may therefore be used in order implement a learning algorithm which
+adapts to the user's feedback via demonstration letters.
 
@@
 
-The method we employ for
-responding to user demonstrations is to move the learning algorithm's parameters
-towards those of the demonstration. In the results presented in this work, the
-linear update equation shown in (\ref{eq:update}) is used, where ${\bf p}$ is the
-learned parameter vector at time step $k$, and $\alpha$ is the learning rate,
-between 0 and 1.
+The method we employ for responding to user demonstrations is to move the
+learning algorithm's parameters towards those of the demonstration. In the
+results presented in this work, the linear update equation shown in
+(\ref{eq:update}) is used, where ${\bf p}$ is the learned parameter vector at
+time step $k$, and $\alpha$ is the learning rate, between 0 and 1.
 
@@
 demonstrations from a child for the letter `s' using a learning rate of
-$\alpha=1/2$. Observe that even poorly-written demonstrations allow the system to improve.
+$\alpha=1/2$. Observe that even poorly-written demonstrations allow the system
+to improve.
 
@@
 It is possible that parameters ${\bf p}^{(k)}$ and ${\bf p}_{demo}$, which
-individually yield acceptable shapes, produce parameters ${\bf p}^{(k+1)}$
-which yield an unacceptable shape. This is especially true if the demonstration
-shape is of a different style to that learnt at time $k$ (see 
-Figure~\ref{fig:eDemo}), as there are no
-restrictions imposed on parameter values. However, the proposed method for adapting to
-the demonstration shapes has the advantage of being able to recover from such a situation: with further
-demonstrations of the same letter, the system would eventually approach the
-demonstration shape. As a result, the event of poor-looking 
-intermediate letters
-would not limit the interaction later proposed in Section \ref{sec:experiment}
-in a technical sense, but it may influence the user's \emph{perception} of the learning
-agent. It remains to be seen if it is necessary to avoid such an event
-mathematically.
+individually yield acceptable shapes, produce parameters ${\bf p}^{(k+1)}$ which
+yield an unacceptable shape. This is especially true if the demonstration shape
+is of a different style to that learnt at time $k$ (see Figure~\ref{fig:eDemo}),
+as there are no restrictions imposed on parameter values. However, the proposed
+method for adapting to the demonstration shapes has the advantage of being able
+to recover from such a situation: with further demonstrations of the same
+letter, the system would eventually approach the demonstration shape. As a
+result, the event of poor-looking intermediate letters would not limit the
+interaction later proposed in Section \ref{sec:experiment} in a technical sense,
+but it may influence the user's \emph{perception} of the learning agent. It
+remains to be seen if it is necessary to avoid such an event mathematically.
 
@@
     \includegraphics[width=0.3\textwidth]{figures/learningEdemo}
-    \caption{\label{fig:eDemo}Example of the learning algorithm
-    responding (top) to user demonstration of shapes (bottom) for the letter `e', passing through a parameter state which yields a poor letter (demonstrations received from a 7-8 year-old child).}
+    \caption{\label{fig:eDemo}Example of the learning algorithm responding (top)
+    to user demonstration of shapes (bottom) for the letter `e', passing through
+    a parameter state which yields a poor letter (demonstrations received from a 7-8
+    year-old child).}
 \end{figure}
@@
 In order to develop a teachable agent that is appropriate for engaging a child
-in the learning by teaching paradigm, we have established capabilities for the robot 
-to engage in handwriting and interactive turn-taking.
+in the learning by teaching paradigm, we have established capabilities for the
+robot to engage in handwriting and interactive turn-taking.
 
-The {\sc nao} V4 humanoid robot, which has been purposely designed by 
-Aldebaran Robotics to look approachable \cite{Gouaillier2008}, is used for
-this work. It is a commercially affordable biped robot, 58cm tall, with 25
-degrees of freedom, two cameras, speech capabilities and the ability to
-autonomously execute a range of tasks.
+The {\sc nao} V4 humanoid robot, which has been purposely designed by Aldebaran
+Robotics to look approachable \cite{Gouaillier2008}, is used for this work. It
+is a commercially affordable biped robot, 58cm tall, with 25 degrees of freedom,
+two cameras, speech capabilities and the ability to autonomously execute a range
+of tasks.
 
-Precise control over what the robot is writing is necessary in the
-proposed application of a handwriting. Because
-of the limited fine motor skills possible with such an affordable robot, in
-addition to the absence of force feedback and other technical necessities, we
-have configured the {\sc nao} to use simulated handwriting with a synchronised tablet
-to achieve this level of control.
+Precise control over what the robot is writing is necessary in the proposed
+application of a handwriting. Because of the limited fine motor skills possible
+with such an affordable robot, in addition to the absence of force feedback and
+other technical necessities, we have configured the {\sc nao} to use simulated
+handwriting with a synchronised tablet to achieve this level of control.
 
-The development of the necessary components for embedding the handwriting learning
-algorithm presented in Section \ref{sec:learningAlgorithm} in the humanoid agent
-are presented in the sections which follow.
+The development of the necessary components for embedding the handwriting
+learning algorithm presented in Section \ref{sec:learningAlgorithm} in the
+humanoid agent are presented in the sections which follow.
 
@@
 robot's motions must still sufficiently match the displayed trajectory in order
-capture the engagement of the child participant in the action. Aldebaran's NaoQi API
-is used for the inverse kinematics of the trajectory following. The Robot
+capture the engagement of the child participant in the action. Aldebaran's NaoQi
+API is used for the inverse kinematics of the trajectory following. The Robot
 Operating System (ROS)\footnote{The ROS stack for {\sc nao} is available at:
 \url{http://wiki.ros.org/nao_robot}.} is used for integration of the {\sc nao}
-with external reference frames, such as the tablet's location, 
-using the $tf$ transformation library \cite{Foote2013}.
+with external reference frames, such as the tablet's location, using the $tf$
+transformation library \cite{Foote2013}.
 
 When using simulated handwriting, it is no longer necessary that the robot
-engages in the typical style of handwriting of using a writing instrument at a desk.
-Having the robot point at a vertical writing surface to cause the
-trajectory to appear (as in Figure \ref{fig:naoWriting}) has several
-advantages:
+engages in the typical style of handwriting of using a writing instrument at a
+desk.  Having the robot point at a vertical writing surface to cause the
+trajectory to appear (as in Figure \ref{fig:naoWriting}) has several advantages:
 
@@
 
-We have therefore designed the system in such a way that the robot is
-simulating handwriting by pointing at the tablet\footnote{Teachers interviewed
-for their feedback on the system advised that children are asked to draw letters
-in the air in a similar manner as part of their handwriting education. The behaviour 
-is hence not unfamiliar to children.}. As
-interacting with a tablet with one's finger is not uncommon, this may aid the
-acceptance of the writing style by users.
+We have therefore designed the system in such a way that the robot is simulating
+handwriting by pointing at the tablet\footnote{Teachers interviewed for their
+feedback on the system advised that children are asked to draw letters in
+the air in a similar manner as part of their handwriting education. The
+behaviour is hence not unfamiliar to children.}. As interacting with a
+tablet with one's finger is not uncommon, this may aid the acceptance of the
+writing style by users.
 
-Because
-motion planning is performed with respect to the hand of the robot, rather than
-its fingertip, one or two of the orientation degrees of freedom of the hand
-are fixed to keep the finger approximately perpendicular to the writing surface,
-depending on the desired accuracy. The remaining free orientation(s), coupled
-with the whole-body motion control available, allow for a sufficient working
-space for writing on the entire tablet.
+Because motion planning is performed with respect to the hand of the robot,
+rather than its fingertip, one or two of the orientation degrees of freedom of
+the hand are fixed to keep the finger approximately perpendicular to the writing
+surface, depending on the desired accuracy. The remaining free orientation(s),
+coupled with the whole-body motion control available, allow for a sufficient
+working space for writing on the entire tablet.
 
@@
 To enable the robot's `writing' to display while the robot is tracing
-trajectories, ROS is used for the communication between the devices,
-including the Android tablet\footnote{For more information about ROS on Android
-devices see \url{http://wiki.ros.org/android}}. As a result, aspects of the
-networking between the tablet and the robot, such as the overheads associated
-with connections, ports, etc. have been simplified.
+trajectories, ROS is used for the communication between the devices, including
+the Android tablet\footnote{For more information about ROS on Android devices
+see \url{http://wiki.ros.org/android}}. As a result, aspects of the networking
+between the tablet and the robot, such as the overheads associated with
+connections, ports, etc. have been simplified.
 
 An Android application has been developed to receive the trajectory message over
-a ROS topic and display the trajectory as an
-animation. Synchronisation between the tablet and the robot is achieved by
-using NTP servers to synchronise device clocks; passing only the necessary number of points (7)
-to the robot's motion planner to improve timing accuracy; and not running 
-computationally expensive tasks on the robot (such as camera publishing) while it 
-is writing.
+a ROS topic and display the trajectory as an animation. Synchronisation between
+the tablet and the robot is achieved by using NTP servers to synchronise device
+clocks; passing only the necessary number of points (7) to the robot's motion
+planner to improve timing accuracy; and not running computationally expensive
+tasks on the robot (such as camera publishing) while it is writing.
 
@@
 determine the relative position of the writing surface (Figure
-\ref{fig:tabletDetection}). When used in an interaction involving a participant, this
-allows a user to move the tablet as required for the interaction. The tablet is 
-assumed to be stationary during the writing process as detecting the tablet interferes
-with the robot's adherance to writing synchronisation.
+\ref{fig:tabletDetection}). When used in an interaction involving a participant,
+this allows a user to move the tablet as required for the interaction. The
+tablet is assumed to be stationary during the writing process as detecting the
+tablet interferes with the robot's adherance to writing synchronisation.
 
@@
 
-The user demonstrations are received by the
-interaction controller running on a desktop computer. It is responsible for
-getting the {\sc nao} to prompt and respond appropriately to feedback received using
-a finite state machine to manage the interaction stage and various system
-inputs. In the context of learning handwriting, an additional input to the system 
-is a word from which the letters are to be learned, which is detected by a fiducial 
-marker on the card displaying the word.
-The controller provides inputs to the learning algorithm including the word to learn
-and the user demonstrations, by inferring the letter which the demonstrations are 
-intended for based on their position on the tablet. The output shapes from the 
-learning algorithm are then sent again to the devices which write them.
+The user demonstrations are received by the interaction controller running on a
+desktop computer. It is responsible for getting the {\sc nao} to prompt and
+respond appropriately to feedback received using a finite state machine to
+manage the interaction stage and various system inputs. In the context of
+learning handwriting, an additional input to the system is a word from which the
+letters are to be learned, which is detected by a fiducial marker on the card
+displaying the word.  The controller provides inputs to the learning algorithm
+including the word to learn and the user demonstrations, by inferring the letter
+which the demonstrations are intended for based on their position on the tablet.
+The output shapes from the learning algorithm are then sent again to the devices
+which write them.
 
@@
 robotic agent represents a tool which may be used for investigating social and
-pedagogical research questions. For example, one such question is what impact the addition of
-such a teachable robotic agent would have on the outcomes of a typical
-handwriting intervention. 
-Preliminary studies at two schools in the Geneva area, involving over 50 children, 
-have been conducted to evaluate the feasibility and technical soundness of the 
-interaction system proposed as a tool for such investigations.
+pedagogical research questions. For example, one such question is what impact
+the addition of such a teachable robotic agent would have on the outcomes of a
+typical handwriting intervention.  Preliminary studies at two schools in the
+Geneva area, involving over 50 children, have been conducted to evaluate the
+feasibility and technical soundness of the interaction system proposed as a tool
+for such investigations.
 
@@
 %handwriting by correcting the letters it writes on the tablet.
-Figure~\ref{fig:pilotInteraction}
-illustrates an example interaction sequence between the participant and the
-robot which consists of the following stages:
+
+Figure~\ref{fig:pilotInteraction} illustrates an example interaction sequence
+between the participant and the robot which consists of the following stages:
 
@@
 
-A pilot study at the first school consisted of four groups of
-approximately 8 english-speaking children each, aged 6-7 years. The children
-interacted with the system for a total of 65 minutes, with the robot writing 96
-letters. 49 of these letters were in response to demonstrations from the children 
-and the remaining were from when new words were requested.
+A pilot study at the first school consisted of four groups of approximately 8
+english-speaking children each, aged 6-7 years. The children interacted with the
+system for a total of 65 minutes, with the robot writing 96 letters. 49 of these
+letters were in response to demonstrations from the children and the remaining
+were from when new words were requested.
 
-As a result of the pilot study, we acted on two key observations. The first
-was that children appeared to have a difficult time providing demonstrations to
-the robot in the same place as previously-written letters. At the time, the
-system required the children to write on top of a letter of the same type as the
-one which they were demonstrating, and the children seemed to find this
+As a result of the pilot study, we acted on two key observations. The first was
+that children appeared to have a difficult time providing demonstrations to the
+robot in the same place as previously-written letters. At the time, the system
+required the children to write on top of a letter of the same type as the one
+which they were demonstrating, and the children seemed to find this
 counter-intuitive and would occasionally just trace the robot's letter as it
@@
 observed giving advice to the child designated as the letter demonstrator,
-potentially giving rise to a higher level paradigm of learning by
-\emph{teaching to teach}. As a consequence of this observation, the study which
-followed at the second school was designed to further observe the effect of the
-number of children interacting with the robot.
+potentially giving rise to a higher level paradigm of learning by \emph{teaching
+to teach}. As a consequence of this observation, the study which followed at the
+second school was designed to further observe the effect of the number of
+children interacting with the robot.
 
 \subsection{Outcomes of Preliminary Study 2}
-The study at the second school involved 21 french-speaking students aged 7-8 years. 7 children
-interacted with the robot individually and 7 sessions included the remaining
-14 students interacting with the robot in pairs.
-Initial parameters were drawn from a range purposely chosen to generate shapes 
-for letters `e' and `s' which would elicit correction. For the other letters, 
-parameters were fixed, generating shapes which some groups still chose to correct 
-(e.g. 13/14 for `n' and 2/14 for `c'). The duration of the sessions
-was between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).
+
+The study at the second school involved 21 french-speaking students aged 7-8
+years. 7 children interacted with the robot individually and 7 sessions included
+the remaining 14 students interacting with the robot in pairs.  Initial
+parameters were drawn from a range purposely chosen to generate shapes for
+letters `e' and `s' which would elicit correction. For the other letters,
+parameters were fixed, generating shapes which some groups still chose to
+correct (e.g. 13/14 for `n' and 2/14 for `c'). The duration of the sessions was
+between 8 and 15 minutes, with an average of 11.4 minutes (SD = 2.3).
 
@@
 
-We have concluded following the second study that the system has 
-been validated as a technically sound autonomous interaction. 
-The interaction setup including the teachable
-robotic agent withstood the interaction which lasted for a total of 160 minutes. 
-During this time the robot wrote 335 letters, 152 of which in response to
-demonstrations received from the 21 children. Technical 
-intervention was only required for the three instances that the robot fell 
-later in the day. Otherwise, the technical components of the system operated 
-autonomously and as expected over the sessions.
+We have concluded following the second study that the system has been validated
+as a technically sound autonomous interaction.  The interaction setup including
+the teachable robotic agent withstood the interaction which lasted for a total
+of 160 minutes.  During this time the robot wrote 335 letters, 152 of which in
+response to demonstrations received from the 21 children. Technical intervention
+was only required for the three instances that the robot fell later in the day.
+Otherwise, the technical components of the system operated autonomously and as
+expected over the sessions.
 
-Furthermore, no child indicated that they did not believe that the robot was writing
-by itself. There were, at times, 
-    questions about the robot's writing method at the beginning of the interaction,
-    but when advised that the robot ``tells the tablet what it wants to write,''
-    this was accepted by the children. 
-%     To allow the children an opportunity to
-%     express doubt in the robot's ability to write without explicitly asking them if
-%     the robot was pretending, the children were asked if they believed that the
-%     robot would be able to write its name, \emph{{\sc nao}} which had not previously been
-%     demonstrated. It was reasoned that this would prompt the children to question
-%     the point of the robot actually \emph{writing} if they had any suspicion that
-%     the robot was pretending, but this was never the case. 
-    On the rare occasion that the
-    robot's writing was not correctly synchronised with the tablet, this did
-    not appear to influence the children's impression. 
-    If older children participate in the interaction study --
-    which may be likely as children with lasting handwriting difficulties are included
-    as participants -- it may become more important to invest time into the
+Furthermore, no child indicated that they did not believe that the robot was
+writing by itself. There were, at times, questions about the robot's writing
+method at the beginning of the interaction, but when advised that the robot
+``tells the tablet what it wants to write,'' this was accepted by the children. 
+%     To allow the children an opportunity to express doubt in the robot's
+%     ability to write without explicitly asking them if the robot was
+%     pretending, the children were asked if they believed that the robot would
+%     be able to write its name, \emph{{\sc nao}} which had not previously been
+%     demonstrated. It was reasoned that this would prompt the children to
+%     question the point of the robot actually \emph{writing} if they had any
+%     suspicion that the robot was pretending, but this was never the case. 
+On the rare occasion that the robot's writing was not correctly synchronised
+with the tablet, this did not appear to influence the children's impression.
+If older children participate in the interaction study -- which may be
+likely as children with lasting handwriting difficulties are included as
+participants -- it may become more important to invest time into the
 believability of the robot's writing scheme. However, for 6-8 year olds the
@@
 
-Regarding the engagement of the children in teaching the robot, 
-    an average of 10.9 demonstration letters (SD = 4.4) were
-    provided to the robot for each session during the interaction.
-    In 9 out of the 14 sessions (64\%), the robot received demonstration letters
-    even \emph{after} reaching the test stage of the interaction. The participants'
-    teaching after the test word had been written and evaluated -- the only
-    purposefully imposed external motivation -- may suggest that by that time
-    the participants had become intrinsically motivated to engage in the
-    interaction, as we anticipated.
+Regarding the engagement of the children in teaching the robot, an average of
+10.9 demonstration letters (SD = 4.4) were provided to the robot for each
+session during the interaction.  In 9 out of the 14 sessions (64\%), the robot
+received demonstration letters even \emph{after} reaching the test stage of the
+interaction. The participants' teaching after the test word had been written and
+evaluated -- the only purposefully imposed external motivation -- may suggest
+that by that time the participants had become intrinsically motivated to engage
+in the interaction, as we anticipated.
 
@@
 \section{Towards Long-term Studies}\label{sec:futureWork}
-%How to break this section up?
 
-A conclusion drawn in a systematic review of handwriting intervention studies~\cite{Hoy2011} 
-is that any of the studies considered which involved 
+A conclusion drawn in a systematic review of handwriting intervention
+studies~\cite{Hoy2011} is that any of the studies considered which involved
 fewer than two practice sessions per week and fewer than a total of 20 practice
-sessions, including homework, were not found to demonstrate effective results. This 
-highlights the necessity to engage students in an interaction which will be sustainable
- over the long-term if 
-we want to address research questions which involve the measurement of learning gains. 
-Several challenges are raised in developing such long-term capabilities for the system.
+sessions, including homework, were not found to demonstrate effective results.
+This highlights the necessity to engage students in an interaction which will be
+sustainable over the long-term if we want to address research questions which
+involve the measurement of learning gains.  Several challenges are raised in
+developing such long-term capabilities for the system.
 
@@
 nominal protocol presented in Section~\ref{sec4}, and consequently still
-requires the supervision of an experimenter. The interaction finite state machine would
-require extension in non-trivial ways to allow for long, fully autonomous
-interactions with children.
+requires the supervision of an experimenter. The interaction finite state
+machine would require extension in non-trivial ways to allow for long, fully
+autonomous interactions with children.
 
-In the current system, the robot can ask questions and prompt participants, but it 
-cannot engage in discussions with the participants. It is clear that work is necessary 
-to develop the conversational agent in the interaction so that the presence of an 
-experimenter is not required for a captivating and continuing engagement. While there is the 
-possiblity to focus the interaction design on group-based interaction with the robot 
-in order to alleviate the necessity of a conversational agent, we find reason to 
-believe that constructing such a social interaction is not a trivial task. Anecdotes 
-from the preliminary studies have shown that some children may criticise another's 
-demonstrations to the robot, which may or may not be as damaging to a child's 
-self-efficacy as when they are criticised in a typical educational context.
+In the current system, the robot can ask questions and prompt participants, but
+it cannot engage in discussions with the participants. It is clear that work is
+necessary to develop the conversational agent in the interaction so that the
+presence of an experimenter is not required for a captivating and continuing
+engagement. While there is the possiblity to focus the interaction design on
+group-based interaction with the robot in order to alleviate the necessity of a
+conversational agent, we find reason to believe that constructing such a social
+interaction is not a trivial task. Anecdotes from the preliminary studies have
+shown that some children may criticise another's demonstrations to the robot,
+which may or may not be as damaging to a child's self-efficacy as when they are
+criticised in a typical educational context.
 
@@
 
-How the children's perception of the robot as a learning agent may change over the 
-long-term remains to be seen. On one occasion during the preliminary studies, a 
-child's response to whether or not the {\sc nao} could write its own name (not
-previously demonstrated) included that it 
-may have problems with the `n', as the child had been correcting the robot on this 
-letter. We believe that the user was projecting human-like learning features, such as 
-forgetfulness, onto the robot, although they were not technically present in the system.
-This may need to be capitalised on when considering how to 
-extend the interaction for long-term use, as the present system -- with a learning rate 
-such that progress is evident to the user -- will cause convergence for a letter within a 
-few iterations.
+How the children's perception of the robot as a learning agent may change over
+the long-term remains to be seen. On one occasion during the preliminary
+studies, a child's response to whether or not the {\sc nao} could write its own
+name (not previously demonstrated) included that it may have problems with the
+`n', as the child had been correcting the robot on this letter. We believe that
+the user was projecting human-like learning features, such as forgetfulness,
+onto the robot, although they were not technically present in the system.  This
+may need to be capitalised on when considering how to extend the interaction for
+long-term use, as the present system -- with a learning rate such that progress
+is evident to the user -- will cause convergence for a letter within a few
+iterations.
 
-We expect that incorporating a
-database of letters drawn by children into the shape modeling process will
-facilitate generating shape models which capture a wider range of mistakes typical
-of children learning handwriting. However, the current system has conceptual -- 
-a PCA-only approach can not generate or learn a different shape topology -- and 
-technical -- no support is currently implemented for shapes which require pen
-lifting between strokes -- limitations which would need to be overcome.
+We expect that incorporating a database of letters drawn by children into the
+shape modeling process will facilitate generating shape models which capture a
+wider range of mistakes typical of children learning handwriting. However, the
+current system has conceptual -- a PCA-only approach can not generate or learn a
+different shape topology -- and technical -- no support is currently implemented
+for shapes which require pen lifting between strokes -- limitations which would
+need to be overcome.
 
 If the system is extended to allow for a wider range of mistakes, a further
-topic for exploration then is how the handwriting error
-generation of the system may be abstracted to a higher level of control so that
-a teacher may configure it to work with a child on a particular type of
-mistakes based on the child's performance. Where would the balance lie between
-developing autonomous capabilities for the system to determine the child's
-difficulties and empowering the teaching staff to decide for themselves
-instead?
+topic for exploration then is how the handwriting error generation of the system
+may be abstracted to a higher level of control so that a teacher may configure
+it to work with a child on a particular type of mistakes based on the child's
+performance. Where would the balance lie between developing autonomous
+capabilities for the system to determine the child's difficulties and empowering
+the teaching staff to decide for themselves instead?
 
-Addressing these challenges will take us further towards answering if 
-the addition of a teachable robotic agent to handwriting interventions 
-would benefit the participants' self-esteem, motivation, and learning gains.
+Addressing these challenges will take us further towards answering if the
+addition of a teachable robotic agent to handwriting interventions would benefit
+the participants' self-esteem, motivation, and learning gains.
 
@@
 education, but instead in an activity -- handwriting -- which requires fine
-physical skills. In such activities, the embodied nature of the robot is appropriate as in interventions where motor mimicry is elicited \cite{Berninger1997} the arm motion for instance is, \emph{by
-itself}, part of the teaching. Furthermore, when facing a child with school 
-difficulties, robots can play the role of a na\"ive learner which neither adults 
-nor peers -- because of the social effects it would induce -- can convincingly 
-play. Along these lines, we hope to see more research
-on non-STEM educational applications of robotics.
+physical skills. In such activities, the embodied nature of the robot is
+appropriate as in interventions where motor mimicry is elicited
+\cite{Berninger1997} the arm motion for instance is, \emph{by itself}, part of
+the teaching. Furthermore, when facing a child with school difficulties, robots
+can play the role of a na\"ive learner which neither adults nor peers -- because
+of the social effects it would induce -- can convincingly play. Along these
+lines, we hope to see more research on non-STEM educational applications of
+robotics.
 
@@
 
-The strong social impact of early educational problems makes continued research in this field
-an undoubtedly meaningful challenge for robotics and human-robot interaction.
+The strong social impact of early educational problems makes continued research
+in this field an undoubtedly meaningful challenge for robotics and human-robot
+interaction.
 

### 2014-12-27 main.tex
De-anonymized + copyright for final submission

@@
 
-%
 % --- Author Metadata here ---
-\conferenceinfo{10th ACM/IEEE International Conference on Human-Robot Interaction}{2015 Portland, USA}
-%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
-%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
+\conferenceinfo{HRI '15, March 02 - 05 2015,}{Portland, OR, USA}
+\CopyrightYear{is held by the owner/author(s). Publication rights licensed to ACM.} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
+\crdata{978-1-4503-2883-8/15/03}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.
 % --- End of Author Metadata ---
@@
 \numberofauthors{1} 
-%\author{
-%\alignauthor
-%Deanna Hood, Séverin Lemaignan, Pierre Dillenbourg\\
-%   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
-%   \affaddr{École Polytechnique Fédérale\\ de Lausanne (EPFL)}\\
-%   %\affaddr{CH-1015 Lausanne, Switzerland}\\
-%   \email{firstname.lastname@epfl.ch}
-%}
-
-%(DH) my EPFL email address won't work for much longer....
+\author{
+\alignauthor
+Deanna Hood, Séverin Lemaignan, Pierre Dillenbourg\\
+   \affaddr{Computer-Human Interaction in Learning and Instruction Laboratory (CHILI)}\\
+   \affaddr{École Polytechnique Fédérale de Lausanne (EPFL)}\\
+   %\affaddr{CH-1015 Lausanne, Switzerland}\\
+   \email{firstname.lastname@epfl.ch}
+}
 
@@
 learning in a range of contexts, most commonly related to language
-skills~\cite{Han2010}, and less often to physical skills (such as
+skills~\cite{han2010robot}, and less often to physical skills (such as
 calligraphy~\cite{Matsui2013}).  Looking at the converse (humans \emph{teaching}
@@
 \end{figure}
-%\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video of the synchronised 
-\footnotetext{See \url{[anonymized]} for a video of the synchronised 
-writing demonstration. }
+\footnotetext{See \url{https://www.youtube.com/watch?v=2qWFSJRxCU0} for a video
+of the synchronised writing demonstration. }
 
@@
 The source code for the teachable robotic handwriting partner has been made 
-%available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
-available at \url{[anonymized]}.
+available at \url{https://github.com/chili-epfl/cowriter_letter_learning}.
 
@@
             \label{fig:first}
-            \includegraphics[width=0.2\textwidth]{figures/1anon.jpg}
+            \includegraphics[width=0.2\textwidth]{figures/1card}
         }~
@@
            \label{fig:second}
-           \includegraphics[width=0.2\textwidth]{figures/2anon.jpg}
+           \includegraphics[width=0.2\textwidth]{figures/2word}
         }\\ %  ------- End of the first row ----------------------%
@@
             \label{fig:third}
-            \includegraphics[width=0.2\textwidth]{figures/3anon.jpg}
+            \includegraphics[width=0.2\textwidth]{figures/3ask}
         }~
@@
             \label{fig:fourth}
-            \includegraphics[width=0.2\textwidth]{figures/4anon.jpg}
+            \includegraphics[width=0.2\textwidth]{figures/4correct}
         }%
@@
 % Anonymized for double-blind review
-%\section*{Acknowledgments}
-%
-%This research was supported by the Swiss National Science Foundation through the
-%National Centre of Competence in Research Robotics.
+\section*{Acknowledgments}
+
+This research was supported by the Swiss National Science Foundation through the
+National Centre of Competence in Research Robotics.
 
